---
title: "ForageModv02 Supplementary Analysis"
output:
  pdf_document:
    toc: true
    toc_depth: 2
    number_sections: true
bibliography: grateful-refs.bib
csl: pnas.csl

---

```{r load-data, message=FALSE, warning=FALSE, include=FALSE}
library(knitr)
library(broom)
library(tidyverse)
library(rcompanion)
library(fitdistrplus)
library(gtsummary)
library(jtools)
library(betareg)
library(mgcv)
library(ggpubr)
library(ggthemes)
library(lme4)
theme_set(theme_bw())

data = readRDS("../results/bb-data.rds")

parameters = c(
  "cycle-duration",  # 100, 250
  "veg-cycle-start", # productive, unproductive
  "veg-distribution", # random, clustered
  "burnt-neighbor-limit", # 1, 4, 8
  "burn-cost", # 0, 50
  "burn-veg-type-threshold", # 4, 7
  "movement-model" #Random, Directed
)
data[,parameters] = lapply(data[,parameters], as.factor)
data$`veg-distribution` = factor(data$`veg-distribution`, 
                                 levels = c("\"random\"", "\"clustered\""))
data$`movement-model` = factor(data$`movement-model`, 
                               levels = c("\"Random Walk\"", "\"Directed Walk\""))

data$adj.fi = data$mean.fi/data$pop.count
data$same.fi.prop = data$mean.same.fi / data$mean.fi

data$pop.dens = data$pop.count/(51*51)

data$bself.prop = data$benefit_self / (data$pop.count * data$mean.fm)
data$bother.prop = data$benefit_other / (data$pop.count * data$mean.fm)

data$burnt = data$`veg_-1`
```

```{r setup-correlation-dataframes, message=FALSE, warning=FALSE, include=FALSE}
veg.100.prod = readRDS("../results/outputs/veg_moransi_100-prod.rds")
veg.100.unprod = readRDS("../results/outputs/veg_moransi_100-unprod.rds")
veg.250.prod = readRDS("../results/outputs/veg_moransi_250-prod.rds")
veg.250.unprod = readRDS("../results/outputs/veg_moransi_250-unprod.rds")
veg.data = bind_rows(veg.100.prod, veg.100.unprod, veg.250.prod, veg.250.unprod)
be.100 = readRDS("../results/outputs/be_morans.i_cycle.100.rds")
be.250 = readRDS("../results/outputs/be_morans.i_cycle.250.rds")
be.data = bind_rows(be.100, be.250)

rm(list = c("veg.100.prod", "veg.100.unprod", 
            "veg.250.prod", "veg.250.unprod", 
            "be.100", "be.250"))

outputs = c(
  "pop.dens", #pop count/world size
  "burnt", 
  "mean.burn.prob", 
  "adj.fi", #average interaction count/ population count
  "mean.fm",  #average forager movements per capita
  "bself.prop", #
  "bother.prop", 
  "veg_morans.i", 
  "shannon.div", 
  "be_morans.i"
)

par(mfrow = c(1,3))
par(mar=c(0,1,0,1))
#plot at 250
data250 = data %>% dplyr::filter(ticks == 250) %>% 
  left_join(veg.data %>% 
              dplyr::filter(ticks == 250) %>% 
              dplyr::select(exp, morans.i, shannon.div, shannon.div.no0) %>% 
              rename(veg_morans.i = morans.i), 
            by = c("exp")) %>% 
  left_join(be.data %>% 
              dplyr::filter(ticks == 250) %>% 
              dplyr::select(exp, morans.i) %>%
              rename(be_morans.i = morans.i), 
            by = c("exp"))

#plot at 2000
data2000 = data %>% filter(ticks == 2000) %>% 
  left_join(veg.data %>% 
              filter(ticks == 2000) %>% 
              dplyr::select(exp, morans.i, shannon.div, shannon.div.no0) %>% 
              rename(veg_morans.i = morans.i), 
            by = c("exp")) %>% 
  left_join(be.data %>% 
              filter(ticks == 2000) %>% 
              dplyr::select(exp, morans.i) %>%
              rename(be_morans.i = morans.i), 
            by = c("exp"))

#plot at 3500
data3500 = data %>% filter(ticks == 3500) %>% 
  left_join(veg.data %>% 
              filter(ticks == 3500) %>% 
              dplyr::select(exp, morans.i, shannon.div, shannon.div.no0) %>% 
              rename(veg_morans.i = morans.i), 
            by = c("exp")) %>% 
  left_join(be.data %>% 
              filter(ticks == 3500) %>% 
              dplyr::select(exp, morans.i) %>%
              rename(be_morans.i = morans.i), 
            by = c("exp"))

start.labs = c("unproductive start", "productive start")
names(start.labs) = c("\"unproductive\"", "\"productive\"")
cycle.labs = c("cycle every 250 ticks", "cycle every 100 ticks")
names(cycle.labs) = c(250, 100)
dist.labs = c("random environmental potential", 
              "clustered environmental potential")
names(dist.labs) = c("\"random\"", "\"clustered\"")
bc.labs = c("burn cost = 0", "burn cost = 100", 
            "burn cost = 200", "burn cost = 300")
names(bc.labs) = c(0, 100, 200, 300)
bt.labs = c("can burn veg types 1-4", "can burn veg types 1-7")
names(bt.labs) = c(4, 7)
bn.labs = c("can burn with 1 burnt neighbor", 
            "can burn with 4 burnt neighbors", 
            "can burn with 8 burnt neighbors")
names(bn.labs) = c(1, 4, 8)
move.labs = c("random walks", "directed walks")
names(move.labs) = c("\"Random Walk\"", "\"Directed Walk\"")

```


# Population maintenance?

First, we checked to see whether all model runs maintained a population across all 3500 ticks.

```{r pop-maintenance, echo=TRUE, message=FALSE, warning=FALSE}
all.exp = unique(data$exp)

end.tick = unique(data$`tick-limit`)
fd = data %>% filter(ticks == end.tick)
finished.exp = unique(fd$exp)
rm(list = "fd")

#finished.data = data %>% filter(exp %in% finished.exp)
unfinished.data = data %>% filter(!(exp %in% finished.exp))
length(unique(unfinished.data$exp))

```

None of our modeled scenarios resulted in population extinction. 
```{r pop-maintenance_2, eval=FALSE, message=FALSE, warning=FALSE, include=FALSE}
lapply((unfinished.data %>% 
          select_at(c("exp", parameters)) %>% 
          distinct())[,parameters], table)
```

```{r filter-out-unsuccessful-runs, echo=TRUE, message=FALSE, warning=FALSE}
data = data %>% filter(exp %in% finished.exp)
```

# Population during model run

```{r population_1, echo=FALSE, fig.height=7, fig.width=8, message=FALSE, warning=FALSE, out.width='100%'}
ggplot(data) +
  geom_smooth(aes(y = pop.dens, x = ticks, group = exp, color = `burn-cost`), 
              alpha = 0.01, size = 0.05) +
  geom_smooth(aes(x = ticks, y = pop.dens), color = "black", se = T) +
  facet_grid(`burn-cost` ~ `cycle-duration`+`veg-cycle-start`, 
             labeller = label_both, scale = "free") +
  scale_color_brewer(palette = "Set2",
                     labels = c("no disturbance cost (0)", 
                                "low disturbance cost (100)", 
                                "medium disturbance cost (200)", 
                                "high disturbance cost (300)")) +
  theme(legend.position = "bottom")
```

Population increases over time. There are fluctuations in population based on the climatic condition of the model, with steep drops in population when the landscape is unproductive. However, the overall trend of population increase is evident across all modeled scenarios.

We looked at linear rates of changes within each climate period of the model to get a more detailed understanding of population change during model run. 

```{r population-change-over-time_1, message=FALSE, warning=FALSE, include=FALSE}
rates <- readRDS("../results/outputs/output-evolution-comparison.rds")

rates = rates %>% left_join(data %>% select_at(c("exp", parameters)), 
                            by = "exp", multiple = "first")
rates[,4:28] <- lapply(rates[,4:28], as.numeric)

tick.seq1 = seq(from = 0, to = 3500, by = 100)
tick.levels = c()
for(i in 1:(length(tick.seq1) - 1)){
  tick.levels = c(tick.levels, paste0(tick.seq1[i] + 1, "-", tick.seq1[i+1]))
}
tick.seq2 = seq(from = 0, to = 3500, by = 250)
for(i in 1:(length(tick.seq2) - 1)){
  tick.levels = c(tick.levels, paste0(tick.seq2[i] + 1, "-", tick.seq2[i+1]))
}
rates$tick.range = factor(rates$tick.range, levels = tick.levels)

rm(list = c("tick.seq1", "tick.seq2", "tick.levels"))
```


```{r population-change-over-time_2, echo=TRUE, fig.height=5, fig.width=8, message=FALSE, warning=FALSE, out.width='100%'}
ggplot(rates %>% filter(`veg-cycle-start` == "\"productive\"")) +
  geom_boxplot(aes(x = tick.range, y = pop.dens.slope, 
                   color = climate.condition)) +
  facet_wrap(~ `cycle-duration`, scales = "free") +
  geom_hline(aes(yintercept = 0), color = "black") +
  scale_color_brewer(palette = "Set2") +
  theme(legend.position = "bottom", axis.text.x = element_text(angle = 45))

```
We find that with short climate cycles, unproductive periods see essentially no change in population, with slopes being essentially zero. With longer climatic cycles, there is slight positive population change during unproductive periods at the beginning of model run. 

Conversely, there is pretty consistent population growth during productive periods of the model until populations reach an equilibrium around 3000 ticks. The results show that population grows more quickly during productive periods at the beginning of model run, with rates of change decreasing toward zero by the end of the model. This demonstrates the effect of a carrying capacity in the model.

We can investigate this carrying capacity by looking at how many patches on the landscape are available to be foraged during a given time interval and how this is related to the change in population density over that same interval.

```{r pop-dens-forageable_1, echo=FALSE, fig.height=8, fig.width=8, message=FALSE, warning=FALSE, out.width='100%'}
ggplot(rates %>% 
         filter(`veg-cycle-start` == "\"productive\"") %>% 
         filter(`cycle-duration` == "100")) +
  geom_point(aes(x = pop.dens.slope, y = average.prop.unforageable, 
                 color = climate.condition)) +
  geom_smooth(aes(x = pop.dens.slope, y = average.prop.unforageable), 
              method = "lm") +
  geom_vline(aes(xintercept = 0), color = "black") +
  geom_hline(aes(yintercept = 1), color = "black") +
  stat_cor(mapping = aes(x = pop.dens.slope, y = average.prop.unforageable), 
           method = "pearson", p.accuracy = 0.01, r.accuracy = 0.01, 
           size = 2.5) +
  facet_wrap(~ tick.range, scales = "free") +
  scale_color_brewer(palette = "Set2") +
  theme(axis.text = element_text(size = 6), legend.position = "bottom", 
        strip.text = element_text(size = 7))

```
We can see that, with short environmental intervals, change in population density over a climatic interval is highly correlated with the proportion of patches that cannot be foraged, indicating that population is indeed controlled by access to energy.

Interestingly, we see opposite correlations for productive vs unproductive climatic windows. During productive periods, there will be population growth (positive slopes) with more forageable land (low proportions of unforageable patches). Conversely, during unproductive periods, there is more frequently population decline and this is strongly associated with lower proportions of unforageable land. This perhaps simply captures the fact that population decline allows for more land to be left unforaged, so smaller proportions of unforageable land, during a climatic interval. When more of the landscape is unforageable (higher proportions), we see a pattern of population stagnation in unproductive climatic intervals because there is not enough energy to allow for growth. 

```{r pop-dens-forageable_2, echo=FALSE, fig.height=8, fig.width=8, message=FALSE, warning=FALSE, out.width='100%'}
ggplot(rates %>% 
         filter(`veg-cycle-start` == "\"productive\"") %>% 
         filter(`cycle-duration` == "250")) +
  geom_point(aes(x = pop.dens.slope, y = average.prop.unforageable, 
                 color = climate.condition)) +
  geom_smooth(aes(x = pop.dens.slope, y = average.prop.unforageable), 
              method = "lm") +
  geom_vline(aes(xintercept = 0), color = "black") +
  geom_hline(aes(yintercept = 1), color = "black") +
  stat_cor(mapping = aes(x = pop.dens.slope, y = average.prop.unforageable), 
           method = "pearson", p.accuracy = 0.01, r.accuracy = 0.01, 
           size = 3.5) +
  facet_wrap(~ tick.range, scales = "free") +
  scale_color_brewer(palette = "Set2") +
  theme(axis.text = element_text(size = 6), legend.position = "bottom", 
        strip.text = element_text(size = 7))

```
When climatic periods are longer, the significant and strong relationship between change in population density and proportions of unforageable patches is reduced or disappears in productive periods until the end of model run. This suggests that with longer climatic cycling, a different aspect of the environment is controlling population density initially.

```{r pop-density-correlations_1, echo=TRUE, message=FALSE, warning=FALSE, out.width='100%'}
outputs = c(
  "pop.dens", #pop count/world size
  "pop.dens.slope",
  #"burnt", 
  "veg_7", 
  "veg_6", 
  "veg_5"
)

data.mid = data %>% dplyr::filter(`cycle-duration`== 250) %>% 
  dplyr::filter(`veg-cycle-start` == "\"productive\"") %>%
  dplyr::filter(ticks > 1500 & ticks <= 1750) %>% 
  group_by(exp) %>%
  summarize(pop.dens = mean(pop.dens), 
            burnt = mean(burnt),
            veg_7 = mean(veg_7), 
            veg_6 = mean(veg_6), 
            veg_5 = mean(veg_5)) %>%
  left_join(rates %>% 
              dplyr::filter(tick.range == "1501-1750") %>% 
              dplyr::filter(`veg-cycle-start` == "\"productive\"") %>% 
              dplyr::select(exp, pop.dens.slope), 
            by = c("exp"))

pvalue.mid = psych::corr.test(data.mid %>% select_at(outputs))$p
corrplot::corrplot(cor(data.mid %>% select_at(outputs), 
                       use = "pairwise.complete.obs"),
                   method = "square", addCoef.col = "black", 
                   col = scales::alpha(corrplot::COL2("RdBu"), alpha = 0.85),
                   p.mat = pvalue.mid, insig="blank", sig.level=0.1, 
                   type = "lower", number.cex = 0.5, diag=F)


rm(list = c("data.mid", "pvalue.mid"))
```
When we look at the correlations between the slope of change in population density for a middle productive period in model runs with longer climatic cycles, we see a significant positive correlation with proportions of high vegetation types (that is patches that produce more resources). This suggests that, even if most of the landscape cannot be foraged, access to a few high value patches is enough to allow for population growth. If forageable patches have lower resource values, then populations will not grow.  


# Forager probability of burning patches

We examined the effects of all model parameters on burning probability across model run using linear regressions. We model the effect of the different parameter settings on model behavior. We also model change over model run by including "ticks" as a independent variable. Finally, we investigate the interaction between time and model parameters.

```{r burning-probability-regression, echo=TRUE, message=FALSE, warning=FALSE, out.width='100%', fig.height=4}
hist(data$mean.burn.prob)

mbp.fit1 = lm(mean.burn.prob ~ ticks + (.), data = data %>% dplyr::select_at(c("mean.burn.prob", "ticks", parameters)))
mbp.fit2 = lm(mean.burn.prob ~ ticks:(.), data = data %>% dplyr::select_at(c("mean.burn.prob", "ticks", parameters)))
mbp.fit3 = lm(mean.burn.prob ~ ticks*(.), data = data %>% dplyr::select_at(c("mean.burn.prob", "ticks", parameters)))

anova(mbp.fit1, mbp.fit2, mbp.fit3)
rm(list = c("mbp.fit1", "mbp.fit2"))

plot(mbp.fit3, which = 2)

plot_summs(mbp.fit3, scale = T)
```

Every parameter significantly affects burning probability on average across model run (independent variables) as well as how burning probability changes during model run (interaction variables). The scaled regression variables shown above also demonstrate that *burn-cost* has the strongest effect on the evolution of burning probability across model run.

```{r burning-probability-regression_2, echo=FALSE, message=FALSE, warning=FALSE, out.width='100%', fig.height=3}

ggarrange(
  ggeffects::ggpredict(mbp.fit3, terms = c("ticks", "burnt-neighbor-limit")) 
  %>%
    plot(show_data = FALSE, show_ci = FALSE) +
    theme(legend.title = element_text(size = 6), 
          title = element_text(size = 8), 
          axis.title = element_text(size = 6)), 
  ggeffects::ggpredict(mbp.fit3, terms = c("ticks", "burn-veg-type-threshold")) 
  %>%
    plot(show_data = FALSE, show_ci = FALSE) +
    theme(legend.title = element_text(size = 6), 
          title = element_text(size = 8), 
          axis.title = element_text(size = 6)), 
  ggeffects::ggpredict(mbp.fit3, terms = c("ticks", "burn-cost")) %>%
    plot(show_data = FALSE, show_ci = FALSE) +
    theme(legend.title = element_text(size = 6), 
          title = element_text(size = 8), 
          axis.title = element_text(size = 6)), 
  nrow = 1, legend = "bottom"
)

rm(list = c("mbp.fit3"))
```

In general, parameters that add limits to burning behaviors (*burn-cost*, *burnt-neighbor-limit*, *burn-veg-type-threshold*) reduce the rate of increase of burning probabilities through model run. The increase of burning probabilities during model run is also faster when agents move randomly.

This model behavior is confirmed by looking at the effects of model parameters on slope of the linear relationship between ticks and burning probability.

```{r rate-of-bp-increase, echo=TRUE, message=FALSE, warning=FALSE, fig.height=6, out.width='100%'}
bp.rates = data.frame(
  exp = character(0), 
  slope = numeric(0)
)
experiments = unique(data$exp)
for(x in experiments) {
  lmdata = data %>% filter(exp == x)
  fit = lm(mean.burn.prob ~ ticks, data = lmdata)
  bp.rates[nrow(bp.rates) + 1, ] <- c(x, summary(fit)$coefficients[2,1])
}
bp.rates = bp.rates %>% left_join(data %>% select_at(c("exp", parameters)), 
                                  by = "exp", multiple = "first")
bp.rates$slope = as.numeric(bp.rates$slope)

bp.rates[,parameters] = lapply(bp.rates[,parameters], as.factor)
bp.rates$`veg-distribution` = factor(bp.rates$`veg-distribution`, 
                                     levels = c("\"random\"", 
                                                "\"clustered\""))
bp.rates$`movement-model` = factor(bp.rates$`movement-model`, 
                                   levels = c("\"Random Walk\"", 
                                              "\"Directed Walk\""))

length(unique((bp.rates %>% filter(slope < 0))$exp))/length(unique(bp.rates$exp))

neg.bprate = bp.rates %>% filter(slope < 0) %>% select_at(c(parameters)) %>% 
  distinct()
table(neg.bprate$`burn-cost`)

rm(list = c("neg.bprate"))
```

Approximately 12% of all model runs result in a decreasing rate of change in burning probabilities. These occur when burning costs are 300, greater than the benefit gained from burning.

```{r rate-of-bp-increase_1-5, echo=TRUE, message=FALSE, warning=FALSE, fig.height=6, out.width='100%'}
rate.fit1= lm(slope ~ ., data = bp.rates %>% 
                select_at(c("slope", parameters)))
rate.fit2 = lm(slope ~ .:., data = bp.rates %>% 
                 select_at(c("slope", parameters)))
anova(rate.fit1, rate.fit2)

plot(rate.fit2, which = 2)

rate.fit.df = rate.fit2 %>% broom::tidy() %>%
  mutate(p.signif = ifelse(p.value < 0.05, TRUE, FALSE)) %>%
  filter(p.signif == F)

plot_summs(rate.fit2, scale = T, 
           omit.coefs = c("(Intercept)", rate.fit.df$term))

rm(list = c("rate.fit1", "rate.fit2"))
```

The parameters that have the strongest positive impacts on the rate of change of burning behaviors are those that control the limits and costs of burning. Increased burning cost always decreases the rate of change, even when interacting with other variables. Increased burning costs have more negative effects when burning behaviors are less restricted by where foragers can perform burning behaviors, likely because more burning opportunities leads to greater accrued costs. However, when burning behaviors are less restricted without a burning cost, this allows burning probabilities to increase more quickly. 

Positive selection for burning behaviors across most of the model runs occurs because there is a consistent low benefit to self of these behaviors. Here, we measure benefit to self as the number of times an agent forages from a patch where they were the last agent to burn it as a proportion of the average total number of foraging events at each tick. 

```{r bp-and-other-outputs_1, echo=TRUE, fig.height=6, message=FALSE, warning=FALSE, out.width='100%'}
ggplot(data %>% filter(ticks > 0)) +
  geom_smooth(aes(x = ticks, y = bself.prop, group = exp, 
                  color = as.factor(`burn-cost`)), 
              alpha = 0.01, linewidth = 0.05) +
  geom_smooth(aes(x = ticks, y = bself.prop), se = F, color = "black") +
  scale_color_brewer(palette = "Set2",
                     labels = c("no burn cost (0)", 
                                "low burn cost (100)", 
                                "high burn cost (200)", 
                                "highest burn cost (300)")) +
  geom_hline(yintercept = 0, linetype = "dotted") +
  facet_grid(`cycle-duration` + `veg-cycle-start` ~ `burn-cost`, 
             labeller = labeller(`burn-cost` = bc.labs, 
                                `cycle-duration` = cycle.labs, 
                                `veg-cycle-start` = start.labs)) +
  labs(y = "proportion of burning benefits for self", 
       x = "ticks", 
       color = "cost of burning") +
  theme(legend.position = "none", axis.title = element_text(size = 8), 
        strip.text = element_text(size = 6))

```

Benefit to self consistently occurs at low levels across model run for most parameter settings, resulting in the evolution of increased burning behaviors.  

```{r bp-and-other-outputs_2, echo=FALSE, fig.height=4, message=FALSE, warning=FALSE, out.width='100%'}
ggplot(rates %>% filter(`veg-cycle-start` == "\"productive\"")) +
  geom_boxplot(aes(x = tick.range, y = start.bself, 
                   color = climate.condition)) +
  facet_wrap(~ `cycle-duration`, scales = "free", labeller = label_both) +
  geom_hline(aes(yintercept = 0), color = "black") +
  scale_color_brewer(palette = "Set2") +
  theme(legend.position = "bottom", axis.text.x = element_text(angle = 45))

```

Across model run, we see higher proportions of self benefit during foraging during unproductive periods, in part due to reduced population density in these climatic intervals.

```{r bp-and-other-outputs_3, echo=TRUE, fig.height=4, message=FALSE, warning=FALSE, out.width='100%'}
fit1 = lmer(end.bself ~ start.steps 
            + average.prop.unforageable 
            + start.pop.density 
            + (1 | tick.range), 
            data = rates %>% 
              filter(`veg-cycle-start` == "\"productive\"") %>% 
              filter(`cycle-duration` == "100") %>% 
              filter(climate.condition == "productive"))
fit2 = lmer(end.bself ~ start.steps 
            + average.prop.unforageable 
            + start.pop.density 
            + start.steps 
            + (1 | tick.range), 
            data = rates %>% 
              filter(`veg-cycle-start` == "\"productive\"") %>% 
              filter(`cycle-duration` == "100") %>% 
              filter(climate.condition == "unproductive"))

plot_summs(fit1, fit2, scale = T, 
           model.names = c("productive intervals", "unproductive intervals"))

```

This self benefit is significantly affected by forager mobility, population density, and proportion of unforageable land, as these will impact the number of patches agents have access to for foraging.  

```{r bp-and-other-outputs_4, echo=TRUE, fig.height=8, fig.width=8, message=FALSE, warning=FALSE, out.width='100%'}
ggplot(rates %>% 
         filter(`veg-cycle-start` == "\"productive\"") %>% 
         filter(`cycle-duration` == "100")) +
  geom_point(aes(x = end.burn.prob, y = end.bself, color = climate.condition)) +
  geom_smooth(aes(x = end.burn.prob, y = end.bself), method = "lm") +
  stat_cor(mapping = aes(x = end.burn.prob, y = end.bself), 
           method = "pearson", p.accuracy = 0.01, r.accuracy = 0.01, 
           size = 2.5) +
  facet_wrap(~ tick.range, scales = "free") +
  scale_color_brewer(palette = "Set2") +
  theme(legend.position = "bottom") +
  theme(axis.text = element_text(size = 6), 
        legend.position = "bottom", 
        strip.text = element_text(size = 7))

```

When looking at how self benefit relates to burning probabilities within climatic intervals, these outputs are fairly strongly correlated at the beginning of model run. We can also see that, within each climatic interval, low burning probabilities cluster very tightly with low proportions of self benefit. This supports the claim that benefit to self drives positive selection for this behavior.

```{r bp-and-other-outputs_5, echo=TRUE, fig.height=8, fig.width=8, message=FALSE, warning=FALSE, out.width='100%'}
ggplot(rates %>% 
         filter(`veg-cycle-start` == "\"productive\"") %>% 
         filter(`cycle-duration` == "100")) +
  geom_point(aes(x = end.burn.prob, y = end.bother, 
                 color = climate.condition)) +
  geom_smooth(aes(x = end.burn.prob, y = end.bother), method = "lm") +
  stat_cor(mapping = aes(x = end.burn.prob, y = end.bother), 
           method = "pearson", p.accuracy = 0.01, r.accuracy = 0.01, 
           size = 2.5) +
  facet_wrap(~ tick.range, scales = "free") +
  scale_color_brewer(palette = "Set2")  +
  theme(legend.position = "bottom") +
  theme(axis.text = element_text(size = 6), 
        legend.position = "bottom", 
        strip.text = element_text(size = 7))

```

By the end of model run, burning probabilities are more highly positively correlated with benefit to others, meaning that the highest probabilities of burning behaviors occur when agents besides the one that burned a patch are benefiting from the increased resource productivity. This suggests that there is a the collective benefit of burning allows for further positive selection of this behavior. 

## Positive evolution of burning behaviors with high burning costs
One interesting model result is the evolution of high probabilities of burning under conditions where this behavior has a high cost - that is a cost that outweighs the energetic benefits gained. 

```{r high-cost-burning_1, echo=FALSE, fig.height=4, fig.width=6, message=FALSE, warning=FALSE, out.width='100%'}

high.burn = data %>% filter(`burn-cost` == 300)

ggplot(high.burn) +
  geom_smooth(aes(x = ticks, y = mean.burn.prob, group = exp, 
                  color = as.factor(`burn-cost`)), 
              alpha = 0.01, linewidth = 0.05, method = "lm") +
  geom_smooth(aes(x = ticks, y = mean.burn.prob), se = F, color = "black") +
  geom_hline(yintercept = 0, linetype = "dotted")

bprate.300 = bp.rates %>% filter(`burn-cost` == 300)
#nrow(bprate.300 %>% filter(slope > 0)) / nrow(bprate.300)
nrow(bprate.300 %>% filter(slope < 0)) / nrow(bprate.300)

```

Around 49% of these high cost scenarios result in decreasing probabilities of burning behaviors. 

```{r high-cost-burning_2, echo=TRUE, fig.height=3, fig.width=5, message=FALSE, warning=FALSE, out.width='100%'}
#hist((high.burn %>% filter(ticks == 3500))$mean.burn.prob)

ggplot(high.burn %>% filter(ticks == 3500)) +
  geom_density(aes(x = mean.burn.prob)) +
  facet_wrap(~ `movement-model`, labeller = label_both)
```

This bimodal distribution in final burning probability appears to be primarily related to the movement model that agents employ. Under random walks, agents are more likely to develop increased burning probabilities. Under directed walks, the high cost of burning keeps burning probabilities low or even negative. This is likely because the targeting of high yield patches allows agents to access enough energy without needing to engage in high cost behaviors. When agents have to rely on randomly encountering high value patches, it is more useful to put energy into creating an environment with more high value patches through burning behaviors. 

# Burnt landscape proportions

Initial correlations reveal that the proportion of burnt landscape is significantly highly correlated with population density and the average burning probability of agents.

```{r burnt-landscape-proportions_plots, echo=FALSE, message=FALSE, warning=FALSE, out.width='100%', fig.height=4}
data$burnt = data$`veg_-1`

ggarrange(
  ggplot(data) +
    geom_point(aes(x = pop.dens, y = burnt, color = ticks)),
  ggplot(data) +
    geom_point(aes(x = mean.burn.prob, y = burnt, color = ticks)),
  nrow = 1, legend = "bottom", common.legend = T
)

```

```{r veg_0-regressions_1, eval=FALSE, fig.height=4, message=FALSE, warning=FALSE, include=FALSE, out.width="100%"}
ggplot(data) +
  geom_density(aes(x = burnt, color = `burn-cost`)) +
  ggokabeito::scale_color_okabe_ito() +
  facet_grid(`burn-cost` ~ `burnt-neighbor-limit`)
```

We used regressions on the proportions of burnt landscape to look at the effects of each parameter. We compared Beta regression and logistic regressions, which are often used for modeling proportion data, and linear regressions using AIC.

```{r veg_0-regressions_2, out.width = '100%', fig.height=4, echo=TRUE, message=FALSE, warning=FALSE}
beta.data = data %>% 
  mutate(burnt = ifelse(burnt == 0, burnt + 0.00001, burnt)) %>% 
  mutate(burnt = ifelse(burnt == 1, burnt - 0.00001, burnt))

beta.fit1 = betareg(burnt ~ ticks*(ticks + `cycle-duration` + 
                                     `veg-cycle-start` + 
                                     `veg-distribution` + 
                                     `burn-cost` + 
                                     `burn-veg-type-threshold` +  
                                     `burnt-neighbor-limit` + 
                                     `movement-model`), 
                    data = beta.data %>% 
                      select_at(c("ticks", "burnt", parameters)))

log.fit1 = glm(burnt ~ ticks*(ticks + `cycle-duration` + 
                                `veg-cycle-start` + 
                                `veg-distribution` + 
                                `burn-cost` + 
                                `burn-veg-type-threshold` +  
                                `burnt-neighbor-limit` + 
                                `movement-model`), 
               data = data %>% 
                 select_at(c("ticks", "burnt", parameters)), 
               family = binomial)

lin.fit1 = lm(burnt ~ ticks*(ticks + `cycle-duration` + 
                               `veg-cycle-start` +
                               `veg-distribution` +
                               `burn-cost` +
                               `burn-veg-type-threshold` +
                               `burnt-neighbor-limit` + 
                               `movement-model`), 
              data = data %>% select_at(c("ticks", "burnt", parameters)))

AIC(beta.fit1)
AIC(log.fit1)
AIC(lin.fit1)

AIC(beta.fit1) < AIC(lin.fit1)

```
Comparison of AIC shows that the Beta regression performs best.

```{r veg_0-regressions_3, echo=FALSE, fig.height=6, message=FALSE, warning=FALSE, out.width='100%'}
ggarrange(
  # ggeffects::ggpredict(beta.fit1, terms = c("ticks", "natural-ignition")) %>%
  #   plot(show_data = FALSE, show_ci = FALSE) +
  #   theme(legend.title = element_text(size = 5), 
  # legend.text = element_text(size = 6), 
  # title = element_text(size = 6), 
  # axis.title = element_text(size = 5)),
  ggeffects::ggpredict(beta.fit1, terms = c("ticks", "cycle-duration")) %>%
    plot(show_data = FALSE, show_ci = FALSE) +
    theme(legend.title = element_text(size = 5), 
          legend.text = element_text(size = 6), 
          title = element_text(size = 6), 
          axis.title = element_text(size = 5)),
  ggeffects::ggpredict(beta.fit1, terms = c("ticks", "veg-cycle-start")) %>%
    plot(show_data = FALSE, show_ci = FALSE) +
    theme(legend.title = element_text(size = 5), 
          legend.text = element_text(size = 6), 
          title = element_text(size = 6), 
          axis.title = element_text(size = 5)),
  ggeffects::ggpredict(beta.fit1, terms = c("ticks", "burn-veg-type-threshold")) %>%
    plot(show_data = FALSE, show_ci = FALSE) +
    theme(legend.title = element_text(size = 5), 
          legend.text = element_text(size = 6), 
          title = element_text(size = 6), 
          axis.title = element_text(size = 5)),
  ggeffects::ggpredict(beta.fit1, terms = c("ticks", "burnt-neighbor-limit")) %>%
    plot(show_data = FALSE, show_ci = FALSE) +
    theme(legend.title = element_text(size = 5), 
          legend.text = element_text(size = 6), 
          title = element_text(size = 6), 
          axis.title = element_text(size = 5)),
  ggeffects::ggpredict(beta.fit1, terms = c("ticks", "burn-cost")) %>%
    plot(show_data = FALSE, show_ci = FALSE) +
    theme(legend.title = element_text(size = 5), 
          legend.text = element_text(size = 6), 
          title = element_text(size = 6), 
          axis.title = element_text(size = 5)),
  ggeffects::ggpredict(beta.fit1, terms = c("ticks", "movement-model")) %>%
    plot(show_data = FALSE, show_ci = FALSE) +
    theme(legend.title = element_text(size = 5), 
          legend.text = element_text(size = 6), 
          title = element_text(size = 6), 
          axis.title = element_text(size = 5)),
  ggeffects::ggpredict(beta.fit1, terms = c("ticks", "veg-distribution")) %>%
    plot(show_data = FALSE, show_ci = FALSE) +
    theme(legend.title = element_text(size = 5), 
          legend.text = element_text(size = 6), 
          title = element_text(size = 6), 
          axis.title = element_text(size = 5)),
  legend = "bottom"
)

```

The predicted proportions of burnt landscape from the best fit Beta regression model show that increasing limits on location of burning or increasing cost to burning significantly affect the amount of burnt landscape. This matches the results above for the effect of these parameters on mean burning probability. This is also consistent with the high positive correlation between proportion of burnt landscape and burning probability through time. 

# Spatial clustering of vegetation types

Spatial clustering (and its converse spatial heterogeneity) of vegetation types is assessed via Moran's I values. We limit our analysis to those significant values of Moran's I to assess the degree of clustering (positive values) or dispersion (negative values). We assessed the effects of the different parameters using linear regressions.

```{r morans-i-regression_1, echo=TRUE, fig.height=4, fig.width=8, message=FALSE, warning=FALSE, out.width="100%"}
veg.100.prod = readRDS("../results/outputs/veg_moransi_100-prod.rds")
veg.100.unprod = readRDS("../results/outputs/veg_moransi_100-unprod.rds")
veg.250.prod = readRDS("../results/outputs/veg_moransi_250-prod.rds")
veg.250.unprod = readRDS("../results/outputs/veg_moransi_250-unprod.rds")

veg.100.prod = veg.100.prod %>% 
  filter(exp %in% finished.exp)
veg.100.unprod = veg.100.unprod %>% 
  filter(exp %in% finished.exp)
veg.250.prod = veg.250.prod %>% 
  filter(exp %in% finished.exp)
veg.250.unprod = veg.250.unprod %>% 
  filter(exp %in% finished.exp)

veg.100.prod = veg.100.prod %>% 
  filter(ticks != 1000) %>% filter(ticks != 2000)
veg.100.unprod = veg.100.unprod %>% 
  filter(ticks != 1000) %>% filter(ticks != 2000)
veg.250.prod = veg.250.prod %>% 
  filter(ticks != 1000) %>% filter(ticks != 2000)
veg.250.unprod = veg.250.unprod %>% 
  filter(ticks != 1000) %>% filter(ticks != 2000)

parameters = c(
  "cycle_duration",  # 100, 250
  "veg_cycle_start", # productive, unproductive
  "veg_distribution", # random, clustered
  "burnt_neighbor_limit", # 1, 4, 8
  "burn_cost", # 0, 50
  "burn_veg_type_threshold", # 4, 7
  "movement_model" #Random, Directed
)

reg.params = parameters[c(3:7)]
veg.100.prod[,reg.params] = lapply(veg.100.prod[,reg.params], as.factor)
veg.100.unprod[,reg.params] = lapply(veg.100.unprod[,reg.params] , as.factor)
veg.250.prod[,reg.params] = lapply(veg.250.prod[,reg.params], as.factor)
veg.250.unprod[,reg.params] = lapply(veg.250.unprod[,reg.params] , as.factor)

veg.100.prod$veg_distribution = factor(veg.100.prod$veg_distribution, 
                                       levels = c("\"random\"", 
                                                  "\"clustered\""))
veg.100.unprod$veg_distribution = factor(veg.100.unprod$veg_distribution, 
                                         levels = c("\"random\"", 
                                                    "\"clustered\""))
veg.250.prod$veg_distribution = factor(veg.250.prod$veg_distribution, 
                                       levels = c("\"random\"", 
                                                  "\"clustered\""))
veg.250.unprod$veg_distribution = factor(veg.250.unprod$veg_distribution, 
                                         levels = c("\"random\"", 
                                                    "\"clustered\""))

veg.100.prod$movement_model = factor(veg.100.prod$movement_model, 
                                     levels = c("\"Random Walk\"", 
                                                "\"Directed Walk\""))
veg.100.unprod$movement_model = factor(veg.100.unprod$movement_model, 
                                       levels = c("\"Random Walk\"",
                                                  "\"Directed Walk\""))
veg.250.prod$movement_model = factor(veg.250.prod$movement_model, 
                                     levels = c("\"Random Walk\"", 
                                                "\"Directed Walk\""))
veg.250.unprod$movement_model = factor(veg.250.unprod$movement_model, 
                                       levels = c("\"Random Walk\"", 
                                                  "\"Directed Walk\""))

# hist(veg.100.prod$morans.i)
# hist(veg.100.unprod$morans.i)
# hist(veg.250.prod$morans.i)
# hist(veg.250.unprod$morans.i)

veg.100.prod.fit1 = lm(morans.i ~ ticks*(.), 
                       data = veg.100.prod %>% 
                         filter(signif == T) %>% 
                         select_at(c("ticks", "morans.i", reg.params)))

veg.100.unprod.fit1 = lm(morans.i ~ ticks*(.), 
                         data = veg.100.unprod %>% 
                           filter(signif == T) %>% 
                           select_at(c("ticks", "morans.i", reg.params)))

veg.250.prod.fit1 = lm(morans.i ~ ticks*(.), 
                       data = veg.250.prod %>% 
                         filter(signif == T) %>% 
                         select_at(c("ticks", "morans.i", reg.params)))

veg.250.unprod.fit1 = lm(morans.i ~ ticks*(.), 
                         data = veg.250.unprod %>% 
                           filter(signif == T) %>% 
                           select_at(c("ticks", "morans.i", reg.params)))

plot(veg.100.prod.fit1, which = 2)
plot(veg.100.unprod.fit1, which = 2)
plot(veg.250.prod.fit1, which = 2)
plot(veg.250.unprod.fit1, which = 2)

plot_summs(veg.100.prod.fit1, 
           veg.100.unprod.fit1,
           veg.250.prod.fit1, 
           veg.250.unprod.fit1, 
           model.names = c(
  "start = productive, cycle = 100", 
  "start = unproductive, cycle = 100", 
  "start = productive, cycle = 250", 
  "start = unproductive, cycle = 250"
), scale = T)

```

Looking at the standardized regression coefficients, we can see that high/medium cost of burning behaviors and a directed walk movement model have the greatest impact on clustering of vegetation types. Interestingly, the underlying distribution of maximum potential vegetation types for patches has essentially no impact on spatial clustering of vegetation types relative to the other parameters. 

```{r morans-i-regression_2, echo=TRUE, fig.height=4, fig.width=8, message=FALSE, warning=FALSE,out.width="100%"}
plot_summs(veg.100.prod.fit1, veg.100.unprod.fit1,veg.250.prod.fit1, veg.250.unprod.fit1, model.names = c(
  "start = productive, cycle = 100", 
  "start = unproductive, cycle = 100", 
  "start = productive, cycle = 250", 
  "start = unproductive, cycle = 250"
), coefs = c("ticks", 
             "natural_ignition0.05", 
             "veg_distribution\"random\"", 
             "burnt_neighbor_limit4", 
             "burnt_neighbor_limit8", 
             "burn_cost100", 
             "burn_cost200", 
             "burn_cost300", 
             "burn_veg_type_threshold7", 
             "movement_model\"Directed Walk\"")) +
  theme(legend.position = "bottom", 
        legend.title = element_blank(), 
        legend.text = element_text(size = 6))

```

Comparing across individual models for the experiments split by whether the model starts in a productive or unproductive state and split by the model climatic cycle duration, we can see that most of the parameters have similar effects. The parameter with significant differences in regression coefficients between the models is: *movement-model* . We can see that when model run starts in a productive state and the climatic cycles are longer, Directed Walks allow for, on average, less spatial clustering of vegetation types.

```{r morans-i-regression_3, echo=TRUE, fig.height=6, fig.width=8, message=FALSE, warning=FALSE,out.width="100%"}
ggarrange(
  ggeffects::ggpredict(veg.100.prod.fit1, 
                       terms = c("ticks", "movement_model", "burn_cost")) %>%
    plot(show_data = FALSE, show_ci = TRUE) +
    theme(legend.title = element_text(size = 5), 
          title = element_text(size = 8), 
          axis.title = element_text(size = 6)) +
    labs(subtitle = "cycle = 100, start = productive"), 
  ggeffects::ggpredict(veg.100.unprod.fit1, 
                       terms = c("ticks", "movement_model", "burn_cost")) %>%
    plot(show_data = FALSE, show_ci = TRUE) +
    theme(legend.title = element_text(size = 6), 
          title = element_text(size = 8), 
          axis.title = element_text(size = 6)) +
    labs(subtitle = "cycle = 100, start = unproductive"), 
  ggeffects::ggpredict(veg.250.prod.fit1, 
                       terms = c("ticks", "movement_model", "burn_cost")) %>%
    plot(show_data = FALSE, show_ci = TRUE) +
    theme(legend.title = element_text(size = 6), 
          title = element_text(size = 8), 
          axis.title = element_text(size = 6)) +
    labs(subtitle = "cycle = 250, start = productive"), 
  ggeffects::ggpredict(veg.250.unprod.fit1, 
                       terms = c("ticks", "movement_model", "burn_cost")) %>%
    plot(show_data = FALSE, show_ci = TRUE) +
    theme(legend.title = element_text(size = 6), 
          title = element_text(size = 8), 
          axis.title = element_text(size = 6)) +
    labs(subtitle = "cycle = 250, start = unproductive"), 
  common.legend = T, legend = "bottom", nrow = 2, ncol = 2)

```

When we look at how vegetation clustering changes over time with different burning costs (facets) and different movement models, it is clear that directed walks result in a faster rate of decline in spatial clustering than random walks across all burning costs. When burning costs are low/none, this decrease is even steeper as more burning occurs, with spatial autocorrelation becoming more dispersed, at negative values, by the end of model run. This is consistent with above results that directed walk result in faster rates of increase in burning probabilities and more burnt patches over time.

```{r morans-i-by-burn-limits, echo=TRUE, fig.height=5, message=FALSE, warning=FALSE, out.width='100%'}
plot.data = veg.data %>% 
  filter(signif == T) %>% 
  filter(cycle_duration == 100) %>% 
  filter(veg_cycle_start == "\"productive\"")
plot.data$burn_cost = as.factor(plot.data$burn_cost)

 ggplot(plot.data) +
  geom_jitter(data = plot.data %>% filter(burn_cost == 0), 
              mapping = aes(x = ticks, y = morans.i, group = ticks, 
                            color = burn_cost), alpha = 0.1, size = 0.25) +
  geom_jitter(data = plot.data %>% filter(burn_cost == 100), 
              mapping = aes(x = ticks, y = morans.i, group = ticks, 
                            color = burn_cost), alpha = 0.1, size = 0.25) +
  geom_jitter(data = plot.data %>% filter(burn_cost == 200), 
              mapping = aes(x = ticks, y = morans.i, group = ticks, 
                            color = burn_cost), alpha = 0.1, size = 0.25) +
  geom_jitter(data = plot.data %>% filter(burn_cost == 300), 
              mapping = aes(x = ticks, y = morans.i, group = ticks, 
                            color = burn_cost), alpha = 0.1, size = 0.25) +
  geom_smooth(mapping = aes(x = ticks, y = morans.i, color = burn_cost)) +
  facet_grid(movement_model ~ burnt_neighbor_limit + burn_veg_type_threshold, 
             labeller = labeller(burnt_neighbor_limit = bn.labs,
                        burn_veg_type_threshold = bt.labs,
                        movement_model = move.labs)) +
  labs(color = "", y = "Shannon Diversity Index") +
  scale_color_brewer(palette = "Set2",
                     labels = c("no disturbance cost (0)", 
                                "low disturbance cost (100)", 
                                "medium disturbance cost (200)", 
                                "high disturbance cost (300)", 
                                "productive interval", 
                                "unproductive interval")) +
  theme(legend.position = "bottom", 
        strip.text = element_text(size = 6), 
        axis.title = element_text(size = 7.5))
```

There are also differing trends based on spatial limits and vegetation limits on burning behaviors. When patches can only be burnt with 4 or less burnt neighbors, spatial clustering of vegetation types is much more decreased, particularly for lower disturbance costs that allow for more burning. 

# Vegetation diversity

Vegetation diversity was measured by Shannon's Diversity Index. This metric considers the proportional abundances of vegetation types to indicate whether one type dominates or abundances are more evenly spread across all types. A SDI value of 0 indicates a lack of diversity with abundance being concentrated in a single species. Higher SDI values indicate more diversity of vegetation types.

```{r veg-diversity-distribution, echo=FALSE, fig.height=4, message=FALSE, warning=FALSE, out.width='100%'}
veg.data = bind_rows(veg.100.prod, veg.100.unprod, veg.250.prod, veg.250.unprod) 

hist(veg.data$shannon.div)

ggplot(veg.data) +
  geom_density(aes(x = shannon.div, color = movement_model))

```

The distribution of this metric is bimodal across model runs. This bimodality is caused by the different movement models used: directed walks result in less diversity than random walks.

We fit a GAM to vegetation type diversity for model runs with random walks because it is a better fit than a linear model. We use GAM to investigate how the effects of the parameters change through time.

```{r veg-diversity-regression_1, echo=TRUE, fig.height=3, message=FALSE, warning=FALSE, out.width='100%'}
veg.data.r = veg.data %>% filter(movement_model == "\"Random Walk\"")
reg.params = parameters = c(
  "cycle_duration",  # 100, 250
  "veg_cycle_start", # productive, unproductive
  "veg_distribution", # random, clustered
  "burnt_neighbor_limit", # 1, 4, 8
  "burn_cost", # 0, 50
  "burn_veg_type_threshold"
)
veg.data.r[,reg.params] = lapply(veg.data.r [,reg.params], as.factor)

rw.gam1 = gam(shannon.div ~ 
                #s(ticks, by = natural_ignition) + 
                s(ticks, by = veg_cycle_start) + 
                s(ticks, by = veg_distribution) + 
                s(ticks, by = burn_cost)  +  
                s(ticks, by = burn_veg_type_threshold) + 
                s(ticks, by = burnt_neighbor_limit) +
                s(ticks, by = cycle_duration), data = veg.data.r)

rw.gam2 = gam(shannon.div ~ veg_cycle_start + 
                veg_distribution + 
                burn_cost + 
                burn_veg_type_threshold + 
                burnt_neighbor_limit + 
                cycle_duration +
                #s(ticks, by = natural_ignition) + 
                s(ticks, by = veg_cycle_start) + 
                s(ticks, by = veg_distribution) + 
                s(ticks, by = burn_cost)  +  
                s(ticks, by = burn_veg_type_threshold) + 
                s(ticks, by = burnt_neighbor_limit) +
                s(ticks, by = cycle_duration), data = veg.data.r)

anova(rw.gam1, rw.gam2, test = "Chisq")

rw.fit1 = lm(shannon.div ~ ticks*(.), data = veg.data.r %>% 
               select_at(c("ticks", "shannon.div", reg.params)))

AIC(rw.gam2)
AIC(rw.fit1)

qq.gam(rw.gam2)

```

```{r veg-diversity-regression_1_3, echo=TRUE, fig.height=3, message=FALSE, warning=FALSE, out.width='100%'}
par(mfrow=c(1,2), cex=0.8)
plot(rw.gam2, select=1, shade=T)
abline(h=0, lty = 2)
plot(rw.gam2, select=2, shade=T)
abline(h=0, lty = 2)

```

The starting environmental conditions do not appear to have significantly differing effects on the evolution of vegetation diversity over model run.

```{r veg-diversity-regression_1_4, echo=TRUE, fig.height=3, message=FALSE, warning=FALSE, out.width='100%'}
par(mfrow=c(1,2), cex=0.8)
plot(rw.gam2, select=3, shade=T)
abline(h=0, lty = 2)
plot(rw.gam2, select=4, shade=T)
abline(h=0, lty = 2)

```

The underlying distribution of resource potential, or maximum vegetation type value, also do not have different effects on vegetation diversity - both distributions have slightly increasingly positive effects over the course of model run.

```{r veg-diversity-regression_1_5, echo=TRUE, fig.height=6, message=FALSE, warning=FALSE, out.width='100%'}
par(mfrow=c(2,2), cex=0.8)
plot(rw.gam2, select=5, shade=T)
abline(h=0, lty = 2)
plot(rw.gam2, select=6, shade=T)
abline(h=0, lty = 2)
plot(rw.gam2, select=7, shade=T)
abline(h=0, lty = 2)
plot(rw.gam2, select=8, shade=T)
abline(h=0, lty = 2)
```

Having a cost associated with burning introduces a larger effect on vegetation diversity than no or low costs of burning. This is likely related to the fact that a burning cost reduces the amount of burning over the course of model run, allowing for a landscape that is not dominated by burnt patches.

```{r veg-diversity-regression_1_6, echo=TRUE, fig.height=3, message=FALSE, warning=FALSE, out.width='100%'}
par(mfrow=c(1,2), cex=0.8)
plot(rw.gam2, select=9, shade=T)
abline(h=0, lty = 2)
plot(rw.gam2, select=10, shade=T)
abline(h=0, lty = 2)
```

Similarly, stricter limits on what types of vegetation can be burned also allows for more vegetation diversity by the end of model run.

```{r veg-diversity-regression_1_7, echo=TRUE, fig.height=3, message=FALSE, warning=FALSE, out.width='100%'}
par(mfrow=c(1,3), cex=0.8)
plot(rw.gam2, select=11, shade=T)
abline(h=0, lty = 2)
plot(rw.gam2, select=12, shade=T)
abline(h=0, lty = 2)
plot(rw.gam2, select=13, shade=T)
abline(h=0, lty = 2)
```

This same pattern is seen even more distinctly with the stricter burnt neighbor limits. When agents can burn patches with 8 burnt neighbors, vegetation diversity declines much more by the end of model run as the number of burnt patches increases.

```{r veg-diversity-regression_1_8, echo=TRUE, fig.height=3, message=FALSE, warning=FALSE, out.width='100%'}
par(mfrow=c(1,2), cex=0.8)
plot(rw.gam2, select=14, shade=T)
abline(h=0, lty = 2)
plot(rw.gam2, select=15, shade=T)
abline(h=0, lty = 2)
```

Both values of cycle duration have similar effects.

We fit a second GAM to vegetation type diversity for model runs with directed walks.

```{r veg-diversity-regression_2, echo=TRUE, fig.height=3, message=FALSE, warning=FALSE, out.width='100%'}
veg.data.d = veg.data %>% filter(movement_model == "\"Directed Walk\"")
reg.params = parameters = c(
  "cycle_duration",  # 100, 250
  "veg_cycle_start", # productive, unproductive
  "veg_distribution", # random, clustered
  "burnt_neighbor_limit", # 1, 4, 8
  "burn_cost", # 0, 50
  "burn_veg_type_threshold"
)
veg.data.d[,reg.params] = lapply(veg.data.d[,reg.params], as.factor)

dw.gam1 = gam(shannon.div ~ 
                #s(ticks, by = natural_ignition) + 
                s(ticks, by = veg_cycle_start) + 
                s(ticks, by = veg_distribution) + 
                s(ticks, by = burn_cost)  +  
                s(ticks, by = burn_veg_type_threshold) + 
                s(ticks, by = as.factor(burnt_neighbor_limit)) +
                s(ticks, by = cycle_duration), data = veg.data.d)

dw.gam2 = gam(shannon.div ~ veg_cycle_start + veg_distribution + burn_cost + burn_veg_type_threshold + burnt_neighbor_limit + cycle_duration +
                #s(ticks, by = natural_ignition) + 
                s(ticks, by = veg_cycle_start) + 
                s(ticks, by = veg_distribution) + 
                s(ticks, by = burn_cost)  +  
                s(ticks, by = burn_veg_type_threshold) + 
                s(ticks, by = burnt_neighbor_limit) +
                s(ticks, by = cycle_duration), data = veg.data.d)

anova(dw.gam1, dw.gam2, test = "Chisq")

dw.fit1 = lm(shannon.div ~ ticks*(.), data = veg.data.d %>% select_at(c("ticks", "shannon.div", reg.params)))

AIC(dw.gam2)
AIC(dw.fit1)

qq.gam(dw.gam2)

```

Overall with directed walks, we get very similar parameter effects through time for most of the parameters. There are, however, key differences in the effects of burning costs and limits to where burning can occur.


```{r veg-diversity-regression_2_3, echo=TRUE, fig.height=3, message=FALSE, warning=FALSE, out.width='100%'}
par(mfrow=c(1,2), cex=0.8)
plot(dw.gam2, select=1, shade=T)
abline(h=0, lty = 2)
plot(dw.gam2, select=2, shade=T)
abline(h=0, lty = 2)

```

We again see similar effects of both starting vegetation conditions on vegetation diversity across model run.

```{r veg-diversity-regression_2_4, echo=TRUE, fig.height=3, message=FALSE, warning=FALSE, out.width='100%'}
par(mfrow=c(1,2), cex=0.8)
plot(dw.gam2, select=3, shade=T)
abline(h=0, lty = 2)
plot(dw.gam2, select=4, shade=T)
abline(h=0, lty = 2)

```

The underlying distribution of resource potential, or maximum vegetation type value, have essentially no effect on vegetation diversity with directed walks. This means that the human behavior is more important for structuring the environment with this movement model.  

```{r veg-diversity-regression_2_5, echo=TRUE, fig.height=6, message=FALSE, warning=FALSE, out.width='100%'}
par(mfrow=c(2,2), cex=0.8)
plot(dw.gam2, select=5, shade=T)
abline(h=0, lty = 2)
plot(dw.gam2, select=6, shade=T)
abline(h=0, lty = 2)
plot(dw.gam2, select=7, shade=T)
abline(h=0, lty = 2)
plot(dw.gam2, select=8, shade=T)
abline(h=0, lty = 2)

```

With directed walks, we can see that low and medium costs for burning behaviors have similar effects: at first negative, since burning is required to introduce new vegetation types, but then becoming positive as more burning is allowed to occur. We see a similar initial pattern with no burning costs; however, by the end of model run, the huge amount of burning leads to too many burnt patches that decreases the overall diversity of vegetation on the landscape. Higher burning costs has the similar effect patterns, but a much more limited effect size. This is likely because high burning costs severely limits burning behaviors and therefore does not have a substantial impact on what vegetation types are available on the landscape. 

```{r veg-diversity-regression_2_6, echo=TRUE, fig.height=3, message=FALSE, warning=FALSE, out.width='100%'}
par(mfrow=c(1,2), cex=0.8)
plot(dw.gam2, select=9, shade=T)
abline(h=0, lty = 2)
plot(dw.gam2, select=10, shade=T)
abline(h=0, lty = 2)

par(mfrow=c(1,3), cex=0.8)
plot(dw.gam2, select=11, shade=T)
abline(h=0, lty = 2)
plot(dw.gam2, select=12, shade=T)
abline(h=0, lty = 2)
plot(dw.gam2, select=13, shade=T)
abline(h=0, lty = 2)
```

The limits on burning behaviors have more exaggerated effects with directed walks. We can again see clearly that more burning (with relaxed burning restrictions) reduces overall vegetation diversity by the end of model run.

```{r veg-diversity-regression_2_8, echo=TRUE, fig.height=3, message=FALSE, warning=FALSE, out.width='100%'}
par(mfrow=c(1,2), cex=0.8)
plot(dw.gam2, select=14, shade=T)
abline(h=0, lty = 2)
plot(dw.gam2, select=15, shade=T)
abline(h=0, lty = 2)
```

Cycle duration appears to have no effect on vegetation diversity with directed walks.

Overall, vegetation diversity is closely tied to proportion of burnt landscape and average burning probability, which are themselves primarily controlled by the restrictions and cost of burning behaviors. By the end of model run we see a strong negative correlation between these two outputs, showing that increasing burning results in less diversity due to the dominating proportion of burnt patches on the landscape when burning is very frequent.


# Spatial distribution of burning events

Because burning behaviors have such a significant impact on the structure of the vegetation in the environment, we were curious if this is caused by differential use of space. To examine this, we looked at the spatial autocorrelation of where burning events occur within the landscape to assess land use by the agents. This analysis is split *cycle-duration.* We first use linear regressions to assess how the parameters and time affect the spatial autocorrelation of burning events. For this, we only consider significant values of Moran's I to evaluate clustering (positive values) and dispersion (negative values).

```{r burning-events_1, echo=FALSE, message=FALSE, warning=FALSE, out.width="100%",fig.height=4}
parameters = c(
  "cycle_duration",  # 100, 250
  "veg_cycle_start", # productive, unproductive
  "veg_distribution", # random, clustered
  "burnt_neighbor_limit", # 1, 4, 8
  "burn_cost", # 0, 50
  "burn_veg_type_threshold", # 4, 7
  "movement_model" #Random, Directed
)

be.morans.100 <- readRDS("../results/outputs/be_morans.i_cycle.100.rds")
be.morans.100[,parameters[-1]] = lapply(be.morans.100[,parameters[-1]] , as.factor)
be.morans.250 <- readRDS("../results/outputs/be_morans.i_cycle.250.rds")
be.morans.250[,parameters[-1]] = lapply(be.morans.250[,parameters[-1]] , as.factor)

be.morans.100$veg_distribution = factor(be.morans.100$veg_distribution, 
                                        levels = c("\"random\"", 
                                                   "\"clustered\""))
be.morans.250$veg_distribution = factor(be.morans.250$veg_distribution, 
                                        levels = c("\"random\"", 
                                                   "\"clustered\""))

be.morans.100$movement_model = factor(be.morans.100$movement_model, 
                                      levels = c("\"Random Walk\"", 
                                                 "\"Directed Walk\""))
be.morans.250$movement_model = factor(be.morans.250$movement_model, 
                                      levels = c("\"Random Walk\"", 
                                                 "\"Directed Walk\""))

be.morans.100 = be.morans.100 %>% filter(exp %in% finished.exp)
be.morans.250 = be.morans.250 %>% filter(exp %in% finished.exp)

#be.morans.100 = be.morans.100 %>% filter(ticks != 1000) %>% filter(ticks != 2000)
#be.morans.250 = be.morans.250 %>% filter(ticks != 1000) %>% filter(ticks != 2000)

# hist(be.morans.100$morans.i)
# hist(be.morans.250$morans.i)

fit1 = lm(morans.i ~ ticks*(.), data = be.morans.100 %>% 
            filter(signif == T) %>% 
            select_at(c("ticks", parameters[-1], "morans.i")))

fit2 = lm(morans.i ~ ticks*(.), data = be.morans.250 %>% 
            filter(signif == T) %>% 
            select_at(c("ticks", parameters[-1], "morans.i")))

par(mfrow = c(1,2))
plot(fit1, which = 2)
title(main = "cycle = 100 ticks")
plot(fit2, which = 2)
title(main = "cycle = 250 ticks")

fit1$coefficients[1:2]
fit2$coefficients[1:2]

```

The intercept values show that, on average, burning events are on average marginally clustered on the landscape. This spatial autocorrelation is then significantly affected by time and, on average, decreases as model run progresses. 

```{r burning-events_2_1, echo=FALSE, message=FALSE, warning=FALSE, out.width="100%"}
plot_summs(fit1, fit2, scale = T, 
           model.names = c("cycle = 100 ticks", "cycle = 250 ticks"))
```

When looking at scaled regression coefficients, we can see that underlying distribution of resource potential (maximum veg type), burning limits, and movement models have the strongest effects on the spatial clustering of burning events. These strong effects are also maintained over time, as evidence by the high standardized regression coefficients for the interaction variables between these parameters and time). Importantly, time increase the effect size of these parameters in the same direction. For example, directed walks reduce the clustering of burning events on average and this effect is more negative with time.

```{r burning-events_2_2_1, echo=TRUE, message=FALSE, warning=FALSE, out.width="100%"}

bn.labs = c("can burn with 1 burnt neighbor", 
            "can burn with 4 burnt neighbors", 
            "can burn with 8 burnt neighbors")
names(bn.labs) = c(1, 4, 8)

p1.2 = ggplot(be.morans.100 %>% filter(signif == T) %>% 
                filter(movement_model == "\"Random Walk\"")) +
  geom_point(mapping = aes(x = ticks, y = morans.i, 
                           color = as.factor(veg_distribution)), alpha = 0.1) +
  geom_smooth(mapping = aes(x = ticks, y = morans.i, 
                            color = as.factor(veg_distribution), 
                            group = as.factor(veg_distribution)), 
              method = "lm") +
  geom_hline(aes(yintercept = 0)) +
  facet_grid(burn_cost ~ burn_veg_type_threshold + burnt_neighbor_limit, 
             scales = "free", 
             labeller = labeller(burn_cost = bc.labs, 
                                 burn_veg_type_threshold = bt.labs, 
                                 burnt_neighbor_limit = bn.labs)) +
  theme(axis.text = element_text(size = 5), 
        strip.text = element_text(size = 6), 
        legend.position = "bottom")

plot(p1.2)
```

```{r burning-events_2_2_2, echo=TRUE, message=FALSE, warning=FALSE, out.width="100%"}
p2.2 = ggplot(be.morans.100 %>% filter(signif == T) %>% 
                filter(movement_model == "\"Directed Walk\"")) +
  geom_point(mapping = aes(x = ticks, y = morans.i, 
                           color = as.factor(veg_distribution)), alpha = 0.1) +
  geom_smooth(mapping = aes(x = ticks, y = morans.i, 
                            color = as.factor(veg_distribution), 
                            group = as.factor(veg_distribution)), 
              method = "lm") +
  geom_hline(aes(yintercept = 0)) +
  facet_grid(burn_cost ~ burn_veg_type_threshold + burnt_neighbor_limit, 
             scales = "free", 
             labeller = labeller(burn_cost = bc.labs, 
                                 burn_veg_type_threshold = bt.labs, 
                                 burnt_neighbor_limit = bn.labs)) +
  theme(axis.text = element_text(size = 5), 
        strip.text = element_text(size = 6), 
        legend.position = "bottom")

plot(p2.2)

```

Plotting the trends of burning event spatial autocorrelation through time by these significant parameters allows us to better visualize these patterns. Here, we split the data by movement model with trend lines for random walks in the top graph and trends for directed walks in the bottom graph. 

First, it is clear that, under random walks, underlying distribution of vegetation potential has a significant impact on clustering or disperson of burning events. This is especially true when burning is limited to specific patches (can burn with fewer burnt neighbors and can only burn certain vegetation types) under low burning costs. As burning costs increase, and burning becomes more infrequent, bunring events are more likely to cluster despite limits on which patches can be burnt. 

With directed walks, the effect of underlying vegetation potential is more varied. For example, when agents can burn any vegetation type, underlying vegetation potential does not change the trend towards spatial randomness or dispersion of burning events. When agents can only burn specific vegetation types, underlying vegetation potential is more important, particularly in cases where patches can have more burnt neighbors. In these cases, underlying clustering of vegetation type potential leads to more clustering of burning events.  

```{r be-dispersion-and-pop, echo=TRUE, fig.height=5, fig.width=5, message=FALSE, warning=FALSE, out.width='100%'}
be.data = bind_rows(be.morans.100, be.morans.250) %>% 
  filter(ticks == 3500) %>%
  left_join(data, by = c("exp", "ticks"))

ggplot(be.data %>% filter(signif == T)) +
  geom_point(aes(y = morans.i, x = pop.dens)) +
  geom_smooth(data = be.data %>% 
                filter(signif == T) %>% 
                filter(morans.i < 0), 
              aes(y = morans.i, x = pop.dens), method = "lm") +
  geom_smooth(data = be.data %>% 
                filter(signif == T) %>% 
                filter(morans.i > 0), 
              aes(y = morans.i, x = pop.dens), method = "lm")

```
Here, we can see that increased population density is clearly associated with increased dispersion of burning events at the end of model run. The correlation between clustering and population density skews positive, but the graph shows that this is less consistent at the highest population densities. 

# Forager mobility

In the model, foragers can adjust how many steps they take during a foraging bout if they determine they will meet their energy requirements with fewer steps. Movement in the model is, therefore, patterned primarily by the energy available in the gridded landscape, which is determined by whether the model is in a productive or unproductive climatic period and how long those climatic periods last.

```{r fm-viz, echo=FALSE, message=FALSE, warning=FALSE, out.width="100%"}
ggplot(data %>% filter(ticks > 0)) +
  # geom_point(aes(x = ticks, y = mean.fm, color = `movement-model`), 
  # alpha = 0.01, size = 0.1) +
  geom_smooth(aes(x = ticks, y = mean.fm, color = `movement-model`), 
              method = "gam") +
  #geom_hline(yintercept = 0, linetype = "dotted") +
  facet_grid(`cycle-duration` ~ `veg-cycle-start`, 
             labeller = label_both) +
  scale_color_colorblind(labels = c("Directed Walk", "Random Walk"))

```

We can see from the above plot that there is a decrease in movement during productive periods and an increase in movement during unproductive periods of the model. This is more smoothed when cycle duration is shorter. 

```{r fm-viz_2, echo=FALSE, message=FALSE, warning=FALSE, out.width="100%"}
ggplot(rates %>% 
         filter(`veg-cycle-start` == "\"productive\"")) +
  geom_boxplot(aes(x = tick.range, y = steps.slope, 
                   color = climate.condition)) +
  facet_grid(`movement-model`~ `cycle-duration`, 
             scales = "free", 
             labeller = label_both) +
  geom_hline(aes(yintercept = 0), color = "black") +
  scale_color_brewer(palette = "Set2") +
  theme(legend.position = "bottom", 
        axis.text.x = element_text(angle = 45))

```
When we break this down by climatic interval, we can see that most of the change to mobility occurs during productive intervals. Interestingly, across these productive intervals, it primarily at the beginning of model run when mobility decreases across the interval. By the end of model run, there is actually a slight increase in mobility across the climatic interval.

```{r fm-viz_3, echo=FALSE, message=FALSE, warning=FALSE, out.width="100%"}
ggplot(rates %>% 
         filter(`veg-cycle-start` == "\"productive\"")) +
  geom_boxplot(aes(x = tick.range, y = start.steps, 
                   color = climate.condition)) +
  facet_grid(`movement-model`~ `cycle-duration`, 
             scales = "free", 
             labeller = label_both) +
  scale_color_brewer(palette = "Set2") +
  theme(legend.position = "bottom", 
        axis.text.x = element_text(angle = 45))

```

The overall decrease in mobility across model run is therefore primarily caused by steep dips in mobility at the beginning of each productive interval. 

To understand how model parameters affected forager mobility, we first chose to investigate average steps per foraging bout as a linear trend to understand overall evolution during model run. Using mixed linear models, we can see how the other parameters affect forager movement while controlling for starting vegetation state to deal with the model end effects seen above.

```{r fm-mm-regs, echo=TRUE, fig.height=3, message=FALSE, warning=FALSE, out.width="100%"}
mm.fit1.1 = lmer(mean.fm ~ ticks + (1 | `veg-cycle-start`), data = data)

mm.fit1.2 = lmer(mean.fm ~ ticks + 
                   `movement-model` + 
                   `burnt-neighbor-limit` + 
                   `burn-cost` + 
                   `burn-veg-type-threshold`  + 
                   `cycle-duration` + 
                   `veg-distribution`+ 
                   (1 | `veg-cycle-start`),
                 data = data)

mm.fit1.3 = lmer(mean.fm ~ ticks*(`movement-model` + 
                                    `burnt-neighbor-limit` + 
                                    `burn-cost` + 
                                    `burn-veg-type-threshold` + 
                                    `cycle-duration` + 
                                    `veg-distribution`) + 
                   (1 | `veg-cycle-start`), 
                 data = data)

mm.fit1.4 = lmer(mean.fm ~ ticks*(`movement-model` + 
                                    `burnt-neighbor-limit` + 
                                    `burn-cost` + 
                                    `burn-veg-type-threshold` + 
                                    `veg-distribution`) + 
                   (1 | `veg-cycle-start`) + 
                   (1 | `cycle-duration`), 
                 data = data)

anova(mm.fit1.1, mm.fit1.2, mm.fit1.3, mm.fit1.4)

qqnorm(resid(mm.fit1.3))
qqline(resid(mm.fit1.3))

ggpubr::ggarrange(
  ggeffects::ggpredict(mm.fit1.3, terms = c("ticks", "veg-distribution")) %>%
    plot(show_data = FALSE, show_ci = FALSE) +
    theme(title = element_text(size = 6), 
          legend.title = element_text(size = 6)), 
  ggeffects::ggpredict(mm.fit1.3, terms = c("ticks", "cycle-duration")) %>%
    plot(show_data = FALSE, show_ci = FALSE) +
    theme(title = element_text(size = 6), 
          legend.title = element_text(size = 6)), 
  legend = "bottom", nrow = 1
)

ggpubr::ggarrange(
  ggeffects::ggpredict(mm.fit1.3, terms = c("ticks", "burnt-neighbor-limit")) %>%
    plot(show_data = FALSE, show_ci = FALSE) +
    theme(title = element_text(size = 6), 
          legend.title = element_text(size = 6)), 
  ggeffects::ggpredict(mm.fit1.3, terms = c("ticks", "burn-veg-type-threshold")) %>%
    plot(show_data = FALSE, show_ci = FALSE) +
    theme(title = element_text(size = 6), 
          legend.title = element_text(size = 6)), 
  ggeffects::ggpredict(mm.fit1.3, terms = c("ticks", "burn-cost")) %>%
    plot(show_data = FALSE, show_ci = FALSE) +
    theme(title = element_text(size = 6), 
          legend.title = element_text(size = 6)), 
  legend = "bottom", nrow = 1
)

ggpubr::ggarrange(
  ggeffects::ggpredict(mm.fit1.3, terms = c("ticks", "movement-model")) %>%
    plot(show_data = FALSE, show_ci = FALSE) +
    theme(title = element_text(size = 6), 
          legend.title = element_text(size = 6)), 
  # ggeffects::ggpredict(mm.fit1.3, terms = c("ticks", "natural-ignition")) %>%
  #   plot(show_data = FALSE, show_ci = FALSE) +
  #   theme(title = element_text(size = 6), legend.title = element_text(size = 6)), 
  legend = "bottom", nrow = 1
)
```

The regression model demonstrate that burning restrictions and burning costs have the greatest difference in impact on forager mobility. Stricter limits on burning behaviors and higher costs result in higher levels of mobility over the course of model run. Interestingly, the predicted mobility for the highest burning cost shows an increase in average moves per foraging bout. This pattern is impossible in the model because we cap mobility at a maximum value. The contrast of this with the other burning costs demonstrates the differential impact that low cost niche construction strategies can have on forager behaviors.

These mobility patterns due to different limits on burning behaviors occur because burning controls the energy available in the environment such that less burning means less overall energy, so agents need to move further to meet their energy needs.

```{r mobility-veg-correlations, echo=FALSE, message=FALSE, warning=FALSE, out.width='100%'}
par(mfrow = c(1,3))
par(mar=c(0,1,0,1))
#plot at 250
pvalue250 = psych::corr.test(data250 %>% 
                               select(mean.fm, shannon.div, 
                                      veg_morans.i, veg_7, veg_6, veg_5))$p
corrplot::corrplot(cor(data250 %>% 
                         select(mean.fm, shannon.div, 
                                veg_morans.i, veg_7, veg_6, veg_5), 
                       use = "pairwise.complete.obs"),
                   method = "square", 
                   addCoef.col = "black", 
                   col = scales::alpha(corrplot::COL2("RdBu"), alpha = 0.85),
                   p.mat = pvalue250, 
                   insig="blank", 
                   sig.level=0.1, 
                   type = "lower", 
                   number.cex = 0.5, 
                   diag=F)

#plot at 2000
pvalue2000 = psych::corr.test(data2000 %>% 
                                select(mean.fm, shannon.div, 
                                       veg_morans.i, veg_7, veg_6, veg_5))$p
corrplot::corrplot(cor(data2000 %>% 
                         select(mean.fm, shannon.div, 
                                veg_morans.i, veg_7, veg_6, veg_5), 
                       use = "pairwise.complete.obs"),
                   method = "square", 
                   addCoef.col = "black", 
                   col = scales::alpha(corrplot::COL2("RdBu"), alpha = 0.85),
                   p.mat = pvalue2000, 
                   insig="blank", 
                   sig.level=0.1, 
                   type = "lower", 
                   number.cex = 0.5, 
                   diag=F)

#plot at 3500
pvalue3500 = psych::corr.test(data3500 %>% 
                                select(mean.fm, shannon.div, 
                                       veg_morans.i, veg_7, veg_6, veg_5))$p
corrplot::corrplot(cor(data3500 %>% 
                         select(mean.fm, shannon.div, 
                                veg_morans.i, veg_7, veg_6, veg_5), 
                       use = "pairwise.complete.obs"),
                   method = "square", 
                   addCoef.col = "black", 
                   col = scales::alpha(corrplot::COL2("RdBu"), alpha = 0.85),
                   p.mat = pvalue3500, 
                   insig="blank", 
                   sig.level=0.1, 
                   type = "lower", 
                   number.cex = 0.5, 
                   diag=F)

```

We can see this pattern exemplified when looking at correlations between forager movement (*mean.fm*) and the highest vegetation types (*veg_7*, *veg_6*, *veg_5*), that is those that provide the most resources. We generally see negative correlations with the high vegetation types, indicating that low forager mobility is significantly correlated with higher proportions of these vegetation types. 

We can also see that low forager mobility is highly correlated with dispersion of vegetation types, as is evidenced by the positive correlation between *mean.fm* and *veg_morans.i*. This indicates that local heterogeneity of the landscape affects how far the foragers need to move. 

Because mobility is the behavior that agents can control in the model, we looked at how changes in this behavior changes with population evolution. 

```{r mobility-pop-correlations_1, echo=FALSE, fig.height=8, fig.width=8, message=FALSE, warning=FALSE, out.width='100%'}
ggplot(rates %>% 
         filter(`veg-cycle-start` == "\"productive\"") %>% 
         filter(`cycle-duration` == "100") %>%
         filter(`movement-model` == "\"Directed Walk\"")) +
  geom_point(aes(y = end.pop.density, x = start.steps, 
                 color = climate.condition)) +
  geom_smooth(aes(y = end.pop.density, x = start.steps), 
              method = "lm") +
  stat_cor(mapping = aes(y = end.pop.density, x = start.steps), 
           method = "pearson", p.accuracy = 0.01, r.accuracy = 0.01, 
           size = 2.5) +
  facet_wrap(~ tick.range, scales = "free_y") +
  scale_color_brewer(palette = "Set2") +
  theme(legend.position = "bottom") +
  theme(axis.text = element_text(size = 6), 
        legend.position = "bottom", 
        strip.text = element_text(size = 7))

```

Because there is relatively little change in forager steps within climatic intervals, we looked at the relationship between the starting number of steps during a climatic interval and the resulting population density at the end of that interval. Throughout model run, these outputs are highly negatively correlated. This suggests that lower amounts of mobility lead to higher population densities because each foraging group requires less room to meet their foraging needs.

# Forager interactions

When looking at forager interactions, we have to consider them in relation to populations since more foragers on the landscape will necessarily mean more possible interactions. The model outputs interaction counts averaged across all agents and we divided this by the population count to get the average proportion of the population that an individual agent interacts with each tick.

```{r adj-fi-viz, echo=FALSE, message=FALSE, warning=FALSE, out.width="100%"}
ggplot(data %>% filter(ticks > 0)) +
  geom_smooth(aes(x = ticks, y = adj.fi, color = `movement-model`), se = T) +
  facet_grid(`cycle-duration` + `veg-cycle-start` ~ `burn-cost`, 
             labeller = labeller(`veg-cycle-start` = start.labs, 
                                 `cycle-duration` = cycle.labs, 
                                 `burn-cost` = bc.labs)) +
  scale_color_colorblind() +
  theme(legend.position = "bottom", strip.text = element_text(size = 6))

```

When we visualize these differences, we can see that for random walks, there is a steep drop off in forager interactions within approximately the first 500 ticks of the model. This is likely because populations are relatively small at the beginning of model run, so each interaction will necessarily be a greater proportion. For the subsequent analyses, we look at the patterns occurring after the first 500 ticks to understand how the parameters affect interactions after a larger population has been established. 

```{r adj-fi-reg_1, echo=TRUE, message=FALSE, warning=FALSE, out.width='100%', fig.height=5}
fi.data = data %>% filter(ticks > 500)

plotNormalDensity(fi.data$adj.fi)

parameters = c(
  "cycle-duration",  # 100, 250
  "veg-cycle-start", # productive, unproductive
  "veg-distribution", # random, clustered
  "burnt-neighbor-limit", # 1, 4, 8
  "burn-cost", # 0, 50
  "burn-veg-type-threshold", # 4, 7
  "movement-model" #Random, Directed
)

fi.fit1 = lm(adj.fi ~ ticks*(.), data = fi.data %>% 
               dplyr::select_at(c(parameters, "ticks", "adj.fi")))

plot_summs(fi.fit1, scale = T)

```

By comparing standardized regression coefficients, we can see the greatest effect on forager interactions is movement models and burn cost. Because the shape of the trend lines is different enough between random walks and directed walks, we split the data by movement model to further investigate parameter effects.

```{r adj-fi-reg_2, echo=TRUE, message=FALSE, warning=FALSE, out.width='100%', fig.height=3}
rw.data = fi.data %>% filter(`movement-model` == "\"Random Walk\"") 
dw.data = fi.data %>% filter(`movement-model` == "\"Directed Walk\"") 

dw.fit1 = lm(adj.fi ~ ticks*(.), data = dw.data %>% 
               filter(ticks > 0) %>% 
               select_at(c("ticks", "adj.fi", parameters[-7])))

rw.fit1 = lm(adj.fi ~ ticks*(.), data = rw.data %>% 
               filter(ticks > 0) %>% 
               select_at(c("ticks", "adj.fi", parameters[-7])))

par(mfrow = c(1,2))
par(mar=c(1,1,1,1))
plot(dw.fit1, which = 2)
plot(rw.fit1, which = 2)

```

```{r parameter-effects-adj-fi_1, out.width="100%", echo=FALSE, message=FALSE, warning=FALSE, fig.height = 4}

plot_summs(dw.fit1, rw.fit1, scale = T, 
           model.names = c("directed walks", "random walks"))


ggarrange(
  ggeffects::ggpredict(dw.fit1, terms = c("ticks", "burn-cost")) %>%
    plot(show_data = FALSE, show_ci = FALSE, limits = c(0, 0.020)) +
    theme(title = element_text(size = 7)), 
  ggeffects::ggpredict(rw.fit1, terms = c("ticks", "burn-cost")) %>%
    plot(show_data = FALSE, show_ci = FALSE, limits = c(0, 0.020)) +
    theme(title = element_text(size = 7)),
  common.legend = T, legend = "bottom", 
  labels = c("Directed Walk", "Random Walk"), 
  nrow = 1, ncol = 2, 
  font.label = list(size = 8), vjust = 0.8
) +
  theme(plot.margin = margin(0.1,0.2,0.1,0.1, "cm"), 
        title = element_text(size = 7))

```
These two regressions demonstrate that restrictions/costs to burning behaviors impact forager interactions, but that these effects are much more prominent and diverging for directed walks. This again indicates that the amount of burning has a significant impact on the evolution of human behaviors in the model. 

```{r interaction-change-over-time, out.width="100%", echo=FALSE, message=FALSE, warning=FALSE}
ggplot(rates %>% 
         filter(`veg-cycle-start` == "\"productive\"") %>% 
         filter(`cycle-duration` == "250")) +
  geom_boxplot(aes(x = tick.range, y = interactions.slope, 
                   color = climate.condition)) +
  facet_grid( `movement-model` ~ `burn-cost`, 
              scales = "free", labeller = label_both) +
  geom_hline(aes(yintercept = 0), color = "black") +
  scale_color_brewer(palette = "Set2") +
  theme(axis.text.x = element_text(angle = 45), 
        legend.position = 'bottom')

```
As is expected, when we look at how forager interactions changes over across climate intervals, there is very limited change except in the earliest intervals during which populations are being established. When changes does occur, it is primarily with agents performing directed walks and when burning costs are lower. 

Therefore, we investigate how interaction rates over time are related to mobility and population density only with directed walks. 
```{r interactions-mobility, echo=FALSE, fig.height=8, fig.width=8, message=FALSE, warning=FALSE, out.width="100%"}
ggplot(rates %>% 
         filter(`veg-cycle-start` == "\"productive\"") %>% 
         filter(`cycle-duration` == "100") %>% 
         filter(`movement-model` == "\"Directed Walk\"")) +
  geom_point(aes(y = start.steps, x = start.interactions, 
                 color = climate.condition)) +
  geom_smooth(aes(y = start.steps, x = start.interactions), 
              method = "lm") +
  stat_cor(mapping = aes(y = start.steps, x = start.interactions), 
           method = "pearson", p.accuracy = 0.01, r.accuracy = 0.01, 
           size = 2.5) +
  facet_wrap(~ tick.range, scales = "free_x") +
  scale_color_brewer(palette = "Set2") +
  theme(legend.position = "bottom") +
  theme(axis.text = element_text(size = 6), 
        legend.position = "bottom", 
        strip.text = element_text(size = 7))

```
Interactions are highly positively correlated with mobility throughout model run, meaning that more mobility allows for more interactions with directed walks. 

The strength of these correlations is impacted by burning costs. 
```{r interactions-mobility_2, echo=FALSE, fig.height=6, fig.width=8, message=FALSE, warning=FALSE, out.width="100%"}
ggplot(rates %>% filter(`veg-cycle-start` == "\"productive\"") %>% 
         filter(`cycle-duration` == "100") %>% 
         filter(`movement-model` == "\"Directed Walk\"") %>%
         filter(tick.range == "1001-1100")) +
  geom_point(aes(y = start.steps, x = start.interactions, 
                 color = climate.condition)) +
  geom_smooth(aes(y = start.steps, x = start.interactions), 
              method = "lm") +
  stat_cor(mapping = aes(y = start.steps, x = start.interactions), 
           method = "pearson", p.accuracy = 0.01, r.accuracy = 0.01, 
           size = 4) +
  facet_wrap(~ `burn-cost`, scales = "free_x", labeller = label_both) +
  scale_color_brewer(palette = "Set2") +
  theme(axis.text = element_text(size = 6), legend.position = "bottom")

```

For example, if we take a productive climate interval in the middle of model run, we see significant and stronger correlations only when burning costs are low, so when burning is more frequent. 

```{r interactions-population, echo=FALSE, fig.height=6, fig.width=8, message=FALSE, warning=FALSE, out.width="100%"}
ggplot(rates %>% filter(`veg-cycle-start` == "\"productive\"") %>% 
         filter(`cycle-duration` == "100") %>% 
         filter(`movement-model` == "\"Directed Walk\"") %>%
         filter(tick.range == "1001-1100")) +
  geom_point(aes(y = start.pop.density, x = start.interactions, 
                 color = climate.condition)) +
  geom_smooth(aes(y = start.pop.density, x = start.interactions), 
              method = "lm") +
  stat_cor(mapping = aes(y = start.pop.density, x = start.interactions), 
           method = "pearson", p.accuracy = 0.01, r.accuracy = 0.01, 
           size = 4) +
  facet_wrap(~ `burn-cost`, scales = "free_x", labeller = label_both) +
  scale_color_brewer(palette = "Set2") +
  theme(axis.text = element_text(size = 6), legend.position = "bottom")
```
The same is true for negative correlations between interactions and population density, although here the strongest relationship is when there is no burning cost. 

These results are because there is minimal change in forager mobility and therefore interactions at the highest burning costs. 

## Maintaining connections with the same foragers
In addition to understanding overall forager interaction rates, we also loosely investigated the formation of social networks. To do so, we tracked how many of a forager's interactions during a given foraging bout overlapped with the interactions of the previous bout. Doing this provides insight into whether foragers are consistently interacting with new people or if there is incipient formation of social groups. If social groups were "forming", we would expect to see increased proportions of interactions being comprised of the same foragers. 

```{r same-network_1, echo=FALSE, fig.height=6, fig.width=8, message=FALSE, warning=FALSE}
plot.data3 = data %>% filter(ticks > 0) %>% 
  filter(`cycle-duration` == 250) %>% 
  filter(`veg-cycle-start` == "\"productive\"")
plot.data3$`burn-cost` =  as.factor(plot.data3$`burn-cost`)

ggplot(plot.data3) +
  # geom_smooth(data = plot.data3, 
  #             mapping = aes(x = ticks, y = same.fi.prop, color = `burn-cost`)) +
  geom_smooth(data = plot.data3 %>% filter(ticks > 0 & ticks <= 250), 
              mapping = aes(x = ticks, y = same.fi.prop, 
                            color = climate.condition), 
              method = "lm") +
  geom_smooth(data = plot.data3 %>% filter(ticks > 250 & ticks <= 500), 
              mapping = aes(x = ticks, y = same.fi.prop, 
                            color = climate.condition), 
              method = "lm") +
  geom_smooth(data = plot.data3 %>% filter(ticks > 500 & ticks <= 750), 
              mapping = aes(x = ticks, y = same.fi.prop, 
                            color = climate.condition), 
              method = "lm") +
  geom_smooth(data = plot.data3 %>% filter(ticks > 750 & ticks <= 1000), 
              mapping = aes(x = ticks, y = same.fi.prop, 
                            color = climate.condition), 
              method = "lm") +
  geom_smooth(data = plot.data3 %>% filter(ticks > 1000 & ticks <= 1250), 
              mapping = aes(x = ticks, y = same.fi.prop, 
                            color = climate.condition), 
              method = "lm") +
  geom_smooth(data = plot.data3 %>% filter(ticks > 1250 & ticks <= 1500), 
              mapping = aes(x = ticks, y = same.fi.prop, 
                            color = climate.condition), 
              method = "lm") +
  geom_smooth(data = plot.data3 %>% filter(ticks > 1500 & ticks <= 1750), 
              mapping = aes(x = ticks, y = same.fi.prop, 
                            color = climate.condition), 
              method = "lm") +
  geom_smooth(data = plot.data3 %>% filter(ticks > 1750 & ticks <= 2000), 
              mapping = aes(x = ticks, y = same.fi.prop, 
                            color = climate.condition), 
              method = "lm") +
  geom_smooth(data = plot.data3 %>% filter(ticks > 2000 & ticks <= 2250), 
              mapping = aes(x = ticks, y = same.fi.prop, 
                            color = climate.condition), 
              method = "lm") +
  geom_smooth(data = plot.data3 %>% filter(ticks > 2250 & ticks <= 2500), 
              mapping = aes(x = ticks, y = same.fi.prop, 
                            color = climate.condition), 
              method = "lm") +
  geom_smooth(data = plot.data3 %>% filter(ticks > 2500 & ticks <= 2750), 
              mapping = aes(x = ticks, y = same.fi.prop, 
                            color = climate.condition), 
              method = "lm") +
  geom_smooth(data = plot.data3 %>% filter(ticks > 2750 & ticks <= 3000), 
              mapping = aes(x = ticks, y = same.fi.prop, 
                            color = climate.condition), 
              method = "lm") +
  geom_smooth(data = plot.data3 %>% filter(ticks > 3000 & ticks <= 3250), 
              mapping = aes(x = ticks, y = same.fi.prop, 
                            color = climate.condition), 
              method = "lm") +
  geom_smooth(data = plot.data3 %>% filter(ticks > 3250 & ticks <= 3500), 
              mapping = aes(x = ticks, y = same.fi.prop, 
                            color = climate.condition), 
              method = "lm") +
  geom_vline(aes(xintercept = 2500), color = "black") +
  facet_grid(`movement-model` ~ `burn-cost`, 
             labeller = label_both, scales = "free") +
  scale_color_colorblind() +
  theme(strip.text = element_text(size = 6), 
        legend.title = element_blank(), 
        legend.position = "bottom", 
        axis.title = element_text(size = 7.5),
        axis.text = element_text(size = 7)) +
  guides(fill = "none") + 
  labs(y = "average same interaction proportion")

```

When we plot the change in average proportion of interactions that are the same as the previous tick across model run by burn cost and movement model, we see that random walks result in overall higher proportions of agents interacting with the same people compared to directed walks. This is driven primarily by high rates of similar interactions in unproductive periods, particularly when burning costs are high. 

Conversely, with directed walks, we see an initial dip in the proportion of interactions that are with the same people as the population is establishing itself. This makes sense because the population is relatively unstable at this time, so there will be more new people on the landscape. 

If we consider after that burn in period, we see that the proportion of interactions that are with the same people starts to increase again and remains higher the population reaches equilibrium and carrying capacity. Because directed walks also result in fewer interactions over the course of model run, this suggests that directed walks in landscapes with a long history of burning and stable population result in smaller social networks, with foragers frequently interacting with the same people.  

# References

```{r citations, echo=FALSE, message=FALSE, warning=FALSE}
pkgs <- grateful::cite_packages(output = "table", 
                                out.dir = ".", 
                                omit = c("QuantPsyc", "marginaleffects"))
knitr::kable(pkgs)
```
