---
title: "Supplementary Material 2 for: Low-cost niche construction can create conditions for subdivided populations"
subtitle: "Supplementary Analyses"

output:
  bookdown::pdf_document2:
    toc: true
    toc_depth: 3
    number_sections: true
    dev: png
    citation_package: biblatex
bibliography: grateful-refs.bib
csl: pnas.csl
link-citations: yes

header-includes:
  - \renewcommand{\figurename}{Figure S}
  - \makeatletter
  - \def\fnum@figure{\figurename\thefigure}
  - \makeatother
  - \usepackage{float}
  - \usepackage{caption}
  - \captionsetup[figure]{font=small}
---

```{r load-data, message=FALSE, warning=FALSE, include=FALSE}
library(knitr)
library(broom)
library(tidyverse)
library(rcompanion)
library(fitdistrplus)
library(gtsummary)
library(jtools)
library(betareg)
library(mgcv)
library(ggpubr)
library(ggthemes)
library(lme4)
library(glmmTMB)
library(emmeans)
library(bookdown)
theme_set(theme_bw())

knitr::opts_chunk$set(
  dpi=300,
  fig.width=8, 
  fig.align = "center", 
  fig.pos = "H", 
  tidy=T
)
options(
  width=80,
  tinytex.verbose = TRUE
)

data = readRDS("../results/bb-data.rds")

parameters = c(
  "cycle-duration",  # 100, 250
  "veg-cycle-start", # productive, unproductive
  "veg-distribution", # random, clustered
  "burnt-neighbor-limit", # 1, 4, 8
  "burn-cost", # 0, 50
  "burn-veg-type-threshold", # 4, 7
  "movement-model" #Random, Directed
)
data[,parameters] = lapply(data[,parameters], as.factor)
data$`veg-distribution` = factor(data$`veg-distribution`, 
                                 levels = c("\"random\"", "\"clustered\""))
data$`movement-model` = factor(data$`movement-model`, 
                               levels = c("\"Random Walk\"", "\"Directed Walk\""))

data$adj.fi = data$mean.fi/data$pop.count
data$same.fi.prop = data$mean.same.fi / data$mean.fi

data$pop.dens = data$pop.count/(51*51)

data$bself.prop = data$benefit_self / (data$pop.count * data$mean.fm)
data$bother.prop = data$benefit_other / (data$pop.count * data$mean.fm)

data$burnt = data$`veg_-1`
```

```{r setup-correlation-dataframes, message=FALSE, warning=FALSE, include=FALSE}
veg.100.prod = readRDS("../results/outputs/veg_moransi_100-prod.rds")
veg.100.unprod = readRDS("../results/outputs/veg_moransi_100-unprod.rds")
veg.250.prod = readRDS("../results/outputs/veg_moransi_250-prod.rds")
veg.250.unprod = readRDS("../results/outputs/veg_moransi_250-unprod.rds")
veg.data = bind_rows(veg.100.prod, veg.100.unprod, veg.250.prod, veg.250.unprod)
be.100 = readRDS("../results/outputs/be_morans.i_cycle.100.rds")
be.250 = readRDS("../results/outputs/be_morans.i_cycle.250.rds")
be.data = bind_rows(be.100, be.250)

rm(list = c("veg.100.prod", "veg.100.unprod", 
            "veg.250.prod", "veg.250.unprod", 
            "be.100", "be.250"))

outputs = c(
  "pop.dens", #pop count/world size
  "burnt", 
  "mean.burn.prob", 
  "adj.fi", #average interaction count/ population count
  "mean.fm",  #average forager movements per capita
  "bself.prop", #
  "bother.prop", 
  "veg_morans.i", 
  "shannon.div", 
  "be_morans.i"
)

# par(mfrow = c(1,3))
# par(mar=c(0,1,0,1))
#plot at 250
data250 = data %>% dplyr::filter(ticks == 250) %>% 
  left_join(veg.data %>% 
              dplyr::filter(ticks == 250) %>% 
              dplyr::select(exp, morans.i, shannon.div, shannon.div.no0) %>% 
              rename(veg_morans.i = morans.i), 
            by = c("exp")) %>% 
  left_join(be.data %>% 
              dplyr::filter(ticks == 250) %>% 
              dplyr::select(exp, morans.i) %>%
              rename(be_morans.i = morans.i), 
            by = c("exp"))

#plot at 2000
data2000 = data %>% filter(ticks == 2000) %>% 
  left_join(veg.data %>% 
              filter(ticks == 2000) %>% 
              dplyr::select(exp, morans.i, shannon.div, shannon.div.no0) %>% 
              rename(veg_morans.i = morans.i), 
            by = c("exp")) %>% 
  left_join(be.data %>% 
              filter(ticks == 2000) %>% 
              dplyr::select(exp, morans.i) %>%
              rename(be_morans.i = morans.i), 
            by = c("exp"))

#plot at 3500
data3500 = data %>% filter(ticks == 3500) %>% 
  left_join(veg.data %>% 
              filter(ticks == 3500) %>% 
              dplyr::select(exp, morans.i, shannon.div, shannon.div.no0) %>% 
              rename(veg_morans.i = morans.i), 
            by = c("exp")) %>% 
  left_join(be.data %>% 
              filter(ticks == 3500) %>% 
              dplyr::select(exp, morans.i) %>%
              rename(be_morans.i = morans.i), 
            by = c("exp"))

start.labs = c("unproductive start", "productive start")
names(start.labs) = c("\"unproductive\"", "\"productive\"")
cycle.labs = c("cycle every 250 ticks", "cycle every 100 ticks")
names(cycle.labs) = c(250, 100)
dist.labs = c("random environmental potential", 
              "clustered environmental potential")
names(dist.labs) = c("\"random\"", "\"clustered\"")
bc.labs = c("burn cost = 0", "burn cost = 100", 
            "burn cost = 200", "burn cost = 300")
names(bc.labs) = c(0, 100, 200, 300)
bt.labs = c("can burn veg types 1-4", "can burn veg types 1-7")
names(bt.labs) = c(4, 7)
bn.labs = c("can burn with 1 burnt neighbor", 
            "can burn with 4 burnt neighbors", 
            "can burn with 8 burnt neighbors")
names(bn.labs) = c(1, 4, 8)
move.labs = c("random walks", "directed walks")
names(move.labs) = c("\"Random Walk\"", "\"Directed Walk\"")

```


# Population maintenance?

First, we checked to see whether all model runs maintained a population across all 3500 ticks.

```{r pop-maintenance, echo=TRUE, message=FALSE, warning=FALSE}
all.exp = unique(data$exp)

end.tick = unique(data$`tick-limit`)
fd = data %>% filter(ticks == end.tick)
finished.exp = unique(fd$exp)
rm(list = "fd")

#finished.data = data %>% filter(exp %in% finished.exp)
unfinished.data = data %>% filter(!(exp %in% finished.exp))
length(unique(unfinished.data$exp))

```

None of our modeled scenarios resulted in population extinction. 
```{r pop-maintenance-2, eval=FALSE, message=FALSE, warning=FALSE, include=FALSE}
lapply((unfinished.data %>% 
          select_at(c("exp", parameters)) %>% 
          distinct())[,parameters], table)
```

```{r filter-out-unsuccessful-runs, echo=FALSE, message=FALSE, warning=FALSE}
data = data %>% filter(exp %in% finished.exp)
```

# Population during model run

Here we look at changes in population during model run. 

## Population density over time
```{r population-1, echo=FALSE, fig.height=7, fig.width=8, message=FALSE, warning=FALSE, out.width='100%', fig.cap = "Population density over time"}
ggplot(data) +
  geom_smooth(aes(y = pop.dens, x = ticks, group = exp, color = `burn-cost`), 
              alpha = 0.01, size = 0.05) +
  geom_smooth(aes(x = ticks, y = pop.dens), color = "black", se = T) +
  facet_grid(`burn-cost` ~ `cycle-duration`+`veg-cycle-start`, 
             labeller = label_both, scale = "free") +
  scale_color_brewer(palette = "Set2",
                     labels = c("no disturbance cost (0)", 
                                "low disturbance cost (100)", 
                                "medium disturbance cost (200)", 
                                "high disturbance cost (300)")) +
  theme(legend.position = "none")
```

As we can see in Figure S\@ref(fig:population-1), population increases over time. There are fluctuations in population based on the climatic condition of the model, with steep drops in population when the landscape is unproductive (see below). However, the overall trend of population increase is evident across all modeled scenarios.

We looked at linear rates of changes to population density within each climate period of the model to get a more detailed understanding of population change during model run. This was accomplished by separating the data into tick ranges based on the cycle duration of each individual model run. Within each tick range, a linear regression was fit to the output variable of interest, in this case population density, with tick as the explanatory variable. We then recorded the coefficient of the tick variable, as well as the estimated value of the dependent variable at the beginning and end of the tick range. We c 

```{r population-change-over-time-1, message=FALSE, warning=FALSE, include=FALSE}
rates <- readRDS("../results/outputs/output-evolution-comparison.rds")

rates = rates %>% left_join(data %>% select_at(c("exp", parameters)), 
                            by = "exp", multiple = "first")
rates[,4:28] <- lapply(rates[,4:28], as.numeric)

tick.seq1 = seq(from = 0, to = 3500, by = 100)
tick.levels = c()
for(i in 1:(length(tick.seq1) - 1)){
  tick.levels = c(tick.levels, paste0(tick.seq1[i] + 1, "-", tick.seq1[i+1]))
}
tick.seq2 = seq(from = 0, to = 3500, by = 250)
for(i in 1:(length(tick.seq2) - 1)){
  tick.levels = c(tick.levels, paste0(tick.seq2[i] + 1, "-", tick.seq2[i+1]))
}
rates$tick.range = factor(rates$tick.range, levels = tick.levels)

rm(list = c("tick.seq1", "tick.seq2", "tick.levels"))
```


```{r population-change-over-time-2, fig.cap="Linear rate of population change within climatic intervals for model runs starting in a productive climatic interval", echo=FALSE, fig.height=5, fig.width=8, message=FALSE, warning=FALSE, out.width='100%'}
ggplot(rates %>% filter(`veg-cycle-start` == "\"productive\"")) +
  geom_boxplot(aes(x = tick.range, y = pop.dens.slope, 
                   color = climate.condition)) +
  facet_wrap(~ `cycle-duration`, scales = "free", labeller = label_both) +
  geom_hline(aes(yintercept = 0), color = "black") +
  scale_color_brewer(palette = "Set2") +
  theme(legend.position = "bottom", axis.text.x = element_text(angle = 45))

```
We see that, on average, with short climate cycles, unproductive periods see essentially no change in population, with slopes being essentially zero (Figure S\@ref(fig:population-change-over-time-2)). With longer climatic cycles, there is slight positive population change during unproductive periods at the beginning of model run. 

Conversely, there is pretty consistent population growth during productive periods of the model until populations reach an equilibrium around 3000 ticks. The results show that population grows more quickly during productive periods at the beginning of model run, with rates of change decreasing toward zero by the end of the model, when population reaches equilibrium. This demonstrates the effect of a carrying capacity in the model.

## Impact of amount of forageable land on population density
We can investigate this carrying capacity by looking at how many patches on the landscape are available to be foraged during a given time interval and how this is related to the change in population density over that same interval using a non-parametric Spearman's rank correlation. Here we use the population density slope value from each tick range and compare it to the average proportion of the modeled landscape that is either already foraged or burnt at a given tick.

```{r pop-dens-forageable-1, fig.cap="Relationship between change in population density within climatic interval and proportion of patches that are unforageable for short climatic intervals (100 time steps)", echo=FALSE, fig.height=8, fig.width=8, message=FALSE, warning=FALSE, out.width='100%'}
test_data = rates %>% 
  filter(`veg-cycle-start` == "\"productive\"") %>% 
  filter(`cycle-duration` == "100")

# hist(test_data$pop.dens.slope)
# hist(test_data$average.prop.unforageable)

ggplot(test_data) +
  geom_point(aes(x = pop.dens.slope, y = average.prop.unforageable, 
                 color = climate.condition)) +
  # geom_smooth(aes(x = pop.dens.slope, y = average.prop.unforageable), 
  #             method = "lm") +
  geom_vline(aes(xintercept = 0), color = "black") +
  geom_hline(aes(yintercept = 1), color = "black") +
  stat_cor(mapping = aes(x = pop.dens.slope, y = average.prop.unforageable), 
           method = "spearman", p.accuracy = 0.01, r.accuracy = 0.01, 
           size = 2.5) +
  facet_wrap(~ tick.range, scales = "free") +
  scale_color_brewer(palette = "Set2") +
  theme(axis.text = element_text(size = 6), legend.position = "bottom", 
        strip.text = element_text(size = 7))

```
We can see that, with short environmental intervals, change in population density over a climatic interval is moderately to highly correlated, and importantly always significantly, with the proportion of patches that cannot be foraged, demonstrating that population size is indeed controlled by access to energy (Figure S\@ref(fig:pop-dens-forageable-1)), as would be expected based on the model structure.

Interestingly, we see opposite correlations for productive vs unproductive climatic windows. During productive periods, there will be population growth (positive slopes) with more forageable land (low proportions of unforageable patches). Conversely, during unproductive periods, there is more frequently population decline and this is strongly associated with lower proportions of unforageable land. This perhaps simply captures the fact that population decline allows for more land to be left unforaged, so smaller proportions of unforageable land, during a climatic interval. When more of the landscape is unforageable (higher proportions), we see a pattern of population stagnation in unproductive climatic intervals because there is not enough energy to allow for growth. 

```{r pop-dens-forageable-2, fig.cap="Relationship between change in population density within climatic interval and proportion of patches that are unforageable for long climatic intervals (250 time steps)", echo=FALSE, fig.height=8, fig.width=8, message=FALSE, warning=FALSE, out.width='100%'}
ggplot(rates %>% 
         filter(`veg-cycle-start` == "\"productive\"") %>% 
         filter(`cycle-duration` == "250")) +
  geom_point(aes(x = pop.dens.slope, y = average.prop.unforageable, 
                 color = climate.condition)) +
  # geom_smooth(aes(x = pop.dens.slope, y = average.prop.unforageable), 
  #             method = "lm") +
  geom_vline(aes(xintercept = 0), color = "black") +
  geom_hline(aes(yintercept = 1), color = "black") +
  stat_cor(mapping = aes(x = pop.dens.slope, y = average.prop.unforageable), 
           method = "spearman", p.accuracy = 0.01, r.accuracy = 0.01,
           size = 3.5) +
  facet_wrap(~ tick.range, scales = "free") +
  scale_color_brewer(palette = "Set2") +
  theme(axis.text = element_text(size = 6), legend.position = "bottom", 
        strip.text = element_text(size = 7))

```
When climatic periods are longer (Figure S\@ref(fig:pop-dens-forageable-2)), the strong relationship between change in population density and proportions of unforageable patches is reduced or disappears in productive periods until the end of model run. This suggests that with longer climatic cycling, a different aspect of the environment is controlling population density initially.

```{r pop-density-correlations-1, fig.cap="Correlation between population density, change in population density, and counts of high value resource types at the middle of model run (ticks 1500-1750) during a productive climatic interval", fig.width=4, fig.height=4, echo=FALSE, message=FALSE, warning=FALSE, out.width='100%'}
outputs = c(
  "pop.dens", #pop count/world size
  "pop.dens.slope",
  #"burnt", 
  "veg_7", 
  "veg_6", 
  "veg_5"
)

data.mid = data %>% dplyr::filter(`cycle-duration`== 250) %>% 
  dplyr::filter(`veg-cycle-start` == "\"productive\"") %>%
  dplyr::filter(ticks > 1500 & ticks <= 1750) %>% 
  group_by(exp) %>%
  summarize(pop.dens = mean(pop.dens), 
            burnt = mean(burnt),
            veg_7 = mean(veg_7), 
            veg_6 = mean(veg_6), 
            veg_5 = mean(veg_5)) %>%
  left_join(rates %>% 
              dplyr::filter(tick.range == "1501-1750") %>% 
              dplyr::filter(`veg-cycle-start` == "\"productive\"") %>% 
              dplyr::select(exp, pop.dens.slope), 
            by = c("exp"))

data.mid %>%
  select(all_of(outputs)) %>%
  summarise_all(~ mean(duplicated(.)))

par(mar=c(0,1,0,1))

kendall_result = psych::corr.test(data.mid %>% select_at(outputs), method = "kendall", use = "pairwise.complete.obs")

cor_matrix = kendall_result$r
pvalue.mid = kendall_result$p

corrplot::corrplot(
  cor_matrix, 
  method = "square", 
  addCoef.col = "black", 
  col = scales::alpha(corrplot::COL2("RdBu"), alpha = 0.85), 
  p.mat = pvalue.mid, 
  insig = "blank", 
  sig.level = 0.1,
  type = "lower", 
  number.cex = 0.75, 
  diag = FALSE
)


rm(list = c("data.mid", "pvalue.mid"))
```
When we look at the Kendall's Tau correlations between the slope of change in population density for a middle productive period in model runs with longer climatic cycles, we see a significant positive correlation with proportions of high vegetation types, that is patches that have a high resource value (Figure S\@ref(fig:pop-density-correlations-1)). This suggests that, even if most of the landscape cannot be foraged, access to a few high value patches is enough to allow for population growth. If forageable patches have lower resource values, then populations will not grow.  


# Forager likelihood of burning patches
We examined the effects of all model parameters on the *burn-prob*, hereafter referred to as *burning probability*^[It is important to note that this variable is not actually a probability. It is a continuous variable that represents the likelihood of an agent to engage in disturbance behaviors in the model. When agents have the opportunity to perform these disturbance behaviors, this likelihood value is compared to a random number between 0 and 1 and so "burning probability" behaves like a probability when its value is between 0 and 1.], across model run by fitting logistic growth curves to each trajectory of burning probability over time for each model run. For each model run, we ascertain the carrying capacity (*K*), or the upper bound of burning probability, and the growth rate (*r*), or the speed of growth.


```{r burning-probability-fitting-curves, echo=TRUE, message=FALSE, warning=FALSE, out.width='100%', fig.height=4, fig.cap="Sample of logistic fits for average forager burning probability over time for individual model runs."}
logistic = function(t, K, r, t0) {
  K / (1 + exp(-r * (t - t0)))
}

fits = data %>%
  group_by(exp) %>%
  do({
    tryCatch({
      fit = minpack.lm::nlsLM(mean.burn.prob ~ logistic(ticks, K, r, t0), 
                              data = ., 
                              start = list(K = max(.$mean.burn.prob), 
                                           r = 0.1, 
                                           t0 = median(.$ticks)))
      coef_df = as.data.frame(as.list(coef(fit)))
    }, error = function(e) {
      message(paste("Fit failed for exp", unique(.$exp)))
      data.frame(K = NA, r = NA, t0 = NA)
    })
  })

#visual check of fits
df_pred = data %>%
  left_join(fits, by = "exp") %>%
  group_by(exp) %>%
  mutate(pred = logistic(ticks, K, r, t0))

sample = sample(unique(data$exp), size = 25)
ggplot(data = data %>% filter(exp %in% sample), aes(ticks, mean.burn.prob)) +
  geom_point(aes(color = exp), alpha = 0.25) +
  geom_line(data = df_pred %>% filter(exp %in% sample), aes(y = pred), linetype = "dashed", color = "black") +
  facet_wrap(~exp) +
  guides(color = "none")

fits = fits %>% left_join(data, by = "exp", multiple = "last") %>% ungroup()
```
We then performed a non-parametric, full factorial ART ANOVA to assess which parameters and interactions between parameters significant affect both the upper bound of average burning probability across the population (*K*) and the growth rate of burning probabilities over model run (*r*). We compare the relative effect sizes by calculating $\eta^{2}$. 

```{r burning-probability-art-anova-k, echo=TRUE, message=FALSE, warning=FALSE, out.width='100%', fig.height=4}
fits = fits %>%
  rename(cycle_duration = `cycle-duration`, 
         veg_cycle_start = `veg-cycle-start`, 
         veg_distribution = `veg-distribution`, 
         burn_cost = `burn-cost`, 
         burn_veg_type_threshold = `burn-veg-type-threshold`, 
         burnt_neighbor_limit = `burnt-neighbor-limit`, 
         movement_model = `movement-model`)
reg.parameters = c("cycle_duration", "veg_cycle_start", "veg_distribution", 
                   "burn_cost", "burn_veg_type_threshold", "burnt_neighbor_limit", 
                   "movement_model")

outliers = boxplot(fits$K, plot =F)$out
k.reg.data = fits %>% filter(!(K %in% outliers)) %>% dplyr::select(c("K", "exp", reg.parameters)) %>% na.omit()

art_K = ARTool::art(K ~ cycle_duration * veg_distribution * veg_cycle_start * burn_cost * burn_veg_type_threshold * burnt_neighbor_limit * movement_model , data = k.reg.data)
anova_K = anova(art_K)
sig_effects_K = subset(anova_K, `Pr(>F)` < 0.05)

```
## Effects of parameters on upper bound of burning likelihood

```{r burning-probability-art-anova-k-2, echo=TRUE, message=FALSE, warning=FALSE, out.width='100%', fig.height=4}
es_K = effectsize::eta_squared(sig_effects_K, partial = T)
es_ranked_K = es_K[order(-es_K$Eta2_partial), ]
head(es_ranked_K, 6)

```

By looking at the parameters with the highest $\eta^{2}$ values, we can see that for the upper bound of burning probabilities, the effect of burning cost is about twice as large as any other parameter or combination of parameters. The next largest effect is the interaction of burning cost and movement model. 

```{r burn-cost-comparisons-bp, echo=FALSE, message=FALSE, warning=FALSE, out.width='100%', fig.height=4, fig.cap="Comparison of fitted K values by burning cost and movement model."}
ggplot(k.reg.data) +
  geom_boxplot(aes(x = burn_cost, y = K)) +
  facet_wrap(~movement_model)

```

When we compare the effects of burning cost across the different cost levels (Figure S\@ref(fig:burn-cost-comparisons-bp)), we see that smaller costs to burning behaviors produce larger *K* values, meaning that the upper bound for burning behaviors is significantly higher when burning costs are low. We can also see that when the agents perform directed walks, this further depressed the maximum average burning probability that the population will reach. The other highly important parameter is the limit on how many burnt neighbors a patch can have and still allow burning. Similar to burn cost, we find that strict limits on where burning can occur depresses the upper bound of burning probabilities that the population can achieve.

## Effects of parameters on growth rate of burning likelihood

```{r burning-probability-art-anova-r, echo=TRUE, message=FALSE, warning=FALSE, out.width='100%', fig.height=4, fig.cap="Comparison of fitted r values by burning cost and burnt neighbor limits."}

outliers = boxplot(fits$r, plot =F)$out
r.reg.data = fits %>% filter(!(r %in% outliers)) %>% dplyr::select(c("r", "exp", reg.parameters)) %>% na.omit()

art_r = ARTool::art(r ~ cycle_duration * veg_distribution * veg_cycle_start * burn_cost * burn_veg_type_threshold * burnt_neighbor_limit * movement_model , data = r.reg.data)
anova_r = anova(art_r)
sig_effects_r = subset(anova_r, `Pr(>F)` < 0.05)

es_r = effectsize::eta_squared(sig_effects_r, partial = T)
es_ranked_r = es_r[order(-es_r$Eta2_partial), ]
head(es_ranked_r, 5)

ggplot(r.reg.data) +
  geom_boxplot(aes(x = burn_cost, y = r)) +
  facet_wrap(~burnt_neighbor_limit, labeller = labeller(burnt_neighbor_limit = bn.labs))

```
We get similar results for the growth of burning probabilities over model run, where cost and limits to burning behaviors have the largest significant effects. Again we see that when burning is the most unlimited (i.e., low burning cost and more freedom to burn whatever patches), *r* values are higher, meaning that population burning probabilities quickly increase to the upper bound *K*. 

## Negative burning likelihood

As shown in Figure 2A in the manuscript, there are model runs that result in a decrease of burning likelihood among foragers to values below 0. This means that foragers never perform burning behaviors even when there are opportunities available.

```{r negative-bp, echo=TRUE, message=FALSE, warning=FALSE, fig.height=6, out.width='100%'}
length(unique((fits %>% filter(mean.burn.prob < 0))$exp))/length(unique(fits$exp))
```

Approximately 12% of all model runs result in a negative burning probabilities by the end of model run. 

```{r negative-bp2, echo=TRUE, message=FALSE, warning=FALSE, fig.height=6, out.width='100%'}
table((fits %>% filter(mean.burn.prob < 0))$burn_cost)
```

This only occurs when burning costs are 300, that is to say burning costs are greater than the benefit gained from burning. This leads to the question, what about high burning costs leads to negative selection on forager affinity for performing burning behaviors? 

## Effect of self benefit on burning behaviors
Positive selection for burning behaviors across most of the model runs occurs because there is a consistent low benefit to self of these behaviors. Here, we measure benefit to self as the number of times an agent forages from a patch where they were the last agent to burn it as a proportion of the average total number of foraging events at each tick. 

```{r bp-and-other-outputs-1, echo=FALSE, fig.height=6, message=FALSE, warning=FALSE, out.width='100%', fig.cap="Proportion of foraging events where benefit of burning is recouped by agent that last performed the burning behavior at a given patch"}
ggplot(data %>% filter(ticks > 0)) +
  geom_smooth(aes(x = ticks, y = bself.prop, group = exp, 
                  color = as.factor(`burn-cost`)), 
              alpha = 0.01, linewidth = 0.05) +
  geom_smooth(aes(x = ticks, y = bself.prop), se = F, color = "black") +
  scale_color_brewer(palette = "Set2",
                     labels = c("no burn cost (0)", 
                                "low burn cost (100)", 
                                "high burn cost (200)", 
                                "highest burn cost (300)")) +
  geom_hline(yintercept = 0, linetype = "dotted") +
  facet_grid(`cycle-duration` + `veg-cycle-start` ~ `burn-cost`, 
             labeller = labeller(`burn-cost` = bc.labs, 
                                 `cycle-duration` = cycle.labs, 
                                 `veg-cycle-start` = start.labs)) +
  labs(y = "proportion of burning benefits for self", 
       x = "ticks", 
       color = "cost of burning") +
  theme(legend.position = "none", axis.title = element_text(size = 8), 
        strip.text = element_text(size = 6))



```

Benefit to self consistently occurs at low levels across model run for most parameter settings, resulting in the evolution of increased burning behaviors (Figure S\@ref(fig:bp-and-other-outputs-1)). However, it is also evident that some model runs with the highest burning cost result in essentially no self benefit of burning behaviors. This is presumably what leads to negative selection, resulting in foragers not performing burning behaviors.  

### Effect of model parameters on self benefit

```{r bp-and-other-outputs-2, echo=FALSE, fig.height=4, message=FALSE, warning=FALSE, out.width='100%', fig.cap="Average proportion of foraging events where benefit of burning is recouped by agent that last performed the burning behavior at a given patch at the start of each climatic interval during model run"}

ggplot(rates %>% filter(`veg-cycle-start` == "\"productive\"")) +
  geom_boxplot(aes(x = tick.range, y = start.bself,
                   color = climate.condition)) +
  facet_wrap(~ `cycle-duration`, scales = "free", labeller = label_both) +
  geom_hline(aes(yintercept = 0), color = "black") +
  scale_color_brewer(palette = "Set2") +
  theme(legend.position = "bottom", axis.text.x = element_text(angle = 45, size = 6))

```

When we break this down by each climatic interval, we see higher proportions of self benefit during unproductive periods (Figure S\@ref(fig:bp-and-other-outputs-2)), in part due to reduced population density in these climatic intervals. To capture the overall trajectory of this variable over time, we fit a logistic function to it and also calculated the minimum and maximum values from the central 500 ticks of the model run.

```{r bp-selfprop-fitting-curves, echo=TRUE, message=FALSE, warning=FALSE, out.width='100%', fig.height=5, fig.cap="Sample of logistic fits for average forager burning probability over time for individual model runs."}
fits_bself = data %>%
  group_by(exp) %>%
  do({
    tryCatch({
      fit = minpack.lm::nlsLM(bself.prop ~ logistic(ticks, K, r, t0), 
                              data = ., 
                              start = list(K = max(.$bself.prop, na.rm = T), 
                                           r = 0.01, 
                                           t0 = median(.$ticks, na.rm = T)))
      coef_df = as.data.frame(as.list(coef(fit)))
      
      tick_range = range(.$ticks, na.rm = T)
      mid_point = mean(tick_range)
      lower_bound = mid_point - 250
      upper_bound = mid_point + 250
      
      central_data = dplyr::filter(., ticks >= lower_bound & ticks < upper_bound)
      
      min_val = min(central_data$bself.prop, na.rm = T)
      max_val = max(central_data$bself.prop, na.rm = T)
      
      coef_df$min_self_prop = min_val
      coef_df$max_self_prop = max_val
      
      coef_df
    }, error = function(e) {
      message(paste("Fit failed for exp", unique(.$exp)))
      data.frame(K = NA, r = NA, t0 = NA, min_central = NA, max_central = NA)
    })
  })

#visual check of fits
df_pred = data %>%
  left_join(fits_bself, by = "exp") %>%
  group_by(exp) %>%
  mutate(pred = logistic(ticks, K, r, t0))

sample = sample(unique(data$exp), size = 25)
ggplot(data %>% filter(exp %in% sample), aes(ticks, bself.prop)) +
  geom_point(aes(color = exp), alpha = 0.25) +
  geom_line(data = df_pred %>% filter(exp %in% sample), mapping = aes(y = pred), linetype = "dashed", color = "black") +
  geom_hline(data = df_pred %>% filter(exp %in% sample), mapping = aes(yintercept = min_self_prop)) +
  geom_hline(data = df_pred %>% filter(exp %in% sample), mapping = aes(yintercept = max_self_prop)) +
  facet_wrap(~exp, scales = "free") +
  guides(color = "none")

fits_bself = fits_bself %>% left_join(data, by = "exp", multiple = "last") %>% ungroup()

fits_bself = fits_bself %>%
  rename(cycle_duration = `cycle-duration`, 
         veg_cycle_start = `veg-cycle-start`, 
         veg_distribution = `veg-distribution`, 
         burn_cost = `burn-cost`, 
         burn_veg_type_threshold = `burn-veg-type-threshold`, 
         burnt_neighbor_limit = `burnt-neighbor-limit`, 
         movement_model = `movement-model`)
```

We then perform the ART ANOVA analysis on the values of *K* and *r* from the fitted logisitic equation, as well as to the maximum value of self benefit achieved over the course of model run. For each, we calculate $\eta^{2}$ to compare effect sizes of model parameters.

```{r bp-selfprop-art-anova, echo=TRUE, message=FALSE, warning=FALSE, out.width='100%'}
outliers = boxplot(fits_bself$K, plot =F)$out
k.reg.data = fits_bself %>% filter(!(K %in% outliers)) %>% dplyr::select(c("K", "exp", reg.parameters)) %>% na.omit()

art_K = ARTool::art(K ~ cycle_duration * veg_distribution * burn_cost * burn_veg_type_threshold * burnt_neighbor_limit * movement_model , data = k.reg.data)
anova_K = anova(art_K)
sig_effects_K = subset(anova_K, `Pr(>F)` < 0.05)

es_K = effectsize::eta_squared(sig_effects_K, partial = T)
es_ranked_K = es_K[order(-es_K$Eta2_partial), ]
head(es_ranked_K, 8)

outliers = boxplot(fits_bself$r, plot =F)$out
r.reg.data = fits_bself %>% filter(!(r %in% outliers)) %>% dplyr::select(c("r", "exp", reg.parameters)) %>% na.omit()

art_r = ARTool::art(r ~ cycle_duration * veg_distribution * burn_cost * burn_veg_type_threshold * burnt_neighbor_limit * movement_model , data = r.reg.data)
anova_r = anova(art_r)
sig_effects_r = subset(anova_r, `Pr(>F)` < 0.05)

es_r = effectsize::eta_squared(sig_effects_r, partial = T)
es_ranked_r = es_r[order(-es_r$Eta2_partial), ]
head(es_ranked_r, 8)

outliers = boxplot(fits_bself$max_self_prop, plot =F)$out
m.reg.data = fits_bself %>% filter(!(r %in% outliers)) %>% dplyr::select(c("max_self_prop", "exp", reg.parameters)) %>% na.omit()

art_max = ARTool::art(max_self_prop ~ cycle_duration * veg_distribution * burn_cost * burn_veg_type_threshold * burnt_neighbor_limit * movement_model, data = m.reg.data)
anova_m = anova(art_max)
sig_effects_m = subset(anova_m, `Pr(>F)` < 0.05)

es_m = effectsize::eta_squared(sig_effects_m, partial = T)
es_ranked_m = es_m[order(-es_m$Eta2_partial), ]
head(es_ranked_m, 8)
```
We find that similar parameters impact the shape of the trajectory of self benefit over model run as with the trajectory of burning probabilities. 

### Relationship between self benefit and burning behaviors over time

We looked at the relationship between self benefit (and conversely, benefit of burning to others) and burning behaviors by comparing the final value of each within each climatic cycle of the model using Spearman's rank correlations.

```{r bp-and-other-outputs-4, fig.cap="Relationship between proportion of self benefit and burning probability at the end of a climatic interval. Results shown for model runs that start in productive periods and have short climatic intervals (100 time steps).", echo=FALSE, fig.height=8, fig.width=8, message=FALSE, warning=FALSE, out.width='100%'}
ggplot(rates %>% 
         filter(`veg-cycle-start` == "\"productive\"") %>% 
         filter(`cycle-duration` == "100")) +
  geom_point(aes(x = end.burn.prob, y = end.bself, color = climate.condition)) +
  #geom_smooth(aes(x = end.burn.prob, y = end.bself), method = "lm") +
  stat_cor(mapping = aes(x = end.burn.prob, y = end.bself), 
           method = "spearman", p.accuracy = 0.01, r.accuracy = 0.01, 
           size = 2.5) +
  facet_wrap(~ tick.range, scales = "free") +
  scale_color_brewer(palette = "Set2") +
  theme(legend.position = "bottom") +
  theme(axis.text = element_text(size = 6), 
        legend.position = "bottom", 
        strip.text = element_text(size = 7))

```

When looking at how self benefit relates to burning probabilities within climatic intervals, these outputs are fairly strongly correlated at the beginning of model run (Figure S\@ref(fig:bp-and-other-outputs-4)). We can also see that, within each climatic interval, low burning probabilities cluster very tightly with low proportions of self benefit. This supports the claim that benefit to self drives positive selection for this behavior.

```{r bp-and-other-outputs-5, fig.cap="Relationship between proportion of other benefit (inverse of self benefit) and burning probability at the end of a climatic interval. Results shown for model runs that start in productive periods and have short climatic intervals (100 time steps).", echo=FALSE, fig.height=8, fig.width=8, message=FALSE, warning=FALSE, out.width='100%'}
ggplot(rates %>% 
         filter(`veg-cycle-start` == "\"productive\"") %>% 
         filter(`cycle-duration` == "100")) +
  geom_point(aes(x = end.burn.prob, y = end.bother, 
                 color = climate.condition)) +
  #geom_smooth(aes(x = end.burn.prob, y = end.bother), method = "lm") +
  stat_cor(mapping = aes(x = end.burn.prob, y = end.bother), 
           method = "spearman", p.accuracy = 0.01, r.accuracy = 0.01, 
           size = 2.5) +
  facet_wrap(~ tick.range, scales = "free") +
  scale_color_brewer(palette = "Set2")  +
  theme(legend.position = "bottom") +
  theme(axis.text = element_text(size = 6), 
        legend.position = "bottom", 
        strip.text = element_text(size = 7))

```

By the end of model run, burning probabilities are more highly positively correlated with benefit to others (Figure S\@ref(fig:bp-and-other-outputs-5)), meaning that the highest probabilities of burning behaviors occur when agents besides the one that burned a patch are benefiting from the increased resource productivity. This suggests that there is a the collective benefit of burning allows for further positive selection of this behavior. 

## Positive evolution of burning behaviors with high burning costs
One interesting model result is the evolution of high probabilities of burning under conditions where this behavior has a high cost - that is a cost that outweighs the energetic benefits gained. 

```{r high-cost-burning-1, fig.cap="Trends of burning probabilities over time for model runs with high burning costs", echo=FALSE, fig.height=3, fig.width=6, message=FALSE, warning=FALSE, out.width='100%'}
high.burn = data %>% filter(`burn-cost` == 300)

ggplot(high.burn) +
  geom_smooth(aes(x = ticks, y = mean.burn.prob, group = exp, 
                  color = as.factor(`burn-cost`)), 
              alpha = 0.01, linewidth = 0.05) +
  geom_smooth(aes(x = ticks, y = mean.burn.prob), se = F, color = "black") +
  geom_hline(yintercept = 0, linetype = "dotted")

```


```{r high-cost-burning-2, echo=TRUE, fig.height=4, fig.width=6, message=FALSE, warning=FALSE, out.width='100%'}
length(unique((fits %>% filter(burn_cost == 300) %>% filter(mean.burn.prob < 0))$exp))/length(unique((fits %>% filter(burn_cost == 300))$exp))
```

Around 51% of these high cost scenarios result in negative likelihood of burning behaviors by the end of model run (Figure S\@ref(fig:high-cost-burning-1)). 

```{r high-cost-burning-3, fig.cap="Burning probability at the end of the model run during high burn cost model scenarios", echo=FALSE, fig.height=3, fig.width=5, message=FALSE, warning=FALSE, out.width='100%'}
#hist((high.burn %>% filter(ticks == 3500))$mean.burn.prob)

ggplot(high.burn %>% filter(ticks == 3500)) +
  geom_density(aes(x = mean.burn.prob)) +
  facet_wrap(~ `movement-model`, labeller = label_both)

rm(list = c("high.burn"))
```

The final burning probability of the model during these high burn cost scenarios appears to be primarily related to the movement model that agents employ (Figure S\@ref(fig:high-cost-burning-3)). Under random walks, agents are more likely to develop increased burning probabilities. Under directed walks, the high cost of burning keeps burning probabilities low or even negative. This is likely because the targeting of high yield patches allows agents to access enough energy without needing to engage in high cost behaviors. When agents have to rely on randomly encountering high value patches, it is more useful to put energy into creating an environment with more high value patches through burning behaviors. 

# Burnt landscape proportions
```{r burnt-landscape-proportions-plots, fig.cap="Relationship between proportion of landscape that is burnt and population density (A) and burning probabilities (B)", echo=FALSE, message=FALSE, warning=FALSE, eval=FALSE, out.width='100%', fig.height=4}
data$burnt = data$`veg_-1`

ggarrange(
  ggplot(data) +
    geom_point(aes(x = pop.dens, y = burnt, color = ticks)),
  ggplot(data) +
    geom_point(aes(x = mean.burn.prob, y = burnt, color = ticks)),
  nrow = 1, legend = "bottom", common.legend = T, labels="AUTO"
)

```

To understand how the different parameters affect the proportion of burnt landscape during model run, we look at the proportion of burnt landscape reached by the end of model run and also how much change in this proportion occurs in the second half of model run compared to the first half of model run.

Because we are considering the proportion of the total landscape that is burnt, we use a Beta regression to examine the effects of the model parameters and their interactions on this proportion. We examine up to three way interactions between the parameters, which explains approximately 91% of the variation in our response variable.

```{r veg-0-regressions-2, out.width = '100%', fig.height=4, echo=TRUE, message=FALSE, warning=FALSE}
beta.data = data %>% filter(ticks == 3500) %>% 
  mutate(burnt = ifelse(burnt == 0, burnt + 0.00001, burnt)) %>% 
  mutate(burnt = ifelse(burnt == 1, burnt - 0.00001, burnt)) %>% 
  select_at(c("ticks", "burnt", parameters)) %>%
  mutate(across(parameters, as.factor))

beta.fit1 = betareg(burnt ~ (`cycle-duration` + 
                               `veg-cycle-start` +
                               `veg-distribution` + 
                               `burn-cost` +
                               `burn-veg-type-threshold` + 
                               `burnt-neighbor-limit` +
                               `movement-model`)^3, 
                    data = beta.data, na.action = na.fail)

summary(beta.fit1)$pseudo.r.squared
plot(fitted(beta.fit1), residuals(beta.fit1, type = "pearson"))

terms = attr(terms(beta.fit1), "term.labels")
drop_stats = map_df(terms, function(t) {
  f = as.formula(paste(". ~ . -", t))
  mod_drop = update(beta.fit1, f)
  
  lr = lmtest::lrtest(mod_drop, beta.fit1)
  data.frame(
    term = t,
    LR_stat = lr[2,"Chisq"], 
    p_value = lr[2, "Pr(>Chisq)"], 
    delatLogLik = as.numeric(logLik(beta.fit1) - logLik(mod_drop))
  )
})

#print(drop_stats %>% filter(p_value < 0.05))

print(head(drop_stats[order(-drop_stats$delatLogLik), ] %>% select(term, delatLogLik), n = 10))

```

We look at the explanatory power of each of the terms by determining which terms improve the model fit the most by comparing the pseudo-R squared values of models with individual terms dropped. The top terms are three-way interactions that include some type of limit on burning behavior typically with *cycle-duration* and *veg-cycle-start*. This is likely because the combination of these two parameters determines what type of vegetation cycle the model ends in; since we are considering the proportion of burnt landscape at the end of model run, these parameters will therefore be important. Furthermore, unsurprisingly, *burnt-neighbor-limit*, which controls how many patches in a neighborhood can be burnt at one time is an important term in these interactions. 

```{r veg-0-regressions-results-1, out.width = '100%', fig.height=4, echo=TRUE, message=FALSE, warning=FALSE}
broom::tidy(beta.fit1) %>%
  filter(component == "mean") %>%
  select(term, estimate, std.error, p.value) %>%
  filter(term %in% c(
    "`cycle-duration`250:`veg-cycle-start`\"unproductive\"",
    "`movement-model`\"Directed Walk\"",
    "`burnt-neighbor-limit`4", 
    "`burnt-neighbor-limit`8", 
    "`burn-veg-type-threshold`7", 
    "`burn-cost`100", 
    "`burn-cost`200", 
    "`burn-cost`300"
  ))
```


When we look at the effects of these parameters, we see that the combination of long cycles and starting in an unproductive cycle reduces the proportion of burnt landscape, because model runs with long cycles always end in the same vegetation productivity state as they start in. As for the burning parameters, we see the same effects as the previous analyses, where increased costs result in less burnt landscape and relaxed limits result in more burnt landscape at the end of model run. We can also see that directed walks, compared to random walks slightly increase the proportion of burnt landscape, suggesting that directed walks allow for overall more burning events.

```{r veg-0-regressions-3, fig.cap="Proportions of landscape that are burnt across model run for different model parameters", echo=FALSE, fig.height=5, message=FALSE, warning=FALSE, out.width='100%'}
ggarrange(
  ggplot(data) +
    geom_smooth(aes(x = ticks, y = burnt, color = `burn-cost`)) +
    facet_grid(`cycle-duration` ~ `veg-cycle-start`), 
  ggplot(data) +
    geom_smooth(aes(x = ticks, y = burnt, color = `burnt-neighbor-limit`)) +
    facet_grid(`cycle-duration` ~ `veg-cycle-start`),
  legend = "bottom", ncol=2, nrow=1
)

```

This is more obvious when we visualize it in Figure S\@ref(fig:veg-0-regressions-3). These results match those above for the effect of these parameters on mean burning probability. This is also consistent with the high positive correlation between proportion of burnt landscape and burning probability through time. 

To look at change in different halves of model run, we calculate the slope between the proportion of burnt landscape at tick 0 and the mid-point of model run and the slope for the mid-point to the end of model run. We fit a linear regression to the difference in slopes between the beginning and end of model run with up to three way interactions between the parameters. We the performed another drop test to determine which parameters/interactions significantly improve model fit.

```{r calculate-trends-burnt-prop, echo=TRUE, message=FALSE, warning=FALSE, out.width='100%', fig.height=4}
fits_burnt = data %>%
  group_by_at(c("exp", parameters)) %>%
  group_modify(~ {
    burnt0 = .[which(.$ticks == 0), "burnt"]$burnt
    burnt1750 = .[which(.$ticks == 1750), "burnt"]$burnt
    burnt3500 = .[which(.$ticks == 3500), "burnt"]$burnt
    
    tibble(burnt_beg = burnt0, 
           burnt_mid = burnt1750, 
           burnt_end = burnt3500, 
           slope_beg = (burnt1750 - burnt0) / (1750), 
           slope_end = (burnt3500 - burnt1750) / (1750))
  }) %>%
  ungroup() %>%
  mutate(slope_diff = slope_beg - slope_end)

#hist(fits_burnt$slope_beg)
#hist(fits_burnt$slope_end)
hist(fits_burnt$slope_diff)

model1 = lm(slope_diff ~ (.)^3, data = fits_burnt %>% select(c("slope_diff", parameters)))
#plot(model1)

rownames(subset(drop1(model1, test = "F"),`Pr(>F)` < 0.05))

```

We get similar results as with the final proportion of burnt landscape. The parameters *cycle-duration* and *veg-cycle-start* are important interaction parameters because they control which vegetation state we are in when calculating these slopes. Then, the main parameters that are important are all of the burning parameters and movement model. 

```{r visualize-trends-burnt-prop, fig.cap="Comparison of slopes between beginning of model run and end of model run by important parameter values for model runs with short cycle durations and starting in a productive cycle", echo=FALSE, fig.height=5, message=FALSE, warning=FALSE, out.width='100%'}
plot_data = fits_burnt %>% filter(`cycle-duration` == 100) %>% filter(`veg-cycle-start` == "\"productive\"")

ggarrange(
  ggplot(plot_data) +
    geom_boxplot(aes(x = `burn-cost`, y = slope_diff)) +
    geom_hline(aes(yintercept = 0), color="red", linetype = "dashed"), 
  ggplot(plot_data) +
    geom_boxplot(aes(x = `burnt-neighbor-limit`, y = slope_diff)) +
    geom_hline(aes(yintercept = 0), color="red", linetype = "dashed"), 
  ggplot(plot_data) +
    geom_boxplot(aes(x = `burn-veg-type-threshold`, y = slope_diff)) +
    geom_hline(aes(yintercept = 0), color="red", linetype = "dashed"), 
  ggplot(plot_data) +
    geom_boxplot(aes(x = `movement-model`, y = slope_diff)) +
    geom_hline(aes(yintercept = 0), color="red", linetype = "dashed"), 
  nrow = 2, ncol = 2
)
```
Looking at the difference in slopes by parameter values, we can see that on average most of the change in burnt landscape proportions occurs in the beginning of model run (the difference between beginning and end is positive on average). This is consistent with the curves shown above (Figure S\@ref(fig:veg-0-regressions-3)) that level off in the second half of model run. We also see that introducing an increasingly large burning cost results in similar amounts of change in both halves of model run, whereas without a burning cost the model quickly reaches a high proportion of burnt landscape. This is somewhat mirrored with the other burning parameters, although the average trend is not as different among the parameter values. We also see that directed walks result in slightly faster change at the beginning of model run compared to random walks. 

```{r veg-0-regressions-clean, echo=FALSE, fig.height=8, message=FALSE, warning=FALSE, out.width='100%'}

rm(list=c("fits_burnt", "beta.fit1", "beta.data", "drop_stats", "plot_data"))

```


# Spatial clustering of vegetation types

Spatial clustering (and its converse spatial heterogeneity) of vegetation types is assessed via Moran's I values. We limit our analysis to those significant values of Moran's I to assess the degree of clustering (positive values) or dispersion (negative values). 

```{r morans-i-regression-0, echo=FALSE, fig.height=4, fig.width=8, message=FALSE, warning=FALSE, out.width="100%"}
veg.100.prod = readRDS("../results/outputs/veg_moransi_100-prod.rds")
veg.100.unprod = readRDS("../results/outputs/veg_moransi_100-unprod.rds")
veg.250.prod = readRDS("../results/outputs/veg_moransi_250-prod.rds")
veg.250.unprod = readRDS("../results/outputs/veg_moransi_250-unprod.rds")

veg.100.prod = veg.100.prod %>% 
  filter(exp %in% finished.exp)
veg.100.unprod = veg.100.unprod %>% 
  filter(exp %in% finished.exp)
veg.250.prod = veg.250.prod %>% 
  filter(exp %in% finished.exp)
veg.250.unprod = veg.250.unprod %>% 
  filter(exp %in% finished.exp)

veg.100.prod = veg.100.prod %>% 
  filter(ticks != 1000) %>% filter(ticks != 2000)
veg.100.unprod = veg.100.unprod %>% 
  filter(ticks != 1000) %>% filter(ticks != 2000)
veg.250.prod = veg.250.prod %>% 
  filter(ticks != 1000) %>% filter(ticks != 2000)
veg.250.unprod = veg.250.unprod %>% 
  filter(ticks != 1000) %>% filter(ticks != 2000)

parameters = c(
  "cycle_duration",  # 100, 250
  "veg_cycle_start", # productive, unproductive
  "veg_distribution", # random, clustered
  "burnt_neighbor_limit", # 1, 4, 8
  "burn_cost", # 0, 50
  "burn_veg_type_threshold", # 4, 7
  "movement_model" #Random, Directed
)

reg.params = parameters[c(3:7)]
veg.100.prod[,reg.params] = lapply(veg.100.prod[,reg.params], as.factor)
veg.100.unprod[,reg.params] = lapply(veg.100.unprod[,reg.params] , as.factor)
veg.250.prod[,reg.params] = lapply(veg.250.prod[,reg.params], as.factor)
veg.250.unprod[,reg.params] = lapply(veg.250.unprod[,reg.params] , as.factor)

veg.100.prod$veg_distribution = factor(veg.100.prod$veg_distribution, 
                                       levels = c("\"random\"", 
                                                  "\"clustered\""))
veg.100.unprod$veg_distribution = factor(veg.100.unprod$veg_distribution, 
                                         levels = c("\"random\"", 
                                                    "\"clustered\""))
veg.250.prod$veg_distribution = factor(veg.250.prod$veg_distribution, 
                                       levels = c("\"random\"", 
                                                  "\"clustered\""))
veg.250.unprod$veg_distribution = factor(veg.250.unprod$veg_distribution, 
                                         levels = c("\"random\"", 
                                                    "\"clustered\""))

veg.100.prod$movement_model = factor(veg.100.prod$movement_model, 
                                     levels = c("\"Random Walk\"", 
                                                "\"Directed Walk\""))
veg.100.unprod$movement_model = factor(veg.100.unprod$movement_model, 
                                       levels = c("\"Random Walk\"",
                                                  "\"Directed Walk\""))
veg.250.prod$movement_model = factor(veg.250.prod$movement_model, 
                                     levels = c("\"Random Walk\"", 
                                                "\"Directed Walk\""))
veg.250.unprod$movement_model = factor(veg.250.unprod$movement_model, 
                                       levels = c("\"Random Walk\"", 
                                                  "\"Directed Walk\""))

veg_data = bind_rows(veg.100.prod, veg.100.unprod, veg.250.prod, veg.250.unprod) %>%
  mutate(across(parameters, .fns = as.factor)) %>% na.omit()

```

```{r morans-i-regression-1, echo=TRUE, fig.height=4, fig.width=8, message=FALSE, warning=FALSE, out.width="100%"}
art_vc = ARTool::art(morans.i ~ cycle_duration * veg_distribution * burn_cost * burn_veg_type_threshold * burnt_neighbor_limit * movement_model, data = veg_data %>% filter(ticks == 3500))
anova_vc = anova(art_vc)
sig_effects_vc = subset(anova_vc, `Pr(>F)` < 0.05)

es_vc = effectsize::eta_squared(sig_effects_vc, partial = T)
es_ranked_vc = es_vc[order(-es_vc$Eta2_partial), ]
head(es_ranked_vc, 11)

```

Performing an aligned ranks transformation ANOVA on the final Moran's I value of each model run, we can see that  cost of burning behaviors and movement model have the greatest effects on resulting clustering of vegetation types by the end of model run. Interestingly, the underlying distribution of maximum potential vegetation types for patches (*veg-distribution*) has essentially no impact on spatial clustering of vegetation types relative to the other parameters, and even the highest effect size scores are only when this underlying distribution is included in an interaction term. 

```{r morans-i-regression-2,  echo=TRUE, fig.height=4, fig.width=8, message=FALSE, warning=FALSE,out.width="100%"}

ARTool::art.con(art_vc, "burn_cost:movement_model", adjust = "tukey")
```

With post-hoc Tukey comparisons, we can see that there are significant differences in the final clustering of vegetation types across all the different combinations of the movement model and burning cost parameters.

```{r morans-i-regression-3, fig.cap="Spatial autocorrelation of vegetation types over model run by burning cost and movement models", echo=FALSE, fig.height=4, fig.width=8, message=FALSE, warning=FALSE,out.width="100%"}
ggplot(veg_data) +
  geom_jitter(aes(x = ticks, y = morans.i, group = ticks, 
                  color = burn_cost), alpha = 0.1, size = 0.25) +
  geom_smooth(mapping = aes(x = ticks, y = morans.i, color = burn_cost)) +
  facet_wrap(~movement_model) +
  scale_color_brewer(palette = "Set2",
                     labels = c("no disturbance cost (0)", 
                                "low disturbance cost (100)", 
                                "medium disturbance cost (200)", 
                                "high disturbance cost (300)"))

```

When we look at how vegetation clustering changes over time with different burning costs  and different movement models, it is clear that directed walks result in a faster rate of decline in spatial clustering than random walks across all burning costs (Figure S\@ref(fig:morans-i-regression-3)). When burning costs are low/none, this decrease is even steeper as more burning occurs, with spatial autocorrelation becoming more dispersed, at negative values, by the end of model run. This is consistent with above results that directed walk result in faster rates of increase in burning probabilities and more burnt patches over time.

```{r morans-i-by-burn-limits, fig.cap="Trends in spatial autocorrelation of vegetation types across model run by parameters for burning costs, movement models and restrictions of burning behaviors", echo=FALSE, fig.height=5, fig.width=8, message=FALSE, warning=FALSE, out.width='100%'}
plot.data = veg.data %>% 
  filter(signif == T) %>% 
  filter(cycle_duration == 100) %>% 
  filter(veg_cycle_start == "\"productive\"")
plot.data$burn_cost = as.factor(plot.data$burn_cost)

ggplot(plot.data) +
  geom_jitter(data = plot.data %>% filter(burn_cost == 0), 
              mapping = aes(x = ticks, y = morans.i, group = ticks, 
                            color = burn_cost), alpha = 0.1, size = 0.25) +
  geom_jitter(data = plot.data %>% filter(burn_cost == 100), 
              mapping = aes(x = ticks, y = morans.i, group = ticks, 
                            color = burn_cost), alpha = 0.1, size = 0.25) +
  geom_jitter(data = plot.data %>% filter(burn_cost == 200), 
              mapping = aes(x = ticks, y = morans.i, group = ticks, 
                            color = burn_cost), alpha = 0.1, size = 0.25) +
  geom_jitter(data = plot.data %>% filter(burn_cost == 300), 
              mapping = aes(x = ticks, y = morans.i, group = ticks, 
                            color = burn_cost), alpha = 0.1, size = 0.25) +
  geom_smooth(mapping = aes(x = ticks, y = morans.i, color = burn_cost)) +
  facet_grid(movement_model ~ burnt_neighbor_limit + burn_veg_type_threshold, 
             labeller = labeller(burnt_neighbor_limit = bn.labs,
                                 burn_veg_type_threshold = bt.labs,
                                 movement_model = move.labs)) +
  labs(color = "", y = "Global Moran's I of vegetation types") +
  scale_color_brewer(palette = "Set2",
                     labels = c("no disturbance cost (0)", 
                                "low disturbance cost (100)", 
                                "medium disturbance cost (200)", 
                                "high disturbance cost (300)", 
                                "productive interval", 
                                "unproductive interval")) +
  theme(legend.position = "bottom", 
        strip.text = element_text(size = 6), 
        axis.title = element_text(size = 6), 
        legend.text = element_text(size =6))

rm(list = c("plot.data", "veg_data"))
```

There are also differing trends based on spatial limits and vegetation limits on burning behaviors. When patches can only be burnt with 4 or less burnt neighbors, spatial clustering of vegetation types is much more decreased (Figure S\@ref(fig:morans-i-by-burn-limits)), particularly for lower disturbance costs that allow for more burning. 

# Vegetation diversity

Vegetation diversity was measured by Shannon's Diversity Index. This metric considers the proportional abundances of vegetation types to indicate whether one type dominates or abundances are more evenly spread across all types. A SDI value of 0 indicates a lack of diversity with abundance being concentrated in a single species. Higher SDI values indicate more diversity of vegetation types.

```{r veg-diversity-distribution, fig.cap="Distribution of vegetation diversity by movement model", echo=FALSE, fig.height=4, message=FALSE, warning=FALSE, out.width='100%'}
veg.data = bind_rows(veg.100.prod, veg.100.unprod, veg.250.prod, veg.250.unprod) 

#hist(veg.data$shannon.div)

ggplot(veg.data) +
  geom_density(aes(x = shannon.div, color = movement_model))

```

The distribution of this metric is bimodal across model runs. This bimodality is caused by the different movement models used: directed walks result in less diversity than random walks (Figure S\@ref(fig:veg-diversity-distribution)). For this reason, we consider the effects of the other parameters for model runs with random and directed walks separately. 

## Vegetation diversity under random walks

```{r veg-diversity-viz, echo=TRUE, fig.height=3, message=FALSE, warning=FALSE, out.width='100%', fig.cap = "Smoothed trend lines for vegetation diversity over model run for each individual experiment run with random walks."}
veg.data.r = veg.data %>% filter(movement_model == "\"Random Walk\"")
reg.params = parameters = c(
  "cycle_duration",  
  "veg_cycle_start", 
  "veg_distribution", 
  "burnt_neighbor_limit", 
  "burn_cost", 
  "burn_veg_type_threshold"
)
veg.data.r[,reg.params] = lapply(veg.data.r [,reg.params], as.factor)

ggplot(veg.data.r) +
  geom_smooth(aes(x = ticks, y = shannon.div, color = exp), se = F, alpha = 0.5)+
  guides(color = "none")

```

When we visualize the trends in vegetation diversity (Figure S\@ref(fig:veg-diversity-viz)), we can see that some exhibit a peak followed by a steep decline whereas others seem to slowly increase over time. To understand how the model parameters affect these trends, we look at how parameters impact the peak and ending value of diversity as well as the tick when diversity peaks using ART ANOVAs and $\eta^{2}$ values. 

```{r veg-r-art-anova, echo=TRUE, fig.height=3, message=FALSE, warning=FALSE, out.width='100%'}
fits_rw = veg.data.r %>%
  group_by_at(c("exp", reg.params)) %>%
  group_modify(~ {
    data.frame(
      peak_value = .[which.max(.$shannon.div),]$shannon.div,
      peak_tick = .[which.max(.$shannon.div),]$ticks,
      end_value = .[which(.$ticks == 3500),]$shannon.div
    )
  }) %>%
  ungroup() %>%
  mutate(peaked = ifelse(peak_tick < 3500, 1, 0))

art_vd = ARTool::art(peak_tick ~ cycle_duration * veg_distribution * burn_cost * burn_veg_type_threshold * burnt_neighbor_limit, data = fits_rw)
anova_vd = anova(art_vd)
sig_effects_vd = subset(anova_vd, `Pr(>F)` < 0.05)

es_vd = effectsize::eta_squared(sig_effects_vd, partial = T)
es_ranked_vd = es_vd[order(-es_vd$Eta2_partial), ]
head(es_ranked_vd, 5)

art_pv = ARTool::art(peak_value ~ cycle_duration * veg_distribution * burn_cost * burn_veg_type_threshold * burnt_neighbor_limit, data = fits_rw)
anova_pv = anova(art_pv)
sig_effects_pv = subset(anova_pv, `Pr(>F)` < 0.05)

es_pv = effectsize::eta_squared(sig_effects_pv, partial = T)
es_ranked_pv = es_pv[order(-es_pv$Eta2_partial), ]
head(es_ranked_pv, 5)

art_ev = ARTool::art(end_value ~ cycle_duration * veg_distribution * burn_cost * burn_veg_type_threshold * burnt_neighbor_limit, data = fits_rw)
anova_ev = anova(art_ev)
sig_effects_ev = subset(anova_ev, `Pr(>F)` < 0.05)

es_ev = effectsize::eta_squared(sig_effects_ev, partial = T)
es_ranked_ev = es_ev[order(-es_ev$Eta2_partial), ]
head(es_ranked_ev, 7)


```

The results of the ART ANOVA analyses demonstrate that the parameters that control burning behaviors have the largest effects on vegetation diversity when agents perform random walks. 


```{r veg-diversity-art-anova-post-hoc-1, echo=TRUE, fig.height=3, message=FALSE, warning=FALSE, out.width='100%', fig.cap = "Comparison of tick where vegetation diversity peaks in model run by burning costs and limits."}
ARTool::art.con(art_vd, "burn_cost", adjust = "tukey")
ARTool::art.con(art_vd, "burnt_neighbor_limit", adjust = "tukey")


ggplot(fits_rw) +
  geom_boxplot(aes(x = burn_cost, y = peak_tick, group = burn_cost)) +
  facet_wrap(~ burnt_neighbor_limit, labeller = label_both)

```

Post-hoc Tukey tests show that increasing burning costs increases the time to peak diversity, whereas relaxing burning limits and costs causes vegetation diversity to peak early and then decline as seen in the graph above (Figure S\@ref(fig:veg-diversity-viz)). This is likely related to the fact that a burning cost or burning limits reduce the amount of burning over the course of model run, allowing for a landscape that is not dominated by burnt patches.

```{r veg-diversity-art-anova-post-hoc-2, echo=TRUE, fig.height=3, message=FALSE, warning=FALSE, out.width='100%', fig.cap = "Comparison of vegetation diversity value at its peak in model run by burning costs and limits."}
ARTool::art.con(art_pv, "burn_cost", adjust = "tukey")
ARTool::art.con(art_pv, "burnt_neighbor_limit", adjust = "tukey")


ggplot(fits_rw) +
  geom_boxplot(aes(x = burn_cost, y = peak_value, group = burn_cost)) +
  facet_wrap(~ burnt_neighbor_limit, labeller = label_both)

```
Interestingly, when we compare peak values across burning costs/limits, it is the different values of burning cost that produce the most significant differences. We can also see that high burning costs limit the peak value that diversity can achieve (Figure S\@ref(fig:veg-diversity-art-anova-post-hoc-2)), likely because not much burning is occurring to introduce variation in the vegetation types available on the landscape.

```{r veg-diversity-art-anova-post-hoc-3, echo=TRUE, fig.height=4, message=FALSE, warning=FALSE, out.width='100%', fig.cap = "Comparison of vegetation diversity value at end of model run by burning costs and limits."}
ARTool::art.con(art_ev, "burn_cost", adjust = "tukey")
ARTool::art.con(art_ev, "burnt_neighbor_limit", adjust = "tukey")


ggplot(fits_rw) +
  geom_boxplot(aes(x = burnt_neighbor_limit, y = end_value, group = burnt_neighbor_limit)) +
  facet_wrap(~ burn_cost, labeller = label_both)

```
Despite the peak limit, high burning costs allow the model to achieve higher end values of vegetation diversity (Figure S\@ref(fig:veg-diversity-art-anova-post-hoc-3)) because these model runs do not experience the steep drop in diversity as more of the landscape becomes burnt. 

## Vegetation diversity under directed walks

```{r veg-diversity-dw-viz, echo=TRUE, fig.height=3, message=FALSE, warning=FALSE, out.width='100%', fig.cap = "Smoothed trend lines for vegetation diversity over model run for each individual experiment run with directed walks."}
veg.data.d = veg.data %>% filter(movement_model == "\"Directed Walk\"")
reg.params = parameters = c(
  "cycle_duration",  # 100, 250
  "veg_cycle_start", # productive, unproductive
  "veg_distribution", # random, clustered
  "burnt_neighbor_limit", # 1, 4, 8
  "burn_cost", # 0, 50
  "burn_veg_type_threshold"
)
veg.data.d[,reg.params] = lapply(veg.data.d[,reg.params], as.factor)

ggplot(veg.data.d) +
  geom_smooth(aes(x = ticks, y = shannon.div, color = exp), se = F, alpha = 0.5)+
  guides(color = "none")

```
With directed walks, we have overall decreased vegetation diversity, but similar kinds of curves (Figure S\@ref(fig:veg-diversity-dw-viz)), so we can apply the same analysis as above.

```{r veg-d-art-anova, echo=TRUE, fig.height=3, message=FALSE, warning=FALSE, out.width='100%'}
fits_dw = veg.data.d %>%
  group_by_at(c("exp", reg.params)) %>%
  group_modify(~ {
    data.frame(
      peak_value = .[which.max(.$shannon.div),]$shannon.div,
      peak_tick = .[which.max(.$shannon.div),]$ticks,
      end_value = .[which(.$ticks == 3500),]$shannon.div
    )
  }) %>%
  ungroup() %>%
  mutate(peaked = ifelse(peak_tick < 3500, 1, 0))

art_vd = ARTool::art(peak_tick ~ cycle_duration * veg_distribution * burn_cost * burn_veg_type_threshold * burnt_neighbor_limit, data = fits_dw)
anova_vd = anova(art_vd)
sig_effects_vd = subset(anova_vd, `Pr(>F)` < 0.05)

es_vd = effectsize::eta_squared(sig_effects_vd, partial = T)
es_ranked_vd = es_vd[order(-es_vd$Eta2_partial), ]
head(es_ranked_vd, 5)

art_pv = ARTool::art(peak_value ~ cycle_duration * veg_distribution * burn_cost * burn_veg_type_threshold * burnt_neighbor_limit, data = fits_dw)
anova_pv = anova(art_pv)
sig_effects_pv = subset(anova_pv, `Pr(>F)` < 0.05)

es_pv = effectsize::eta_squared(sig_effects_pv, partial = T)
es_ranked_pv = es_pv[order(-es_pv$Eta2_partial), ]
head(es_ranked_pv, 9)

art_ev = ARTool::art(end_value ~ cycle_duration * veg_distribution * burn_cost * burn_veg_type_threshold * burnt_neighbor_limit, data = fits_dw)
anova_ev = anova(art_ev)
sig_effects_ev = subset(anova_ev, `Pr(>F)` < 0.05)

es_ev = effectsize::eta_squared(sig_effects_ev, partial = T)
es_ranked_ev = es_ev[order(-es_ev$Eta2_partial), ]
head(es_ranked_ev, 9)


```


Overall with directed walks, we get very similar relative effect sizes for most of the parameters, with burning costs/limits coming out at the most impactful. 

```{r veg-diversity-dw-art-anova-post-hoc-1, echo=TRUE, fig.height=3, message=FALSE, warning=FALSE, out.width='100%', fig.cap = "Comparison of tick where vegetation diversity peaks in model run by burning costs and limits."}
ARTool::art.con(art_vd, "burn_cost", adjust = "tukey")

ggplot(fits_dw) +
  geom_boxplot(aes(x = burn_cost, y = peak_tick, group = burn_cost))

```
For directed walks, we again see that low burning costs results in early peaks in diversity followed by declines (Figure S\@ref(fig:veg-diversity-dw-art-anova-post-hoc-1)). Interestingly, high burning costs do not follow the pattern as would be expected, but this is likely just an artifact of peak identification on a trend line that have little variation.

```{r veg-diversity-d-art-anova-post-hoc-2, echo=TRUE, fig.height=3, message=FALSE, warning=FALSE, out.width='100%', fig.cap = "Comparison of vegetation diversity value at its peak in model run by burning costs and limits."}
ARTool::art.con(art_pv, "burn_cost", adjust = "tukey")
ARTool::art.con(art_pv, "burnt_neighbor_limit", adjust = "tukey")


ggplot(fits_rw) +
  geom_boxplot(aes(x = burn_cost, y = peak_value, group = burn_cost)) +
  facet_wrap(~ burnt_neighbor_limit, labeller = label_both)

```
Comparison of peak values of vegetation diversity have the same patterns as with random walks.

```{r veg-diversity-d-art-anova-post-hoc-3, echo=TRUE, fig.height=4.5, message=FALSE, warning=FALSE, out.width='100%', fig.cap = "Comparison of vegetation diversity value at end of model run by burning costs and limits."}
ARTool::art.con(art_ev, "burn_cost:burnt_neighbor_limit", adjust = "tukey")
ARTool::art.con(art_ev, "burn_veg_type_threshold:burnt_neighbor_limit", adjust = "tukey")


ggplot(fits_rw) +
  geom_boxplot(aes(x = burn_cost, y = end_value, group = burn_cost)) +
  facet_grid(burn_veg_type_threshold~ burnt_neighbor_limit, labeller = label_both)

```
The limits on burning behaviors have more exaggerated effects with directed walks (Figures S\@ref(fig:veg-diversity-d-art-anova-post-hoc-3)). We can again see clearly that more burning (with relaxed burning restrictions) significantly reduces overall vegetation diversity by the end of model run.


```{r veg-diversity-regression-3, echo=FALSE, fig.height=3, message=FALSE, warning=FALSE, out.width='100%'}
rm(list = c("fits_dw", "fits_rw", 
            "veg.data.r", "veg.data.d"))
```

# Burning behaviors and resource distributions

The above results demonstrate that vegetation spatial autocorrelation and vegetation diversity primarily controlled by the restrictions and cost of burning behaviors; we have also shown that these parameters also control the evolution of burning behaviors across model run. For this reason, we were interested in how burning behaviors, as measured by average burning probabilities, are related to resource distributions during model run. We assessed these with non-parametric Kendall's tau correlations.

```{r burn-veg-correlations-1, fig.cap="Correlations between burning probabilities, burnt landscape proportions, vegetation diversity, vegetation spatial autocorrelation, and high value vegetation types at beginning, middle, and end of model run from left to right", fig.show="hold", fig.height=6, fig.width=8, echo=FALSE, message=FALSE, warning=FALSE, out.width='100%'}
par(mfrow = c(1,3))
par(mar=c(0,1,0,1))
#plot at 250
kendall_result = psych::corr.test(data250 %>% 
                                    select(mean.burn.prob, burnt,
                                           shannon.div, veg_morans.i, 
                                           veg_7, veg_6, veg_5), 
                                  method = "kendall", use = "pairwise.complete.obs")

cor_matrix = kendall_result$r
pvalue.mid = kendall_result$p

corrplot::corrplot(
  cor_matrix, 
  method = "square", 
  addCoef.col = "black", 
  col = scales::alpha(corrplot::COL2("RdBu"), alpha = 0.85), 
  p.mat = pvalue.mid, 
  insig = "blank", 
  sig.level = 0.1,
  type = "lower", 
  number.cex = 0.75, 
  diag = FALSE
)

#plot at 2000
kendall_result = psych::corr.test(data2000 %>% 
                                    select(mean.burn.prob, burnt,
                                           shannon.div, veg_morans.i, 
                                           veg_7, veg_6, veg_5), 
                                  method = "kendall", use = "pairwise.complete.obs")

cor_matrix = kendall_result$r
pvalue.mid = kendall_result$p

corrplot::corrplot(
  cor_matrix, 
  method = "square", 
  addCoef.col = "black", 
  col = scales::alpha(corrplot::COL2("RdBu"), alpha = 0.85), 
  p.mat = pvalue.mid, 
  insig = "blank", 
  sig.level = 0.1,
  type = "lower", 
  number.cex = 0.75, 
  diag = FALSE
)

#plot at 3500
kendall_result = psych::corr.test(data3500 %>% 
                                    select(mean.burn.prob, burnt,
                                           shannon.div, veg_morans.i, 
                                           veg_7, veg_6, veg_5), 
                                  method = "kendall", use = "pairwise.complete.obs")

cor_matrix = kendall_result$r
pvalue.mid = kendall_result$p

corrplot::corrplot(
  cor_matrix, 
  method = "square", 
  addCoef.col = "black", 
  col = scales::alpha(corrplot::COL2("RdBu"), alpha = 0.85), 
  p.mat = pvalue.mid, 
  insig = "blank", 
  sig.level = 0.1,
  type = "lower", 
  number.cex = 0.75, 
  diag = FALSE
)

```

By the end of model run we see a stronger negative correlation of burning probabilities with vegetation Moran's I and Shannon Diversity (Figure S\@ref(fig:burn-veg-correlations-1)). Increasing burning results in less diversity because of dominating proportion of burnt patches on the landscape when burning is very frequent. The negative correlation with vegetation spatial autocorrelation demonstrates that the landscape becomes more locally heterogeneous as burning becomes more frequent. Interestingly, however, there does not appear to be a strong correlation between average burning probabilities and the number of high yield patches on the landscape, despite the fact that burning behaviors are required to create these high yield patches. 

```{r high-yield-veg, fig.cap="Proportions of high yield vegetation proportions throughout model run", fig.height=5, fig.width=8, echo=FALSE, message=FALSE, warning=FALSE, out.width='100%'}

high.veg = data %>%
  select(ticks, `cycle-duration`, `veg-cycle-start`, veg_7, veg_6, veg_5) %>%
  pivot_longer(veg_7:veg_5, names_to = "high_yield_veg", values_to = "proportion")

ggplot(high.veg) +
  geom_line(aes(x = ticks, y = proportion, 
                group = high_yield_veg, color = high_yield_veg)) +
  facet_grid(`cycle-duration` ~ `veg-cycle-start`, labeller = label_both)

rm(list = c("high.veg"))
```
However, we can see that the proportion of high yield patches increases over the course of model run (Figure S\@ref(fig:high-yield-veg)). This means that as burning behaviors become more frequent with time, there will be more high yield patches on the landscape.

# Forager mobility

In the model, foragers can adjust how many steps they take during a foraging bout if they determine they will meet their energy requirements with fewer steps. Movement in the model is, therefore, patterned primarily by the energy available in the gridded landscape, which is determined by whether the model is in a productive or unproductive climatic period and how long those climatic periods last.

```{r fm-viz, fig.cap="Trends in average steps per foraging bout across model run", echo=FALSE, message=FALSE, warning=FALSE, out.width="100%"}
ggplot(data %>% filter(ticks > 0)) +
  # geom_point(aes(x = ticks, y = mean.fm, color = `movement-model`), 
  # alpha = 0.01, size = 0.1) +
  geom_smooth(aes(x = ticks, y = mean.fm, color = `movement-model`), 
              method = "gam") +
  #geom_hline(yintercept = 0, linetype = "dotted") +
  facet_grid(`cycle-duration` ~ `veg-cycle-start`, 
             labeller = label_both) +
  scale_color_colorblind(labels = c("Directed Walk", "Random Walk"))

```

We can see in Figure S\@ref(fig:fm-viz) that there is a decrease in movement during productive periods and an increase in movement during unproductive periods of the model. This is more smoothed when cycle duration is shorter. 

```{r fm-viz-2, fig.cap="Slope of linear relationship between steps per foraging bout and time for each climatic interval across model run", echo=FALSE, message=FALSE, warning=FALSE, out.width="100%", fig.height=5.5}
ggplot(rates %>% 
         filter(`veg-cycle-start` == "\"productive\"")) +
  geom_boxplot(aes(x = tick.range, y = steps.slope, 
                   color = climate.condition)) +
  facet_grid(`movement-model`~ `cycle-duration`, 
             scales = "free", 
             labeller = label_both) +
  geom_hline(aes(yintercept = 0), color = "black") +
  scale_color_brewer(palette = "Set2") +
  theme(legend.position = "bottom", 
        axis.text.x = element_text(angle = 45, size = 6))

```
When we break this down by climatic interval, we can see that most of the change to mobility, as measured by the linear slope within each tick range, occurs during productive intervals (Figure S\@ref(fig:fm-viz-2)). Interestingly, across these productive intervals, it primarily at the beginning of model run when mobility decreases across the interval. By the end of model run, there is actually a slight increase in mobility across the climatic interval.

```{r fm-viz-3, fig.cap="Average number of steps per foraging bout at the beginning of each climatic interval across model run", echo=FALSE, message=FALSE, warning=FALSE, out.width="100%", fig.height=5.5}
ggplot(rates %>% 
         filter(`veg-cycle-start` == "\"productive\"")) +
  geom_boxplot(aes(x = tick.range, y = start.steps, 
                   color = climate.condition)) +
  facet_grid(`movement-model`~ `cycle-duration`, 
             scales = "free", 
             labeller = label_both) +
  scale_color_brewer(palette = "Set2") +
  theme(legend.position = "bottom", 
        axis.text.x = element_text(angle = 45, size=6))

```

The overall decrease in mobility across model run is primarily caused by steep dips in mobility at the beginning of each productive interval (Figure S\@ref(fig:fm-viz-3)). 

## Effect of model parameters on forager mobility

To understand how model parameters affected forager mobility, we chose to investigate the difference between the final average steps per foraging bout achieved at the end of model run and the upper limit on forager steps imposed by the model parameters (for this manuscript, this value is 10). This results in a count variable that is zero-inflated because many model runs maintain the maximum number of possible forager steps. Therefore, using a mixed, zero-inflated Tweedie model, we can see how the other parameters affect forager movement while controlling for starting vegetation state and cycle duration to deal with the model end effects seen above.

```{r fm-mm-regs, echo=TRUE, message=FALSE, warning=FALSE, out.width="100%"}
reg.parameters = c(
  "veg-distribution", 
  "burnt-neighbor-limit",
  "burn-cost", 
  "burn-veg-type-threshold", 
  "movement-model" 
)

reg.data = data %>% filter(ticks == 3500) %>% select(c("ticks", "mean.fm", reg.parameters, "cycle-duration", "veg-cycle-start")) %>%
  mutate(across(c(reg.parameters, "cycle-duration", "veg-cycle-start"), .fns = as.factor)) %>%
  mutate(reduction_of_steps = (10 - mean.fm))

hist(reg.data$reduction_of_steps)

# car::vif(glm(reduction_of_steps ~ `veg-distribution` + `burnt-neighbor-limit` + 
#                  `burn-cost` + `burn-veg-type-threshold` + `movement-model`,
#                data = reg.data,
#                family = poisson))

mm.fit1 = glmmTMB(reduction_of_steps ~ (`veg-distribution` + `burnt-neighbor-limit` + `burn-cost` + `burn-veg-type-threshold` + `movement-model`) + (1 | `cycle-duration`:`veg-cycle-start`), 
                  data = reg.data,  zi = ~ `burn-cost` + `cycle-duration`:`veg-cycle-start`,
                  family = tweedie(link = "log"))


sim <- DHARMa::simulateResiduals(mm.fit1, n=200)
DHARMa::testDispersion(sim)
DHARMa::testZeroInflation(sim)

summary(mm.fit1)


```

First, we consider the effects on the zero inflation model, that is the model parameters that result in no change from the maximum number of steps by the end of model run. We can see that most models see some reduction in forager mobility by the end of model run. However, this is affected by burning costs and the vegetation productivity state the model ends in. If the model ends in an unproductive state (cycle duration = 250 and veg cycle stat = productive or cycle duration = 100 and veg cycle start = unproductive), then the final average number of steps the agents are taking will be closer to maximum mobility. If the model finishes in a productive state, that reduction in mobility is evident. 

When looking at the fixed effects of the parameters, we get confirmation that there is typically a reduction in forager mobility by the end model run (intercept term). The other parameters significantly affecting forager mobility at the end of model run are the burning costs/limits and the movement model. As with most other things in the model, relaxing burning costs and limits leads to more reduction of steps because it leads to more burning and therefore increased resource availability within a local neighborhood. Directed walks also result in more reduction of steps because agents are able to target high value patches and therefore do not need to spend as much time "searching" to reach their energy needs. 


## Correlations between mobility and distributions of vegetation types

These mobility patterns due to different limits on burning behaviors occur because burning controls the energy available in the environment such that less burning means less overall energy, so agents need to move further to meet their energy needs. To confirm this, we look at the Kendall's tau correlations between forager mobility and vegetation distribution/types.

```{r mobility-veg-correlations, fig.cap="Correlations between forager mobility, vegetation diversity, vegetation spatial autocorrelation, and high value vegetation types at beginning, middle, and end of model run from left to right", fig.show="hold", fig.height=6, fig.width=8, echo=FALSE, message=FALSE, warning=FALSE, out.width='100%'}
par(mfrow = c(1,3))
par(mar=c(0,1,0,1))
#plot at 250
kendall_result = psych::corr.test(data250 %>% 
                                    select(mean.fm, shannon.div, 
                                           veg_morans.i, veg_7, veg_6, veg_5), 
                                  method = "kendall", use = "pairwise.complete.obs")

cor_matrix = kendall_result$r
pvalue.mid = kendall_result$p

corrplot::corrplot(
  cor_matrix, 
  method = "square", 
  addCoef.col = "black", 
  col = scales::alpha(corrplot::COL2("RdBu"), alpha = 0.85), 
  p.mat = pvalue.mid, 
  insig = "blank", 
  sig.level = 0.1,
  type = "lower", 
  number.cex = 0.75, 
  diag = FALSE
)

#plot at 2000
kendall_result = psych::corr.test(data2000 %>% 
                                    select(mean.fm, shannon.div, 
                                           veg_morans.i, veg_7, veg_6, veg_5), 
                                  method = "kendall", use = "pairwise.complete.obs")

cor_matrix = kendall_result$r
pvalue.mid = kendall_result$p

corrplot::corrplot(
  cor_matrix, 
  method = "square", 
  addCoef.col = "black", 
  col = scales::alpha(corrplot::COL2("RdBu"), alpha = 0.85), 
  p.mat = pvalue.mid, 
  insig = "blank", 
  sig.level = 0.1,
  type = "lower", 
  number.cex = 0.75, 
  diag = FALSE
)

#plot at 3500
kendall_result = psych::corr.test(data3500 %>% 
                                    select(mean.fm, shannon.div, 
                                           veg_morans.i, veg_7, veg_6, veg_5), 
                                  method = "kendall", use = "pairwise.complete.obs")

cor_matrix = kendall_result$r
pvalue.mid = kendall_result$p

corrplot::corrplot(
  cor_matrix, 
  method = "square", 
  addCoef.col = "black", 
  col = scales::alpha(corrplot::COL2("RdBu"), alpha = 0.85), 
  p.mat = pvalue.mid, 
  insig = "blank", 
  sig.level = 0.1,
  type = "lower", 
  number.cex = 0.75, 
  diag = FALSE
)
```

We can see this pattern exemplified when looking at correlations between forager movement (*mean.fm*) and the highest vegetation types (*veg_7*, *veg_6*, *veg_5*), that is those that provide the most resources. We generally see negative correlations with the high vegetation types (Figure S\@ref(fig:mobility-veg-correlations)), indicating that low forager mobility is significantly correlated with higher proportions of these vegetation types. 

We can also see that low forager mobility is highly correlated with dispersion of vegetation types, as is evidenced by the positive correlation between *mean.fm* and *veg_morans.i*. This indicates that local heterogeneity of the landscape affects how far the foragers need to move. 

## Correlations between forager mobility and population density

Because mobility is the behavior that agents can control in the model, we looked at how changes in this behavior changes with population evolution using Spearman's rank correlations within climatic intervals. Because there is relatively little change in forager steps within climatic intervals, we looked at the relationship between the starting number of steps during a climatic interval and the resulting population density at the end of that interval. 

```{r mobility-pop-correlations-1, fig.cap="Relationship between average steps per foraging bout during climatic intervals and the resulting population density during the same climatic interval for model scenarios with short climatic cycles (100 ticks)", echo=FALSE, fig.height=8, fig.width=8, message=FALSE, warning=FALSE, out.width='100%'}
ggplot(rates %>% 
         filter(`veg-cycle-start` == "\"productive\"") %>% 
         filter(`cycle-duration` == "100") %>%
         filter(`movement-model` == "\"Directed Walk\"")) +
  geom_point(aes(y = end.pop.density, x = start.steps, 
                 color = climate.condition)) +
  # geom_smooth(aes(y = end.pop.density, x = start.steps), 
  #             method = "lm") +
  stat_cor(mapping = aes(y = end.pop.density, x = start.steps), 
           method = "spearman", p.accuracy = 0.01, r.accuracy = 0.01, 
           size = 2.5) +
  facet_wrap(~ tick.range, scales = "free_y") +
  scale_color_brewer(palette = "Set2") +
  theme(legend.position = "bottom") +
  theme(axis.text = element_text(size = 6), 
        legend.position = "bottom", 
        strip.text = element_text(size = 7))

```

Throughout model run, these outputs are highly negatively correlated (Figure S\@ref(fig:mobility-pop-correlations-1)). This suggests that lower amounts of mobility allow higher population densities because each foraging group requires less room to meet their foraging needs.

# Forager interactions

When looking at forager interactions, we have to consider them in relation to populations since more foragers on the landscape will necessarily mean more possible interactions. The model outputs interaction counts averaged across all agents and we divided this by the population count to get the average proportion of the population that an individual agent interacts with each tick.

```{r adj-fi-viz, fig.cap="Trends in average proportion of population a given agent interacts with across model run", echo=FALSE, message=FALSE, warning=FALSE, out.width="100%", fig.height=7}
ggplot(data %>% filter(ticks > 0)) +
  geom_smooth(aes(x = ticks, y = adj.fi, color = `movement-model`), se = T) +
  facet_grid(`cycle-duration` + `veg-cycle-start` ~ `burn-cost`, 
             labeller = labeller(`veg-cycle-start` = start.labs, 
                                 `cycle-duration` = cycle.labs, 
                                 `burn-cost` = bc.labs)) +
  scale_color_colorblind() +
  theme(legend.position = "bottom", strip.text = element_text(size = 6))

```

When we visualize these differences (Figure S\@ref(fig:adj-fi-viz)), we can see that for random walks, there is a steep drop off in forager interactions within approximately the first 500 ticks of the model. This is likely because populations are relatively small at the beginning of model run, so each interaction will necessarily be a greater proportion. 

We used Beta regressions to examine the effects of the parameters on the proportion of forager interactions at model tick = 1000 and at the end of model run. To assess the relevance of parameters to the model, we calculate whether each term improved model fit using a LRT test and by calculating the change in likelihood (delatLogLik).

## Forager interactions at the beginning of model run

```{r adj-fi-reg-1, echo=TRUE, message=FALSE, warning=FALSE, fig.show="hold", out.width='100%', fig.height=3}
reg.params = c(
  "cycle-duration", 
  "veg-distribution",
  "veg-cycle-start", 
  "burn-cost",
  "burn-veg-type-threshold",
  "burnt-neighbor-limit", 
  "movement-model"
)

beta.data1000 = data %>% filter(ticks == 1000) %>%
  mutate(adj.fi = ifelse(adj.fi == 0, adj.fi + 0.00001, adj.fi)) %>% 
  mutate(adj.fi = ifelse(adj.fi == 1, adj.fi - 0.00001, adj.fi)) %>% 
  select_at(c("ticks", "adj.fi", reg.params)) %>%
  mutate(across(reg.params, as.factor))

beta.fit1 = betareg(adj.fi ~ (`cycle-duration` + 
                                `veg-cycle-start` +
                                `veg-distribution` + 
                                `burn-cost` +
                                `burn-veg-type-threshold` + 
                                `burnt-neighbor-limit` + 
                                `movement-model`)^2, 
                    data = beta.data1000, na.action = na.fail)

summary(beta.fit1)$pseudo.r.squared
plot(fitted(beta.fit1), residuals(beta.fit1, type = "pearson"))

terms = attr(terms(beta.fit1), "term.labels")
drop_stats = map_df(terms, function(t) {
  f = as.formula(paste(". ~ . -", t))
  mod_drop = update(beta.fit1, f)
  
  lr = lmtest::lrtest(mod_drop, beta.fit1)
  data.frame(
    term = t,
    LR_stat = lr[2,"Chisq"], 
    p_value = lr[2, "Pr(>Chisq)"], 
    delatLogLik = as.numeric(logLik(beta.fit1) - logLik(mod_drop))
  )
})

print(drop_stats %>% filter(p_value < 0.05))


```

We can see that, for the early parts of model run (tick = 1000), there are only 7 parameters or interactions for which dropping the term would significantly reduce model fit.  

```{r parameter-effects-adj-fi-1,  out.width="100%", echo=FALSE, message=FALSE, warning=FALSE, fig.height = 4}

print(head(drop_stats[order(-drop_stats$delatLogLik), ] %>% select(term, delatLogLik), n = 10))

```

When we order by the raw improvement in likelihood, we can see that the interactions between burning costs/limits and movement models contribute the most to explaining the variation in the response (have a stronger impact on model fit). 

```{r parameter-effects-adj-fi-2,  out.width="100%", echo=FALSE, message=FALSE, warning=FALSE, fig.height = 4}

as.data.frame(emmeans(beta.fit1, ~ `burn-cost`:`movement-model`) %>%
                pairs(adjust = "tukey")) %>% filter(p.value < 0.05) %>% select(contrast, estimate)

```

When we do pairwise comparisons among the parameter values with Tukey adjustment we can see that most of the significant differences occur with directed walks, where directed walks result in more interaction than random walks. These effect sizes are very small, likely because the interaction proportions themselves are small. We also see that increased burning costs within a particular movement model (here only directed walks) also increase the interaction proportions at the beginning of model run.

## Forager interactions at the end of model run

```{r adj-fi-reg-2, echo=TRUE, message=FALSE, warning=FALSE, fig.show="hold", out.width='100%', fig.height=3}
reg.params = c(
  "cycle-duration", 
  "veg-distribution",
  "veg-cycle-start", 
  "burn-cost",
  "burn-veg-type-threshold",
  "burnt-neighbor-limit", 
  "movement-model"
)

beta.data3500 = data %>% filter(ticks == 3500) %>%
  mutate(adj.fi = ifelse(adj.fi == 0, adj.fi + 0.00001, adj.fi)) %>% 
  mutate(adj.fi = ifelse(adj.fi == 1, adj.fi - 0.00001, adj.fi)) %>% 
  select_at(c("ticks", "adj.fi", reg.params)) %>%
  mutate(across(reg.params, as.factor))

beta.fit1 = betareg(adj.fi ~ (`cycle-duration` + 
                                `veg-cycle-start` +
                                `veg-distribution` + 
                                `burn-cost` +
                                `burn-veg-type-threshold` + 
                                `burnt-neighbor-limit` + 
                                `movement-model`)^3, 
                    data = beta.data3500, na.action = na.fail)

summary(beta.fit1)$pseudo.r.squared
plot(fitted(beta.fit1), residuals(beta.fit1, type = "pearson"))

terms = attr(terms(beta.fit1), "term.labels")
drop_stats = map_df(terms, function(t) {
  f = as.formula(paste(". ~ . -", t))
  mod_drop = update(beta.fit1, f)
  
  lr = lmtest::lrtest(mod_drop, beta.fit1)
  data.frame(
    term = t,
    LR_stat = lr[2,"Chisq"], 
    p_value = lr[2, "Pr(>Chisq)"], 
    delatLogLik = as.numeric(logLik(beta.fit1) - logLik(mod_drop))
  )
})

print(head(drop_stats[order(-drop_stats$delatLogLik), ] %>% select(term, delatLogLik), n = 10))

```
For forager interactions at the end of model run we again see that the interactions between movement models and burning rules are of high importance for explaining variation. We can also see that the ending vegetation productivity state (determined by the *cycle-duration* and *veg-cycle-start* interaction) affects forager interactions, likely because of the effect this has on mobility. Interestingly, we also see the underlying vegetation distribution included in these important interactions. 

```{r parameter-effects-adj-fi-3,  out.width="100%", echo=FALSE, message=FALSE, warning=FALSE, fig.height = 4}

as.data.frame(emmeans(beta.fit1, ~ `veg-distribution`) %>%
                pairs(adjust = "tukey")) %>% filter(p.value < 0.05) %>% select(contrast, estimate)

```

When we look at the pairwise comparisons on vegetation distribution, we see that landscapes with clustered underlying vegetation structure result in more interactions than landscapes with no imposed underlying vegetation structure. 


```{r parameter-effects-adj-fi-4,  out.width="100%", echo=FALSE, message=FALSE, warning=FALSE, fig.height = 4}

as.data.frame(emmeans(beta.fit1, ~ `burn-cost`:`movement-model`) %>%
                pairs(adjust = "tukey")) %>% filter(p.value < 0.05) %>% select(contrast, estimate)

```

This vegetation distribution effect interacts with those of burning costs/limits and movement models as well. When we look at the two way interaction of burning costs and movement models, we see that directed walks result in more interaction unless burning costs are high. Increased burning costs also results in more interactions regardless of movement model.

## Change in forager interactions over time
```{r interaction-change-over-time, fig.cap="Change in proportion of the population foragers interact with across each climatic interval", out.width="100%", fig.height=6, echo=FALSE, message=FALSE, warning=FALSE}
ggplot(rates %>% 
         filter(`veg-cycle-start` == "\"productive\"") %>% 
         filter(`cycle-duration` == "250")) +
  geom_boxplot(aes(x = tick.range, y = interactions.slope, 
                   color = climate.condition)) +
  facet_grid( `movement-model` ~ `burn-cost`, 
              scales = "free", labeller = label_both) +
  geom_hline(aes(yintercept = 0), color = "black") +
  scale_color_brewer(palette = "Set2") +
  theme(axis.text.x = element_text(angle = 45, size = 6), 
        legend.position = 'bottom')

```
As is expected, when we look at how forager interactions change over across climate intervals, as measured by the linear slope, there is very limited change except in the earliest intervals during which populations are being established. When changes does occur, it is primarily with agents performing directed walks and when burning costs are lower (Figure S\@ref(fig:interaction-change-over-time). 

## Relationship between forager interactions and: forager mobility and population density
Therefore, we investigate how interaction rates over time are related to mobility and population density only with directed walks using Spearman's rank correlations. 
```{r interactions-mobility, fig.cap="Relationship between proportion of population foragers interact with and steps per foraging bout at the beginning of each climatic interval across model run", echo=FALSE, fig.height=8, fig.width=8, message=FALSE, warning=FALSE, out.width="100%"}
ggplot(rates %>% 
         filter(`veg-cycle-start` == "\"productive\"") %>% 
         filter(`cycle-duration` == "100") %>% 
         filter(`movement-model` == "\"Directed Walk\"")) +
  geom_point(aes(y = start.steps, x = start.interactions, 
                 color = climate.condition)) +
  # geom_smooth(aes(y = start.steps, x = start.interactions), 
  #             method = "lm") +
  stat_cor(mapping = aes(y = start.steps, x = start.interactions), 
           method = "spearman", p.accuracy = 0.01, r.accuracy = 0.01, 
           size = 2.5) +
  facet_wrap(~ tick.range, scales = "free_x") +
  scale_color_brewer(palette = "Set2") +
  theme(legend.position = "bottom") +
  theme(axis.text = element_text(size = 6), 
        legend.position = "bottom", 
        strip.text = element_text(size = 7))

```
Interactions are highly positively correlated with mobility throughout model run (Figure S\@ref(fig:interactions-mobility)), meaning that more mobility allows for more interactions with directed walks. 

```{r interactions-mobility-2, fig.cap="Relationship between proportion of the population foragers interact with and number of steps per foraging bout for a climatic period at the middle of model run. Relationship visualized by model scenarios with different burning costs", echo=FALSE, fig.height=6, fig.width=8, message=FALSE, warning=FALSE, out.width="100%"}
ggplot(rates %>% filter(`veg-cycle-start` == "\"productive\"") %>% 
         filter(`cycle-duration` == "100") %>% 
         filter(`movement-model` == "\"Directed Walk\"") %>%
         filter(tick.range == "1001-1100")) +
  geom_point(aes(y = start.steps, x = start.interactions, 
                 color = climate.condition)) +
  # geom_smooth(aes(y = start.steps, x = start.interactions), 
  #             method = "lm") +
  stat_cor(mapping = aes(y = start.steps, x = start.interactions), 
           method = "spearman", p.accuracy = 0.01, r.accuracy = 0.01, 
           size = 4) +
  facet_wrap(~ `burn-cost`, scales = "free_x", labeller = label_both) +
  scale_color_brewer(palette = "Set2") +
  theme(axis.text = element_text(size = 6), legend.position = "bottom")

```

The strength of these correlations is impacted by burning costs. For example, if we take a productive climate interval in the middle of model run (Figure S\@ref(fig:interactions-mobility-2)), we see significant and stronger correlations only when burning costs are low, so when burning is more frequent. 

```{r interactions-population, fig.cap="Relationship between proportion of the population foragers interact with and population density for a climatic period at the middle of model run. Relationship visualized by model scenarios with different burning costs", echo=FALSE, fig.height=6, fig.width=8, message=FALSE, warning=FALSE, out.width="100%"}
ggplot(rates %>% filter(`veg-cycle-start` == "\"productive\"") %>% 
         filter(`cycle-duration` == "100") %>% 
         filter(`movement-model` == "\"Directed Walk\"") %>%
         filter(tick.range == "1001-1100")) +
  geom_point(aes(y = start.pop.density, x = start.interactions, 
                 color = climate.condition)) +
  # geom_smooth(aes(y = start.pop.density, x = start.interactions), 
  #             method = "lm") +
  stat_cor(mapping = aes(y = start.pop.density, x = start.interactions), 
           method = "spearman", p.accuracy = 0.01, r.accuracy = 0.01, 
           size = 4) +
  facet_wrap(~ `burn-cost`, scales = "free_x", labeller = label_both) +
  scale_color_brewer(palette = "Set2") +
  theme(axis.text = element_text(size = 6), legend.position = "bottom")
```
The same is true for negative correlations between interactions and population density, although here the strongest relationship is when there is no burning cost (Figure S\@ref(fig:interactions-population)). These results occur because there is minimal change in forager mobility and therefore interactions at the highest burning costs. 

## Maintaining connections with the same foragers
In addition to understanding overall forager interaction rates, we also loosely investigated the formation of social networks. To do so, we tracked how many of a forager's interactions during a given foraging bout overlapped with the interactions of the previous bout. Doing this provides insight into whether foragers are consistently interacting with new people or if there is incipient formation of social groups. If social groups were "forming", we would expect to see increased proportions of interactions being comprised of the same foragers. 

```{r same-network-1, fig.cap="Trends in average proportion of interactions that are the same as the previous tick across model run. Trend lines are shown for each individual climatic interval. Results shown for model scenarios with long climatic cycles (250 ticks)", echo=FALSE, fig.height=5, fig.width=8, message=FALSE, warning=FALSE}
plot.data3 = data %>% filter(ticks > 0) %>% 
  filter(`cycle-duration` == 250) %>% 
  filter(`veg-cycle-start` == "\"productive\"")
plot.data3$`burn-cost` =  as.factor(plot.data3$`burn-cost`)

ggplot(plot.data3) +
  # geom_smooth(data = plot.data3, 
  #             mapping = aes(x = ticks, y = same.fi.prop, color = `burn-cost`)) +
  geom_smooth(data = plot.data3 %>% filter(ticks > 0 & ticks <= 250), 
              mapping = aes(x = ticks, y = same.fi.prop, 
                            color = climate.condition), 
              method = "lm") +
  geom_smooth(data = plot.data3 %>% filter(ticks > 250 & ticks <= 500), 
              mapping = aes(x = ticks, y = same.fi.prop, 
                            color = climate.condition), 
              method = "lm") +
  geom_smooth(data = plot.data3 %>% filter(ticks > 500 & ticks <= 750), 
              mapping = aes(x = ticks, y = same.fi.prop, 
                            color = climate.condition), 
              method = "lm") +
  geom_smooth(data = plot.data3 %>% filter(ticks > 750 & ticks <= 1000), 
              mapping = aes(x = ticks, y = same.fi.prop, 
                            color = climate.condition), 
              method = "lm") +
  geom_smooth(data = plot.data3 %>% filter(ticks > 1000 & ticks <= 1250), 
              mapping = aes(x = ticks, y = same.fi.prop, 
                            color = climate.condition), 
              method = "lm") +
  geom_smooth(data = plot.data3 %>% filter(ticks > 1250 & ticks <= 1500), 
              mapping = aes(x = ticks, y = same.fi.prop, 
                            color = climate.condition), 
              method = "lm") +
  geom_smooth(data = plot.data3 %>% filter(ticks > 1500 & ticks <= 1750), 
              mapping = aes(x = ticks, y = same.fi.prop, 
                            color = climate.condition), 
              method = "lm") +
  geom_smooth(data = plot.data3 %>% filter(ticks > 1750 & ticks <= 2000), 
              mapping = aes(x = ticks, y = same.fi.prop, 
                            color = climate.condition), 
              method = "lm") +
  geom_smooth(data = plot.data3 %>% filter(ticks > 2000 & ticks <= 2250), 
              mapping = aes(x = ticks, y = same.fi.prop, 
                            color = climate.condition), 
              method = "lm") +
  geom_smooth(data = plot.data3 %>% filter(ticks > 2250 & ticks <= 2500), 
              mapping = aes(x = ticks, y = same.fi.prop, 
                            color = climate.condition), 
              method = "lm") +
  geom_smooth(data = plot.data3 %>% filter(ticks > 2500 & ticks <= 2750), 
              mapping = aes(x = ticks, y = same.fi.prop, 
                            color = climate.condition), 
              method = "lm") +
  geom_smooth(data = plot.data3 %>% filter(ticks > 2750 & ticks <= 3000), 
              mapping = aes(x = ticks, y = same.fi.prop, 
                            color = climate.condition), 
              method = "lm") +
  geom_smooth(data = plot.data3 %>% filter(ticks > 3000 & ticks <= 3250), 
              mapping = aes(x = ticks, y = same.fi.prop, 
                            color = climate.condition), 
              method = "lm") +
  geom_smooth(data = plot.data3 %>% filter(ticks > 3250 & ticks <= 3500), 
              mapping = aes(x = ticks, y = same.fi.prop, 
                            color = climate.condition), 
              method = "lm") +
  #geom_vline(aes(xintercept = 2500), color = "black") +
  facet_grid(`movement-model` ~ `burn-cost`, 
             labeller = label_both, scales = "free") +
  scale_color_colorblind() +
  theme(strip.text = element_text(size = 6), 
        legend.title = element_blank(), 
        legend.position = "bottom", 
        axis.title = element_text(size = 7.5),
        axis.text = element_text(size = 7)) +
  guides(fill = "none") + 
  labs(y = "average same interaction proportion")

```

When we plot the change in average proportion of interactions that are the same as the previous tick across model run by burn cost and movement model, we see that random walks result in overall higher proportions of agents interacting with the same people compared to directed walks (Figure S\@ref(fig:same-network-1)). This is driven primarily by high rates of similar interactions in unproductive periods, particularly when burning costs are high. Conversely, with directed walks, we see an initial dip in the proportion of interactions that are with the same people as the population is establishing itself. This makes sense because the population is relatively unstable at this time, so there will be more new people on the landscape. If we consider after that burn in period, we see that the proportion of interactions that are with the same people starts to increase again and remains higher as the population reaches equilibrium and carrying capacity (Figure S\@ref(fig:same-network-1)). Because directed walks also result in fewer interactions over the course of model run, this suggests that directed walks in landscapes with a long history of burning and stable population result in smaller social networks, with foragers frequently interacting with the same people.  

# Spatial distribution of burning events  

Because burning behaviors have such a significant impact on the structure of the vegetation in the environment, we were curious if this is caused by differential use of space. To examine this, we looked at the spatial autocorrelation of where burning events occur within the landscape to assess land use by the agents.For this, we only consider significant values of Moran's I to evaluate clustering (positive values) and dispersion (negative values).

```{r burning-events-1, echo=FALSE, message=FALSE, warning=FALSE, out.width="100%",fig.height=5}
parameters = c(
  "cycle_duration",  # 100, 250
  "veg_cycle_start", # productive, unproductive
  "veg_distribution", # random, clustered
  "burnt_neighbor_limit", # 1, 4, 8
  "burn_cost", # 0, 50
  "burn_veg_type_threshold", # 4, 7
  "movement_model" #Random, Directed
)

be.morans.100 <- readRDS("../results/outputs/be_morans.i_cycle.100.rds")
be.morans.100[,parameters[-1]] = lapply(be.morans.100[,parameters[-1]] , as.factor)
be.morans.250 <- readRDS("../results/outputs/be_morans.i_cycle.250.rds")
be.morans.250[,parameters[-1]] = lapply(be.morans.250[,parameters[-1]] , as.factor)

be.morans.100$veg_distribution = factor(be.morans.100$veg_distribution, 
                                        levels = c("\"random\"", 
                                                   "\"clustered\""))
be.morans.250$veg_distribution = factor(be.morans.250$veg_distribution, 
                                        levels = c("\"random\"", 
                                                   "\"clustered\""))

be.morans.100$movement_model = factor(be.morans.100$movement_model, 
                                      levels = c("\"Random Walk\"", 
                                                 "\"Directed Walk\""))
be.morans.250$movement_model = factor(be.morans.250$movement_model, 
                                      levels = c("\"Random Walk\"", 
                                                 "\"Directed Walk\""))

be.morans.100 = be.morans.100 %>% filter(exp %in% finished.exp)
be.morans.250 = be.morans.250 %>% filter(exp %in% finished.exp)

be.morans = bind_rows(be.morans.100, be.morans.250) %>%
  mutate(across(parameters, .fns = as.factor))

ggplot(be.morans %>% 
         filter(signif == T)) +
  geom_boxplot(aes(x = ticks, y = morans.i, group = ticks), alpha = 0.75) +
  facet_grid(movement_model ~ veg_distribution, labeller = label_both)

```

Preliminary observation of the data shows that the different parameters show different trends in the spatial autocorrelation of burning events. Specifically we can see a trend towards dispersion when the underlying vegetation distribution is random, particularly with directed walks. We also see a trend towards highly clustered burning events when the underlying vegetation distribution is clustered; however, this effect is dampened with directed walks. To more formally investigate this, we performed an aligned ranks transformation ANOVA to statistically assess the effects of the different parameters, and their two-way interactions, on the final value of Moran's I of burning events.


```{r burning-events-1-1, echo=TRUE, message=FALSE, warning=FALSE, out.width="100%",fig.height=4}
art_be_morans = ARTool::art(morans.i ~ cycle_duration * veg_distribution * burn_cost * burn_veg_type_threshold * burnt_neighbor_limit * movement_model, data = be.morans %>% filter(ticks == 3500))
anova_be = anova(art_be_morans)

sig_effects_be = subset(anova_be, `Pr(>F)` < 0.05)

es_be = effectsize::eta_squared(sig_effects_be, partial = T)
es_ranked_be = es_be[order(-es_be$Eta2_partial), ]
head(es_ranked_be, 10)

```

We can see that burning costs/limits still have the highest effect size on the clustering/dispersion of burning events, likely because they dictate how many burning events there will be, but after that it is underlying vegetation distribution and movement model that have the next highest effect sizes. 

```{r burning-events-2-2-2, fig.cap="Trends of spatial autocorrelation of burning events across model run for model scenarios with directed walks", echo=FALSE, message=FALSE, warning=FALSE, fig.height=7, out.width="100%"}
p2.2 = ggplot(be.morans.100 %>% filter(signif == T) %>% 
                filter(movement_model == "\"Directed Walk\"")) +
  geom_point(mapping = aes(x = ticks, y = morans.i, 
                           color = as.factor(veg_distribution)), alpha = 0.1) +
  geom_smooth(mapping = aes(x = ticks, y = morans.i, 
                            color = as.factor(veg_distribution), 
                            group = as.factor(veg_distribution))) +
  geom_hline(aes(yintercept = 0)) +
  facet_grid(burnt_neighbor_limit ~ burn_cost, 
             scales = "free", 
             labeller = labeller(burn_cost = bc.labs, 
                                 burn_veg_type_threshold = bt.labs, 
                                 burnt_neighbor_limit = bn.labs)) +
  theme(axis.text = element_text(size = 8), 
        strip.text = element_text(size = 8), 
        legend.position = "bottom")

plot(p2.2)

```

```{r burning-events-2-2-1, fig.cap="Trends of spatial autocorrelation of burning events across model run for model scenarios with random walks", echo=FALSE, message=FALSE, warning=FALSE, fig.height=7, out.width="100%"}
p1.2 = ggplot(be.morans.100 %>% filter(signif == T) %>% 
                filter(movement_model == "\"Random Walk\"")) +
  geom_point(mapping = aes(x = ticks, y = morans.i, 
                           color = as.factor(veg_distribution)), alpha = 0.1) +
  geom_smooth(mapping = aes(x = ticks, y = morans.i, 
                            color = as.factor(veg_distribution), 
                            group = as.factor(veg_distribution))) +
  geom_hline(aes(yintercept = 0)) +
  facet_grid(burnt_neighbor_limit ~ burn_cost, 
             scales = "free", 
             labeller = labeller(burn_cost = bc.labs, 
                                 burn_veg_type_threshold = bt.labs, 
                                 burnt_neighbor_limit = bn.labs))+
  theme(axis.text = element_text(size = 8), 
        strip.text = element_text(size = 8), 
        legend.position = "bottom")

plot(p1.2)
```

Plotting the trends of burning event spatial autocorrelation through time by these significant parameters allows us to better visualize these patterns. Here, we split the data by movement model with trends for directed walks (Figure S\@ref(fig:burning-events-2-2-2)) and trend lines for random walks (Figure S\@ref(fig:burning-events-2-2-1)). 

First, it is clear that, under random walks, underlying distribution of vegetation potential has a significant impact on clustering or disperson of burning events (Figure S\@ref(fig:burning-events-2-2-1)). This is especially true when burning is limited to specific patches under low burning costs. As burning costs increase, and burning becomes more infrequent, burning events are more likely to cluster despite limits on which patches can be burnt. 

With directed walks, the effect of underlying vegetation potential is more varied (Figure S\@ref(fig:burning-events-2-2-2)). For example, when agents can burn any vegetation type, underlying vegetation potential does not change the trend towards spatial randomness or dispersion of burning events. When agents can only burn specific vegetation types, underlying vegetation potential is more important, particularly in cases where patches can have more burnt neighbors. In these cases, underlying clustering of vegetation type potential leads to more clustering of burning events.  

# References

```{r citations, echo=FALSE, message=FALSE, warning=FALSE}
grateful::cite_packages(
  output = "paragraph",
  out.format = "pdf",
  out.dir = ".",
  omit = c("QuantPsyc", "marginaleffects")
)

```
