---
title: "ForageModv02 Supplementary Analysis"
output:
  html_document:
    toc: true
    toc_depth: 2
bibliography: grateful-refs.bib
csl: pnas.csl
---

```{r load-data, message=FALSE, warning=FALSE, include=FALSE}
library(knitr)
library(broom)
library(tidyverse)
library(rcompanion)
library(fitdistrplus)
library(gtsummary)
library(jtools)
library(betareg)
library(mgcv)
library(ggpubr)
library(ggthemes)
library(lme4)
theme_set(theme_bw())

data = readRDS("../results/bb-data.rds")

parameters = c(
  "natural-ignition", # 0.00, 0.05
  "cycle-duration",  # 100, 250
  "veg-cycle-start", # productive, unproductive
  "veg-distribution", # random, clustered
  "burnt-neighbor-limit", # 1, 4, 8
  "burn-cost", # 0, 50
  "burn-veg-type-threshold", # 4, 7
  "movement-model" #Random, Directed
)
data[,parameters] = lapply(data[,parameters], as.factor)
data$`veg-distribution` = factor(data$`veg-distribution`, levels = c("\"random\"", "\"clustered\""))
data$`movement-model` = factor(data$`movement-model`, levels = c("\"Random Walk\"", "\"Directed Walk\""))

data$adj.fi = data$mean.fi/data$pop.count
data$pop.dens = data$pop.count/(51*51)

data$benefit.ratio = data$benefit_self/data$benefit_other
data$benefit.ratio = ifelse(is.nan(data$benefit.ratio), NA, data$benefit.ratio)

data$burnt = data$`veg_-1`
```

## Population maintenance?

First, we checked to see whether all model runs maintained a population across all 2000 ticks.

```{r pop-maintenance, echo=TRUE, message=FALSE, warning=FALSE}
all.exp = unique(data$exp)

end.tick = unique(data$`tick-limit`)
fd = data %>% filter(ticks == end.tick)
finished.exp = unique(fd$exp)

finished.data = data %>% filter(exp %in% finished.exp)
unfinished.data = data %>% filter(!(exp %in% finished.exp))
length(unique(unfinished.data$exp))

```

Approximately 9% (665 runs) of our modeled scenarios resulted in population extinction. Here we show how failures counts break down by the different parameters:

```{r pop-maintenance_2, echo=FALSE, message=FALSE, warning=FALSE}
lapply((unfinished.data %>% select_at(c("exp", parameters)) %>% distinct())[,parameters], table)
```

Nearly all of the model runs that could not sustain a population had costs to burning behaviors that matched or exceeded the energetic benefits gained from burning. Interestingly, in all of these model runs, foragers use random walks. This suggests that a directed mobility strategy is enough to offset the impact of high costs of burning behaviors. Across the other parameters, those that end in fail are more or less equally spread.

We filter out these unsuccessful runs to avoid issues in analyzing trends over the course of model run.

```{r filter-out-unsuccessful-runs, echo=TRUE, message=FALSE, warning=FALSE}
data = data %>% filter(exp %in% finished.exp)
```

## Correlations of outputs over time

Next, we looked at the correlation between outputs across model runs.

```{r output-correlations_1, echo=FALSE, message=FALSE, warning=FALSE, out.width="100%", fig.height=4, out.height='75%'}

outputs = c(
  #"pop.count",
  "pop.dens", #pop count/world size
  "burnt", 
  "mean.burn.prob", 
  #"mean.fi", #average forager interaction count
  "adj.fi", #average interaction count/ population count
  "mean.fm",  #average forager movements per capita
  "benefit_self", #
  "benefit_other"
  #"benefit.ratio"
)

pvalue = psych::corr.test(data %>% select_at(outputs))$p
corrplot::corrplot(cor(data %>% select_at(outputs), use = "pairwise.complete.obs"),
                   method = "square", addCoef.col = "black", 
                   col = scales::alpha(corrplot::COL2("RdBu"), alpha = 0.85),
                   p.mat = pvalue, insig="blank", sig.level=0.1, 
                   type = "lower", number.cex = 0.5, diag=F)

```

We can see that population density is strongly positively correlated with mean burning probability (*mean.burn.prob*). This indicates that large populations are more likely to burn the landscape. This contextualizes the positive correlation between population density and proportion of burnt landscape (*burnt*). We also see that population density is negatively correlated with forager movement (*mean.fm*), meaning foragers move less within large populations. Foragers also move less when they are burning the landscape more frequently.

We also investigated how these correlations change over time by looking at the correlations between outputs at 250 ticks, 1000 ticks, and 2000 ticks. For this, we also include spatial autocorrelation values of vegetation types and burning events, as well as a diversity metric of vegetation types.

```{r output-correlations_2, echo=FALSE, message=FALSE, warning=FALSE, out.width='100%'}

outputs = c(
  #"pop.count",
  "pop.dens", #pop count/world size
  "burnt", 
  "mean.burn.prob", 
  #"mean.fi", #average forager interaction count
  "adj.fi", #average interaction count/ population count
  "mean.fm",  #average forager movements per capita
  "benefit_self", #
  "benefit_other", 
  "veg_morans.i", 
  "shannon.div", 
  "be_morans.i"
)

veg.100.prod = readRDS("../results/outputs/veg_moransi_100-prod.rds")
veg.100.unprod = readRDS("../results/outputs/veg_moransi_100-unprod.rds")
veg.250.prod = readRDS("../results/outputs/veg_moransi_250-prod.rds")
veg.250.unprod = readRDS("../results/outputs/veg_moransi_250-unprod.rds")
veg.data = bind_rows(veg.100.prod, veg.100.unprod, veg.250.prod, veg.250.unprod)
be.100 = readRDS("../results/outputs/be_morans.i_cycle.100.rds")
be.250 = readRDS("../results/outputs/be_morans.i_cycle.250.rds")
be.data = bind_rows(be.100, be.250)


par(mfrow = c(1,3))
par(mar=c(0,1,0,1))
#plot at 250
data250 = data %>% dplyr::filter(ticks == 250) %>% 
  left_join(veg.data %>% 
              dplyr::filter(ticks == 250) %>% 
              dplyr::select(exp, morans.i, shannon.div, shannon.div.no0) %>% 
              rename(veg_morans.i = morans.i), 
            by = c("exp")) %>% 
  left_join(be.data %>% 
              dplyr::filter(ticks == 250) %>% 
              dplyr::select(exp, morans.i) %>%
              rename(be_morans.i = morans.i), 
            by = c("exp"))

pvalue250 = psych::corr.test(data250 %>% select_at(outputs))$p
corrplot::corrplot(cor(data250 %>% select_at(outputs), use = "pairwise.complete.obs"),
                   method = "square", addCoef.col = "black", 
                   col = scales::alpha(corrplot::COL2("RdBu"), alpha = 0.85),
                   p.mat = pvalue250, insig="blank", sig.level=0.1, 
                   type = "lower", number.cex = 0.5, diag=F)

#plot at 1000
data1000 = data %>% filter(ticks == 1000) %>% 
  left_join(veg.data %>% 
              filter(ticks == 1000) %>% 
              dplyr::select(exp, morans.i, shannon.div, shannon.div.no0) %>% 
              rename(veg_morans.i = morans.i), 
            by = c("exp")) %>% 
  left_join(be.data %>% 
              filter(ticks == 1000) %>% 
              dplyr::select(exp, morans.i) %>%
              rename(be_morans.i = morans.i), 
            by = c("exp"))

pvalue1000 = psych::corr.test(data1000 %>% select_at(outputs))$p
corrplot::corrplot(cor(data1000 %>% select_at(outputs), use = "pairwise.complete.obs"),
                   method = "square", addCoef.col = "black", 
                   col = scales::alpha(corrplot::COL2("RdBu"), alpha = 0.85),
                   p.mat = pvalue1000, insig="blank", sig.level=0.1, 
                   type = "lower", number.cex = 0.5, diag=F)

#plot at 2000
data2000 = data %>% filter(ticks == 2000) %>% 
  left_join(veg.data %>% 
              filter(ticks == 2000) %>% 
              dplyr::select(exp, morans.i, shannon.div, shannon.div.no0) %>% 
              rename(veg_morans.i = morans.i), 
            by = c("exp")) %>% 
  left_join(be.data %>% 
              filter(ticks == 2000) %>% 
              dplyr::select(exp, morans.i) %>%
              rename(be_morans.i = morans.i), 
            by = c("exp"))

pvalue2000 = psych::corr.test(data2000 %>% select_at(outputs))$p
corrplot::corrplot(cor(data2000 %>% select_at(outputs), use = "pairwise.complete.obs"),
                   method = "square", addCoef.col = "black", 
                   col = scales::alpha(corrplot::COL2("RdBu"), alpha = 0.85),
                   p.mat = pvalue2000, insig="blank", sig.level=0.1, 
                   type = "lower", number.cex = 0.5, diag=F)
```

The direction of correlations between outputs remain relatively consistent over the course of model run, either becoming more positive or more negative.

These correlations over time begin to reveal some of the model behavior, demonstrating that spatial clustering of vegetation types decreases with increased burning, but is positively correlated with forager mobility and interactions.

## Population during model run

```{r population_1, echo=FALSE, fig.height=4, fig.width=8, message=FALSE, warning=FALSE, out.width='100%'}
ggplot(data) +
  geom_smooth(aes(y = pop.dens, x = ticks, color = exp, group = exp)) +
  geom_smooth(aes(x = ticks, y = pop.dens), color = "black", se = T) +
  guides(color = "none") +
  facet_grid(`cycle-duration` ~ `veg-cycle-start`, labeller = label_both)
```

<!-- We model population density across model run with a Poisson regression. We model the change in population across time by including "ticks" as a independent variable. We also investigate the interaction between time and model parameters. -->

<!-- ```{r population_2, echo=TRUE, message=FALSE, warning=FALSE, out.width="100%", fig.height=3} -->
<!-- #hist(data$pop.count) -->
<!-- #hist(data$pop.dens) -->

<!-- pop.fit1 = glm(pop.dens ~ ticks, data = data, family = "poisson") -->
<!-- pop.fit2 = glm(pop.dens ~ ticks + (`veg-distribution` + `burnt-neighbor-limit` + `burn-cost` + `burn-veg-type-threshold` + `natural-ignition` + `veg-cycle-start` + `movement-model` + `cycle-duration`), data = data, family = "poisson") -->
<!-- pop.fit3 = glm(pop.dens ~ ticks*(`veg-distribution` + `burnt-neighbor-limit` + `burn-cost` + `burn-veg-type-threshold` + `natural-ignition` + `veg-cycle-start` + `movement-model` + `cycle-duration`), data = data, family = "poisson") -->
<!-- anova(pop.fit1, pop.fit2, pop.fit3, test = "Chisq") -->


<!-- plot_summs(pop.fit3, scale = T) -->
<!-- # pop.fit3 %>% broom::tidy() %>% -->
<!-- #   mutate(p.value = scales::pvalue(p.value)) %>% -->
<!-- #   kable() -->

<!-- ggarrange( -->
<!--   ggeffects::ggpredict(pop.fit3, terms = c("ticks", "movement-model")) %>% -->
<!--     plot(show_data = FALSE, show_ci = FALSE) + -->
<!--     theme(legend.title = element_text(size = 6),  -->
<!--           legend.text = element_text(size = 6),  -->
<!--           title = element_text(size = 8),  -->
<!--           axis.title = element_text(size = 6)),  -->
<!--   ggeffects::ggpredict(pop.fit3, terms = c("ticks", "burnt-neighbor-limit")) %>% -->
<!--     plot(show_data = FALSE, show_ci = FALSE) + -->
<!--     theme(legend.title = element_text(size = 6), title = element_text(size = 8), axis.title = element_text(size = 6)),  -->
<!--   ggeffects::ggpredict(pop.fit3, terms = c("ticks", "burn-veg-type-threshold")) %>% -->
<!--     plot(show_data = FALSE, show_ci = FALSE) + -->
<!--     theme(legend.title = element_text(size = 6), title = element_text(size = 8), axis.title = element_text(size = 6)),  -->
<!--   nrow = 1, legend = "bottom" -->
<!-- ) -->

<!-- ``` -->

Population increases over time. There are fluctuations in population based on the climatic condition of the model, with steep drops in population when the landscape is unproductive. However, the overall trend of population increase is evident across all modeled scenarios.

## Forager probability of burning patches

We examined the effects of all model parameters on burning probability across model run using linear regressions. We model the effect of the different parameter settings on model behavior. We also model change over model run by including "ticks" as a independent variable. Finally, we investigate the interaction between time and model parameters.

```{r burning-probability-regression, echo=TRUE, message=FALSE, warning=FALSE, out.width='100%', fig.height=4}
hist(data$mean.burn.prob)

mbp.fit1 = lm(mean.burn.prob ~ ticks + (.), data = data %>% dplyr::select_at(c("mean.burn.prob", "ticks", parameters)))
mbp.fit2 = lm(mean.burn.prob ~ ticks:(.), data = data %>% dplyr::select_at(c("mean.burn.prob", "ticks", parameters)))
mbp.fit3 = lm(mean.burn.prob ~ ticks*(.), data = data %>% dplyr::select_at(c("mean.burn.prob", "ticks", parameters)))

anova(mbp.fit1, mbp.fit2, mbp.fit3)

plot(mbp.fit3, which = 2)

plot_summs(mbp.fit3, scale = T)
# mbp.fit3 %>% broom::tidy() %>% 
#   mutate(p.value = scales::pvalue(p.value)) %>%
#   kable()
```

Every parameter significantly affects burning probability on average across model run (independent variables) as well as how burning probability changes during model run (interaction variables). The scaled regression variables shown above also demonstrate that *burn-cost* has the strongest effect on the evolution of burning probability across model run.

```{r burning-probability-regression_2, echo=FALSE, message=FALSE, warning=FALSE, out.width='100%', fig.height=3}

ggarrange(
  #   ggeffects::ggpredict(mbp.fit3, terms = c("ticks", "veg-cycle-start")) %>%
  #     plot(show_data = FALSE, show_ci = FALSE) +
  #     theme(legend.title = element_text(size = 6), title = element_text(size = 8), axis.title = element_text(size = 6)), 
  #   ggeffects::ggpredict(mbp.fit3, terms = c("ticks", "cycle-duration")) %>%
  #     plot(show_data = FALSE, show_ci = FALSE) +
  #     theme(legend.title = element_text(size = 6), title = element_text(size = 8), axis.title = element_text(size = 6)), 
  #   ggeffects::ggpredict(mbp.fit3, terms = c("ticks", "veg-distribution")) %>%
  #     plot(show_data = FALSE, show_ci = FALSE) +
  #     theme(legend.title = element_text(size = 6), title = element_text(size = 8), axis.title = element_text(size = 6)), 
  #   ggeffects::ggpredict(mbp.fit3, terms = c("ticks", "movement-model")) %>%
  #     plot(show_data = FALSE, show_ci = FALSE) +
  #     theme(legend.title = element_text(size = 6), title = element_text(size = 8), axis.title = element_text(size = 6))
  # )
  # ggarrange(
  #   ggeffects::ggpredict(mbp.fit3, terms = c("ticks", "natural-ignition")) %>%
  #     plot(show_data = FALSE, show_ci = FALSE) +
  #     theme(legend.title = element_text(size = 6), title = element_text(size = 8), axis.title = element_text(size = 6)), 
  ggeffects::ggpredict(mbp.fit3, terms = c("ticks", "burnt-neighbor-limit")) %>%
    plot(show_data = FALSE, show_ci = FALSE) +
    theme(legend.title = element_text(size = 6), title = element_text(size = 8), axis.title = element_text(size = 6)), 
  ggeffects::ggpredict(mbp.fit3, terms = c("ticks", "burn-veg-type-threshold")) %>%
    plot(show_data = FALSE, show_ci = FALSE) +
    theme(legend.title = element_text(size = 6), title = element_text(size = 8), axis.title = element_text(size = 6)), 
  ggeffects::ggpredict(mbp.fit3, terms = c("ticks", "burn-cost")) %>%
    plot(show_data = FALSE, show_ci = FALSE) +
    theme(legend.title = element_text(size = 6), title = element_text(size = 8), axis.title = element_text(size = 6)), 
  nrow = 1, legend = "bottom"
)
```

In general, parameters that add limits to burning behaviors (*burn-cost*, *burnt-neighbor-limit*, *burn-veg-type-threshold*) reduce the rate of increase of burning probabilities through model run. The increase of burning probabilities during model run is also faster when agents move randomly and when the environment is initially unproductive and patchy with randomly distributed resource potentials.

This model behavior is confirmed by looking at the effects of model parameters on slope of the linear relationship between ticks and burning probability.

```{r rate-of-bp-increase, echo=TRUE, message=FALSE, warning=FALSE, fig.height=6, out.width='100%'}
bp.rates = data.frame(
  exp = character(0), 
  slope = numeric(0)
)
experiments = unique(data$exp)
for(x in experiments) {
  lmdata = data %>% filter(exp == x)
  fit = lm(mean.burn.prob ~ ticks, data = lmdata)
  bp.rates[nrow(bp.rates) + 1, ] <- c(x, summary(fit)$coefficients[2,1])
}
bp.rates = bp.rates %>% left_join(data %>% select_at(c("exp", parameters)), by = "exp", multiple = "first")
bp.rates$slope = as.numeric(bp.rates$slope)

bp.rates[,parameters] = lapply(bp.rates[,parameters], as.factor)
bp.rates$`veg-distribution` = factor(bp.rates$`veg-distribution`, levels = c("\"random\"", "\"clustered\""))
bp.rates$`movement-model` = factor(bp.rates$`movement-model`, levels = c("\"Random Walk\"", "\"Directed Walk\""))

rate.fit1= lm(slope ~ ., data = bp.rates %>% select_at(c("slope", parameters)))
rate.fit2 = lm(slope ~ .:., data = bp.rates %>% select_at(c("slope", parameters)))
anova(rate.fit1, rate.fit2)

plot(rate.fit2, which = 2)

rate.fit.df = rate.fit2 %>% broom::tidy() %>%
  mutate(p.signif = ifelse(p.value < 0.05, TRUE, FALSE)) %>%
  filter(p.signif == F)

plot_summs(rate.fit2, scale = T, omit.coefs = c("(Intercept)", rate.fit.df$term))

# rate.fit2 %>% broom::tidy() %>% 
#   filter(p.value <= 0.05) %>%
#   mutate(p.value = scales::pvalue(p.value)) %>%
#   kable()
```

The parameters that have the strongest positive impacts on the rate of change of burning behaviors are those that control the limits and costs of burning. Increased burning cost always decreases the rate of change, even when interacting with other variables. Interestingly, increased burning costs have more negative effects when burning behaviors are less restricted by where foragers can perform burning behaviors. However, when burning behaviors are less restricted without a burning cost, this allows burning probabilities to increase more quickly. 

## Burnt landscape proportions

Initial correlations reveal that the proportion of burnt landscape is significantly highly correlated with population density and the average burning probability of agents.

```{r burnt-landscape-proportions_plots, echo=FALSE, message=FALSE, warning=FALSE, out.width='100%', fig.height=4}
data$burnt = data$`veg_-1`

ggarrange(
  ggplot(data) +
    geom_point(aes(x = pop.dens, y = burnt, color = ticks)),
  ggplot(data) +
    geom_point(aes(x = mean.burn.prob, y = burnt, color = ticks)),
  nrow = 1, legend = "bottom", common.legend = T
)

```

```{r veg_0-regressions_1, eval=FALSE, fig.height=4, message=FALSE, warning=FALSE, include=FALSE, out.width="100%"}

ggplot(data) +
  geom_density(aes(x = burnt, color = `burn-cost`)) +
  ggokabeito::scale_color_okabe_ito() +
  facet_grid(`burn-cost` ~ `burnt-neighbor-limit`)
```

We used regressions on the proportions of burnt landscape to look at the effects of each parameter. We compared Beta regression and logistic regressions, which are often used for modeling proportion data, and linear regressions using AIC.

```{r veg_0-regressions_2, out.width = '100%', fig.height=4, echo=TRUE, message=FALSE, warning=FALSE}
beta.data = data %>% mutate(burnt = ifelse(burnt == 0, burnt + 0.00001, burnt)) %>% mutate(burnt = ifelse(burnt == 1, burnt - 0.00001, burnt))

beta.fit1 = betareg(burnt ~ ticks*(ticks + `natural-ignition` + `cycle-duration` + 
                                       `veg-cycle-start` + `veg-distribution` + `burn-cost` + `burn-veg-type-threshold` +  `burnt-neighbor-limit` + 
                                       `movement-model`), data = beta.data %>% select_at(c("ticks", "burnt", parameters)))

log.fit1 = glm(burnt ~ ticks*(ticks + `natural-ignition` + `cycle-duration` + 
                                       `veg-cycle-start` + `veg-distribution` + `burn-cost` + `burn-veg-type-threshold` +  `burnt-neighbor-limit` + 
                                       `movement-model`), data = data %>% select_at(c("ticks", "burnt", parameters)), family = binomial)

lin.fit1 = lm(burnt ~ ticks*(ticks + `natural-ignition` + `cycle-duration` + 
                                       `veg-cycle-start` + `veg-distribution` + `burn-cost` + `burn-veg-type-threshold` +  `burnt-neighbor-limit` + 
                                       `movement-model`), data = data %>% select_at(c("ticks", "burnt", parameters)))

AIC(beta.fit1)
AIC(log.fit1)
AIC(lin.fit1)

AIC(beta.fit1) < AIC(lin.fit1)

```
Comparison of AIC shows that the Beta regression performs best.

```{r veg_0-regressions_3, echo=FALSE, fig.height=6, message=FALSE, warning=FALSE, out.width='100%'}
ggarrange(
  ggeffects::ggpredict(beta.fit1, terms = c("ticks", "natural-ignition")) %>%
    plot(show_data = FALSE, show_ci = FALSE) +
    theme(legend.title = element_text(size = 4), title = element_text(size = 6), axis.title = element_text(size = 4)), 
  ggeffects::ggpredict(beta.fit1, terms = c("ticks", "cycle-duration")) %>%
    plot(show_data = FALSE, show_ci = FALSE) +
    theme(legend.title = element_text(size = 4), title = element_text(size = 6), axis.title = element_text(size = 4)),
  ggeffects::ggpredict(beta.fit1, terms = c("ticks", "veg-cycle-start")) %>%
    plot(show_data = FALSE, show_ci = FALSE) +
    theme(legend.title = element_text(size = 4), title = element_text(size = 6), axis.title = element_text(size = 4)),
  ggeffects::ggpredict(beta.fit1, terms = c("ticks", "burn-veg-type-threshold")) %>%
    plot(show_data = FALSE, show_ci = FALSE) +
    theme(legend.title = element_text(size = 4), title = element_text(size = 6), axis.title = element_text(size = 4)), 
   ggeffects::ggpredict(beta.fit1, terms = c("ticks", "burnt-neighbor-limit")) %>%
    plot(show_data = FALSE, show_ci = FALSE) +
    theme(legend.title = element_text(size = 4), title = element_text(size = 6), axis.title = element_text(size = 4)),
  ggeffects::ggpredict(beta.fit1, terms = c("ticks", "burn-cost")) %>%
    plot(show_data = FALSE, show_ci = FALSE) +
    theme(legend.title = element_text(size = 4), title = element_text(size = 6), axis.title = element_text(size = 4)),
  ggeffects::ggpredict(beta.fit1, terms = c("ticks", "movement-model")) %>%
    plot(show_data = FALSE, show_ci = FALSE) +
    theme(legend.title = element_text(size = 4), title = element_text(size = 6), axis.title = element_text(size = 4)),
  legend = "bottom"
)

```

*TODO* Natural ignition of the landscape obviously results in higher proportions of burnt landscape, especially at the beginning of model run when burning probabilities are low. The ability to burn any patch type (*burn-veg-type-threshold* = 7) and lack of burn cost also results in higher proportions of burnt landscape through time. Finally, directed walks result in more of the landscape be burnt at a given moment throughout model run.

## Spatial clustering of vegetation types

Spatial clustering (and its converse spatial heterogeneity) of vegetation types is assessed via Moran's I values. We limit our analysis to those significant values of Moran's I to assess the degree of clustering (positive values) or dispersion (negative values). We assessed the effects of the different parameters using linear regressions.

```{r morans-i-regression_1, echo=TRUE, fig.height=4, fig.width=8, message=FALSE, warning=FALSE, out.width="100%"}
veg.100.prod = readRDS("../results/outputs/veg_moransi_100-prod.rds")
veg.100.unprod = readRDS("../results/outputs/veg_moransi_100-unprod.rds")
veg.250.prod = readRDS("../results/outputs/veg_moransi_250-prod.rds")
veg.250.unprod = readRDS("../results/outputs/veg_moransi_250-unprod.rds")

veg.100.prod = veg.100.prod %>% filter(exp %in% finished.exp)
veg.100.unprod = veg.100.unprod %>% filter(exp %in% finished.exp)
veg.250.prod = veg.250.prod %>% filter(exp %in% finished.exp)
veg.250.unprod = veg.250.unprod %>% filter(exp %in% finished.exp)

veg.100.prod = veg.100.prod %>% filter(ticks != 1000) %>% filter(ticks != 2000)
veg.100.unprod = veg.100.unprod %>% filter(ticks != 1000) %>% filter(ticks != 2000)
veg.250.prod = veg.250.prod %>% filter(ticks != 1000) %>% filter(ticks != 2000)
veg.250.unprod = veg.250.unprod %>% filter(ticks != 1000) %>% filter(ticks != 2000)

parameters = c(
  "natural_ignition", # 0.00, 0.05
  "cycle_duration",  # 100, 250
  "veg_cycle_start", # productive, unproductive
  "veg_distribution", # random, clustered
  "burnt_neighbor_limit", # 1, 4, 8
  "burn_cost", # 0, 50
  "burn_veg_type_threshold", # 4, 7
  "movement_model" #Random, Directed
)

reg.params = parameters[c(1,4:8)]
veg.100.prod[,reg.params] = lapply(veg.100.prod[,reg.params], as.factor)
veg.100.unprod[,reg.params] = lapply(veg.100.unprod[,reg.params] , as.factor)
veg.250.prod[,reg.params] = lapply(veg.250.prod[,reg.params], as.factor)
veg.250.unprod[,reg.params] = lapply(veg.250.unprod[,reg.params] , as.factor)

veg.100.prod$veg_distribution = factor(veg.100.prod$veg_distribution, levels = c("\"random\"", "\"clustered\""))
veg.100.unprod$veg_distribution = factor(veg.100.unprod$veg_distribution, levels = c("\"random\"", "\"clustered\""))
veg.250.prod$veg_distribution = factor(veg.250.prod$veg_distribution, levels = c("\"random\"", "\"clustered\""))
veg.250.unprod$veg_distribution = factor(veg.250.unprod$veg_distribution, levels = c("\"random\"", "\"clustered\""))

veg.100.prod$movement_model = factor(veg.100.prod$movement_model, levels = c("\"Random Walk\"", "\"Directed Walk\""))
veg.100.unprod$movement_model = factor(veg.100.unprod$movement_model, levels = c("\"Random Walk\"", "\"Directed Walk\""))
veg.250.prod$movement_model = factor(veg.250.prod$movement_model, levels = c("\"Random Walk\"", "\"Directed Walk\""))
veg.250.unprod$movement_model = factor(veg.250.unprod$movement_model, levels = c("\"Random Walk\"", "\"Directed Walk\""))

# hist(veg.100.prod$morans.i)
# hist(veg.100.unprod$morans.i)
# hist(veg.250.prod$morans.i)
# hist(veg.250.unprod$morans.i)

veg.100.prod.fit1 = lm(morans.i ~ ticks*(.), data = veg.100.prod %>% filter(signif == T) %>% select_at(c("ticks", "morans.i", reg.params)))

veg.100.unprod.fit1 = lm(morans.i ~ ticks*(.), data = veg.100.unprod %>% filter(signif == T) %>% select_at(c("ticks", "morans.i", reg.params)))

veg.250.prod.fit1 = lm(morans.i ~ ticks*(.), data = veg.250.prod %>% filter(signif == T) %>% select_at(c("ticks", "morans.i", reg.params)))

veg.250.unprod.fit1 = lm(morans.i ~ ticks*(.), data = veg.250.unprod %>% filter(signif == T) %>% select_at(c("ticks", "morans.i", reg.params)))

plot(veg.100.prod.fit1, which = 2)
plot(veg.100.unprod.fit1, which = 2)
plot(veg.250.prod.fit1, which = 2)
plot(veg.250.unprod.fit1, which = 2)

plot_summs(veg.100.prod.fit1, veg.100.unprod.fit1,veg.250.prod.fit1, veg.250.unprod.fit1, model.names = c(
  "start = productive, cycle = 100", 
  "start = unproductive, cycle = 100", 
  "start = productive, cycle = 250", 
  "start = unproductive, cycle = 250"
), scale = T)

```

Looking at the standardized regression coefficients, we can see that high/medium cost of burning behaviors and a directed walk movement model have the greatest impact on clustering of vegetation types. Interestingly, the underlying distribution of maximum potential vegetation types for patches has essentially no impact on spatial clustering of vegetation types relative to the other parameters. 

```{r morans-i-regression_2, echo=TRUE, fig.height=4, fig.width=8, message=FALSE, warning=FALSE,out.width="100%"}
plot_summs(veg.100.prod.fit1, veg.100.unprod.fit1,veg.250.prod.fit1, veg.250.unprod.fit1, model.names = c(
  "start = productive, cycle = 100", 
  "start = unproductive, cycle = 100", 
  "start = productive, cycle = 250", 
  "start = unproductive, cycle = 250"
), coefs = c("ticks", "natural_ignition0.05", "veg_distribution\"random\"", "burnt_neighbor_limit4", "burnt_neighbor_limit8", "burn_cost100", "burn_cost200", "burn_cost300", "burn_veg_type_threshold7", "movement_model\"Directed Walk\"")) +
  theme(legend.position = "bottom", legend.title = element_blank(), legend.text = element_text(size = 6))

```

Comparing across individual models for the experiments split by whether the model starts in a productive or unproductive state and split by the model climatic cycle duration, we can see that most of the parameters have similar effects. The parameters with significant differences in regression coefficients between the models are: *movement-model* and *natural-ignition*. We can see that when model run starts in a unproductive state and the climatic cycles are longer, Directed Walks allow for on average less spatial clustering of vegetation types. We can also see that natural ignition has a less negative effect on clustering of vegetation types when the model starts on a productive landscape.

```{r morans-i-regression_3, echo=TRUE, fig.height=6, fig.width=8, message=FALSE, warning=FALSE,out.width="100%"}
ggarrange(
  ggeffects::ggpredict(veg.100.prod.fit1, terms = c("ticks", "movement_model", "burn_cost")) %>%
    plot(show_data = FALSE, show_ci = TRUE) +
    theme(legend.title = element_text(size = 5), title = element_text(size = 8), axis.title = element_text(size = 6)) +
    labs(subtitle = "cycle = 100, start = productive"), 
  ggeffects::ggpredict(veg.100.unprod.fit1, terms = c("ticks", "movement_model", "burn_cost")) %>%
    plot(show_data = FALSE, show_ci = TRUE) +
    theme(legend.title = element_text(size = 6), title = element_text(size = 8), axis.title = element_text(size = 6)) +
    labs(subtitle = "cycle = 100, start = unproductive"), 
  ggeffects::ggpredict(veg.250.prod.fit1, terms = c("ticks", "movement_model", "burn_cost")) %>%
    plot(show_data = FALSE, show_ci = TRUE) +
    theme(legend.title = element_text(size = 6), title = element_text(size = 8), axis.title = element_text(size = 6)) +
    labs(subtitle = "cycle = 250, start = productive"), 
  ggeffects::ggpredict(veg.250.unprod.fit1, terms = c("ticks", "movement_model", "burn_cost")) %>%
    plot(show_data = FALSE, show_ci = TRUE) +
    theme(legend.title = element_text(size = 6), title = element_text(size = 8), axis.title = element_text(size = 6)) +
    labs(subtitle = "cycle = 250, start = unproductive"), 
  common.legend = T, legend = "bottom", nrow = 2, ncol = 2)

```

When we look at how vegetation clustering changes over time with different burning costs (facets) and different movement models, it is clear that directed walks result in a faster rate of decline in spatial clustering than random walks across all burning costs. When burning costs are low/none, this decrease is even steeper as more burning occurs, with spatial autocorrelation becoming more dispersed, at negative values, by the end of model run. 

## Vegetation diversity

Vegetation diversity was measured by Shannon's Diversity Index. This metric considers the proportional abundances of vegetation types to indicate whether one type dominates or abundances are more evenly spread across all types. A SDI value of 0 indicates a lack of diversity with abundance being concentrated in a single species. Higher SDI values indicate more diversity of vegetation types.

```{r veg-diversity-distribution, echo=FALSE, fig.height=4, message=FALSE, warning=FALSE, out.width='100%'}
veg.data = bind_rows(veg.100.prod, veg.100.unprod, veg.250.prod, veg.250.unprod) 

hist(veg.data$shannon.div)

ggplot(veg.data) +
  geom_density(aes(x = shannon.div, color = movement_model))

```

The distribution of this metric is bimodal across model runs. This bimodality is caused by the different movement models used: directed walks result in less diversity than random walks.

We fit a GAM to vegetation type diversity for model runs with random walks because it is a better fit than a linear model. We use GAM to investigate how the effects of the parameters change through time.

```{r veg-diversity-regression_1, echo=TRUE, fig.height=3, message=FALSE, warning=FALSE, out.width='100%'}
veg.data.r = veg.data %>% filter(movement_model == "\"Random Walk\"")
reg.params = parameters = c(
  "natural_ignition", # 0.00, 0.05
  "cycle_duration",  # 100, 250
  "veg_cycle_start", # productive, unproductive
  "veg_distribution", # random, clustered
  "burnt_neighbor_limit", # 1, 4, 8
  "burn_cost", # 0, 50
  "burn_veg_type_threshold"
)
veg.data.r[,reg.params] = lapply(veg.data.r [,reg.params], as.factor)

rw.gam1 = gam(shannon.div ~ 
                s(ticks, by = natural_ignition) + 
                s(ticks, by = veg_cycle_start) + 
                s(ticks, by = veg_distribution) + 
                s(ticks, by = burn_cost)  +  
                s(ticks, by = burn_veg_type_threshold) + 
                s(ticks, by = burnt_neighbor_limit) +
                s(ticks, by = cycle_duration), data = veg.data.r)

rw.gam2 = gam(shannon.div ~ natural_ignition + veg_cycle_start + veg_distribution + burn_cost + burn_veg_type_threshold + burnt_neighbor_limit + cycle_duration +
                s(ticks, by = natural_ignition) + 
                s(ticks, by = veg_cycle_start) + 
                s(ticks, by = veg_distribution) + 
                s(ticks, by = burn_cost)  +  
                s(ticks, by = burn_veg_type_threshold) + 
                s(ticks, by = burnt_neighbor_limit) +
                s(ticks, by = cycle_duration), data = veg.data.r)

anova(rw.gam1, rw.gam2, test = "Chisq")

rw.fit1 = lm(shannon.div ~ ticks*(.), data = veg.data.r %>% select_at(c("ticks", "shannon.div", reg.params)))

AIC(rw.gam2)
AIC(rw.fit1)

qq.gam(rw.gam2)

```

```{r veg-diversity-regression_1_2, echo=TRUE, fig.height=3, message=FALSE, warning=FALSE, out.width='100%'}
par(mfrow=c(1,2), cex=0.8)
plot(rw.gam2, select=1, shade=T)
abline(h=0, lty = 2)
plot(rw.gam2, select=2, shade=T)
abline(h=0, lty = 2)

```

When there is natural ignition events in the model, we can see that vegetation diversity steadily decreases. Conversely, without natural ignition events, there is initially an increase in vegetation diversity and then a steady decreases. This is likely because diversity decreases as the proportion of burnt landscape steadily increases over model run. Having natural ignition events simply creates even more burnt landscape.

```{r veg-diversity-regression_1_3, echo=TRUE, fig.height=3, message=FALSE, warning=FALSE, out.width='100%'}
par(mfrow=c(1,2), cex=0.8)
plot(rw.gam2, select=3, shade=T)
abline(h=0, lty = 2)
plot(rw.gam2, select=4, shade=T)
abline(h=0, lty = 2)

```

The starting environmental conditions do not appear to have a large effect on vegetation diversity.

```{r veg-diversity-regression_1_4, echo=TRUE, fig.height=3, message=FALSE, warning=FALSE, out.width='100%'}
par(mfrow=c(1,2), cex=0.8)
plot(rw.gam2, select=5, shade=T)
abline(h=0, lty = 2)
plot(rw.gam2, select=6, shade=T)
abline(h=0, lty = 2)

```

The underlying distribution of resource potential, or maximum vegetation type value, also do not have different effects on vegetation diversity - both distributions have slightly increasingly positive effects over the course of model run.

```{r veg-diversity-regression_1_5, echo=TRUE, fig.height=6, message=FALSE, warning=FALSE, out.width='100%'}
par(mfrow=c(2,2), cex=0.8)
plot(rw.gam2, select=7, shade=T)
abline(h=0, lty = 2)
plot(rw.gam2, select=8, shade=T)
abline(h=0, lty = 2)
plot(rw.gam2, select=9, shade=T)
abline(h=0, lty = 2)
plot(rw.gam2, select=10, shade=T)
abline(h=0, lty = 2)
```

Having a cost associated with burning introduces a larger effect on vegetation diversity than no or low costs of burning. This is likely related to the fact that a burning cost reduces the amount of burning over the course of model run, allowing for a landscape that is not dominated by burnt patches.

```{r veg-diversity-regression_1_6, echo=TRUE, fig.height=3, message=FALSE, warning=FALSE, out.width='100%'}
par(mfrow=c(1,2), cex=0.8)
plot(rw.gam2, select=11, shade=T)
abline(h=0, lty = 2)
plot(rw.gam2, select=12, shade=T)
abline(h=0, lty = 2)
```

Similarly, stricter limits on what types of vegetation can be burned also allows for more vegetation diversity by the end of model run.

```{r veg-diversity-regression_1_7, echo=TRUE, fig.height=3, message=FALSE, warning=FALSE, out.width='100%'}
par(mfrow=c(1,3), cex=0.8)
plot(rw.gam2, select=13, shade=T)
abline(h=0, lty = 2)
plot(rw.gam2, select=14, shade=T)
abline(h=0, lty = 2)
plot(rw.gam2, select=15, shade=T)
abline(h=0, lty = 2)
```

This same pattern is seen even more distinctly with the stricter burnt neighbor limits. 

```{r veg-diversity-regression_1_8, echo=TRUE, fig.height=3, message=FALSE, warning=FALSE, out.width='100%'}
par(mfrow=c(1,2), cex=0.8)
plot(rw.gam2, select=16, shade=T)
abline(h=0, lty = 2)
plot(rw.gam2, select=17, shade=T)
abline(h=0, lty = 2)
```

Both values of cycle duration have similar effects.

We fit a second GAM to vegetation type diversity for model runs with directed walks.

```{r veg-diversity-regression_2, echo=TRUE, fig.height=3, message=FALSE, warning=FALSE, out.width='100%'}
veg.data.d = veg.data %>% filter(movement_model == "\"Directed Walk\"")
reg.params = parameters = c(
  "natural_ignition", # 0.00, 0.05
  "cycle_duration",  # 100, 250
  "veg_cycle_start", # productive, unproductive
  "veg_distribution", # random, clustered
  "burnt_neighbor_limit", # 1, 4, 8
  "burn_cost", # 0, 50
  "burn_veg_type_threshold"
)
veg.data.d[,reg.params] = lapply(veg.data.d[,reg.params], as.factor)

dw.gam1 = gam(shannon.div ~ s(ticks, by = natural_ignition) + 
                s(ticks, by = veg_cycle_start) + 
                s(ticks, by = veg_distribution) + 
                s(ticks, by = burn_cost)  +  
                s(ticks, by = burn_veg_type_threshold) + 
                s(ticks, by = as.factor(burnt_neighbor_limit)) +
                s(ticks, by = cycle_duration), data = veg.data.d)

dw.gam2 = gam(shannon.div ~ natural_ignition + veg_cycle_start + veg_distribution + burn_cost + burn_veg_type_threshold + burnt_neighbor_limit + cycle_duration +
                s(ticks, by = natural_ignition) + 
                s(ticks, by = veg_cycle_start) + 
                s(ticks, by = veg_distribution) + 
                s(ticks, by = burn_cost)  +  
                s(ticks, by = burn_veg_type_threshold) + 
                s(ticks, by = burnt_neighbor_limit) +
                s(ticks, by = cycle_duration), data = veg.data.d)

anova(dw.gam1, dw.gam2, test = "Chisq")

dw.fit1 = lm(shannon.div ~ ticks*(.), data = veg.data.d %>% select_at(c("ticks", "shannon.div", reg.params)))

AIC(dw.gam2)
AIC(dw.fit1)

qq.gam(dw.gam2)

```

Overall with directed walks, we get very similar parameter effects through time for most of the parameters. There are, however, key differences in the effects of burning costs and limits to where burning can occur.

```{r veg-diversity-regression_2_2, echo=TRUE, fig.height=3, message=FALSE, warning=FALSE, out.width='100%'}
par(mfrow=c(1,2), cex=0.8)
plot(dw.gam2, select=1, shade=T)
abline(h=0, lty = 2)
plot(dw.gam2, select=2, shade=T)
abline(h=0, lty = 2)

```

For directed walks, natural ignition does not have a very large effect on vegetation diversity.

```{r veg-diversity-regression_2_3, echo=TRUE, fig.height=3, message=FALSE, warning=FALSE, out.width='100%'}
par(mfrow=c(1,2), cex=0.8)
plot(dw.gam2, select=3, shade=T)
abline(h=0, lty = 2)
plot(dw.gam2, select=4, shade=T)
abline(h=0, lty = 2)

```

We again see similar effects of both starting vegetation conditions on vegetation diversity across model run.

```{r veg-diversity-regression_2_4, echo=TRUE, fig.height=3, message=FALSE, warning=FALSE, out.width='100%'}
par(mfrow=c(1,2), cex=0.8)
plot(dw.gam2, select=5, shade=T)
abline(h=0, lty = 2)
plot(dw.gam2, select=6, shade=T)
abline(h=0, lty = 2)

```

The underlying distribution of resource potential, or maximum vegetation type value, have essentially no effect on vegetation diversity with directed walks. This means that the human behavior is more important for structuring the environment with this movement model.  

```{r veg-diversity-regression_2_5, echo=TRUE, fig.height=6, message=FALSE, warning=FALSE, out.width='100%'}
par(mfrow=c(2,2), cex=0.8)
plot(dw.gam2, select=7, shade=T)
abline(h=0, lty = 2)
plot(dw.gam2, select=8, shade=T)
abline(h=0, lty = 2)
plot(dw.gam2, select=9, shade=T)
abline(h=0, lty = 2)
plot(dw.gam2, select=10, shade=T)
abline(h=0, lty = 2)

```

With directed walks, we can see that low and medium costs for burning behaviors have similar effects: at first negative, since burning is required to introduce new vegetation types, but then becoming positive as more burning is allowed to occur. We see a similar initial pattern with no burning costs; however, by the end of model run, the huge amount of burning leads to too many burnt patches that decreases the overall diversity of vegetation on the landscape. High burning cost has the opposite effect pattern, but a much more limited effect size. This is likely because high burning costs severely limits burning behaviors and therefore does not have a substantial impact on what vegetation types are available on the landscape. 

```{r veg-diversity-regression_2_6, echo=TRUE, fig.height=3, message=FALSE, warning=FALSE, out.width='100%'}
par(mfrow=c(1,2), cex=0.8)
plot(dw.gam2, select=11, shade=T)
abline(h=0, lty = 2)
plot(dw.gam2, select=12, shade=T)
abline(h=0, lty = 2)

par(mfrow=c(1,3), cex=0.8)
plot(dw.gam2, select=13, shade=T)
abline(h=0, lty = 2)
plot(dw.gam2, select=14, shade=T)
abline(h=0, lty = 2)
plot(dw.gam2, select=15, shade=T)
abline(h=0, lty = 2)
```

```{r veg-diversity-regression_2_7, eval=FALSE, fig.height=3, message=FALSE, warning=FALSE, include=FALSE, out.width='100%'}

```

The limits on burning behaviors have more exaggerated effects with directed walks. We can again see clearly that more burning (with relaxed burning restrictions) reduces overall vegetation diversity by the end of model run.

```{r veg-diversity-regression_2_8, echo=TRUE, fig.height=3, message=FALSE, warning=FALSE, out.width='100%'}
par(mfrow=c(1,2), cex=0.8)
plot(dw.gam2, select=16, shade=T)
abline(h=0, lty = 2)
plot(dw.gam2, select=17, shade=T)
abline(h=0, lty = 2)
```

Cycle duration appears to have no effect on vegetation diversity with directed walks.

<!-- ### Vegetation diversity omitting burnt patches? -->

<!-- The lack of vegetation type diversity in the model contradicts evidence from the ethnographic record that indicates Shannon's Diversity should increase with anthropogenic burning. -->

<!-- However, above we include burnt patches within the diversity calculations, which may be skewing the results because burnt patches make up the majority of the landscape as burning becomes more frequent. -->

<!-- ```{r issues-with-SDI, eval=FALSE, include=FALSE} -->
<!-- veg.long = data %>% pivot_longer(c(veg_0, veg_1, veg_2, veg_3, veg_4, veg_5, veg_6, veg_7), names_to = "veg_type", values_to = "proportion") -->

<!-- ggplot(veg.long) + -->
<!--   geom_point(aes(x = ticks, y = proportion, color = veg_type)) + -->
<!--   facet_grid(`veg-cycle-start` ~ `cycle-duration`, scales = "free") -->

<!-- ``` -->

<!-- We recalculated SDI omitting the burnt patches to understand if the diversity of other vegetation types increases over model run. -->

<!-- ```{r SDI-no-burnt_1, echo=FALSE, fig.height=5, message=FALSE, warning=FALSE, out.width='100%'} -->
<!-- ggplot(veg.data %>% filter(signif == T)) + -->
<!--   geom_jitter(data = veg.data %>% filter(signif == T) %>% filter(burn_cost == 0), mapping = -->
<!--                 aes(x = ticks, y = shannon.div.no0, group = ticks, color = burn_cost), alpha = 0.1, size = 0.25) + -->
<!--   geom_jitter(data = veg.data %>% filter(signif == T) %>% filter(burn_cost == 100), mapping = -->
<!--                 aes(x = ticks, y = shannon.div.no0, group = ticks, color = burn_cost), alpha = 0.1, size = 0.25) + -->
<!--   geom_jitter(data = veg.data %>% filter(signif == T) %>% filter(burn_cost == 200), mapping = -->
<!--                 aes(x = ticks, y = shannon.div.no0, group = ticks, color = burn_cost), alpha = 0.1, size = 0.25) + -->
<!--   geom_jitter(data = veg.data %>% filter(signif == T) %>% filter(burn_cost == 300), mapping = -->
<!--                 aes(x = ticks, y = shannon.div.no0, group = ticks, color = burn_cost), alpha = 0.1, size = 0.25) + -->
<!--   geom_smooth(mapping = aes(x = ticks, y = shannon.div.no0, color = burn_cost)) + -->
<!--   facet_grid(movement_model ~ cycle_duration + veg_cycle_start , labeller = label_both) + -->
<!--   labs(color = "", y = "Shannon Diversity Index") + -->
<!--   scale_color_brewer(palette = "Set2", -->
<!--                      labels = c("no burn cost (0)", "low burn cost (100)", "medium burn cost (200)", "high burn cost (300)")) + -->
<!--   theme(legend.position = "bottom", strip.text = element_text(size = 6.5),) -->

<!-- ``` -->

<!-- When we omit burnt patches from our diversity calculations, we can see that diversity does indeed increase over the course of model run when agents perform random walks. Clearly, directed walks still result in very reduced vegetation diversity, although there is some increasing positive variation in this by the end of model runs. -->

<!-- We again fit a GAM to investigate how the other parameters affect the increase in diversity of vegetation types excluding burnt patches. -->

<!-- ```{r SDI-no-burnt_2, echo=FALSE, fig.height=3, message=FALSE, warning=FALSE, out.width='100%'} -->
<!-- rw.no0.gam1 = gam(shannon.div.no0 ~  -->
<!--                 s(ticks, by = natural_ignition) +  -->
<!--                 s(ticks, by = veg_cycle_start) +  -->
<!--                 s(ticks, by = veg_distribution) +  -->
<!--                 s(ticks, by = burn_cost)  +   -->
<!--                 s(ticks, by = burn_veg_type_threshold) +  -->
<!--                 s(ticks, by = burnt_neighbor_limit) + -->
<!--                 s(ticks, by = cycle_duration), data = veg.data.r) -->

<!-- rw.no0.gam2 = gam(shannon.div.no0 ~ natural_ignition + veg_cycle_start + veg_distribution + burn_cost + burn_veg_type_threshold + burnt_neighbor_limit + cycle_duration + -->
<!--                 s(ticks, by = natural_ignition) +  -->
<!--                 s(ticks, by = veg_cycle_start) +  -->
<!--                 s(ticks, by = veg_distribution) +  -->
<!--                 s(ticks, by = burn_cost)  +   -->
<!--                 s(ticks, by = burn_veg_type_threshold) +  -->
<!--                 s(ticks, by = burnt_neighbor_limit) + -->
<!--                 s(ticks, by = cycle_duration), data = veg.data.r) -->

<!-- anova(rw.no0.gam1, rw.no0.gam2, test = "Chisq") -->

<!-- qq.gam(rw.no0.gam2) -->
<!-- ``` -->

<!-- We investigate how the effect trends of the parameters that result in more or less burning on vegetation type diversity not including burnt patches. -->

<!-- ```{r SDI-no-burnt_2_1, echo=TRUE, fig.height=3, message=FALSE, warning=FALSE, out.width='100%'} -->
<!-- par(mfrow=c(1,2), cex=0.8) -->
<!-- plot(rw.no0.gam2, select=1, shade=T) -->
<!-- abline(h=0, lty = 2) -->
<!-- plot(rw.no0.gam2, select=2, shade=T) -->
<!-- abline(h=0, lty = 2) -->

<!-- ``` -->

<!-- The presence of natural ignition initial has a positive impact on diversity, but this effect becomes negative by the end of model run, likely because it contributes to the high number of burnt patches. -->

<!-- ```{r SDI-no-burnt_2_2, echo=TRUE, fig.height=3, message=FALSE, warning=FALSE, out.width='100%'} -->
<!-- par(mfrow=c(2,2), cex=0.8) -->
<!-- plot(rw.no0.gam2, select=7, shade=T) -->
<!-- abline(h=0, lty = 2) -->
<!-- plot(rw.no0.gam2, select=8, shade=T) -->
<!-- abline(h=0, lty = 2) -->
<!-- plot(rw.no0.gam2, select=9, shade=T) -->
<!-- abline(h=0, lty = 2) -->
<!-- plot(rw.no0.gam2, select=10, shade=T) -->
<!-- abline(h=0, lty = 2) -->

<!-- ``` -->

<!-- A cost to burning reduces the probability of burning and therefore frequency of burning behaviors. For this reason, it has the opposite effect trend to natural ignition. By limiting burning at the end of model run, we see greater diversity in the other vegetation types. -->

<!-- ```{r SDI-no-burnt_2_3, echo=TRUE, fig.height=3, message=FALSE, warning=FALSE, out.width='100%'} -->
<!-- par(mfrow=c(1,2), cex=0.8) -->
<!-- plot(rw.no0.gam2, select=11, shade=T) -->
<!-- abline(h=0, lty = 2) -->
<!-- plot(rw.no0.gam2, select=12, shade=T) -->
<!-- abline(h=0, lty = 2) -->
<!-- ``` -->

<!-- The same pattern arises when the types of vegetation that agents can burn is limited. Interestingly, however, there is still a positive impact by the end of model run when agents can burn any vegetation type. This likely indicates that this parameter does not strongly affect the overall trend towards increasing diversity. -->

<!-- ```{r SDI-no-burnt_2_4, echo=TRUE, fig.height=3, message=FALSE, warning=FALSE, out.width='100%'} -->
<!-- par(mfrow=c(1,3), cex=0.8) -->
<!-- plot(rw.no0.gam2, select=13, shade=T) -->
<!-- abline(h=0, lty = 2) -->
<!-- plot(rw.no0.gam2, select=14, shade=T) -->
<!-- abline(h=0, lty = 2) -->
<!-- plot(rw.no0.gam2, select=15, shade=T) -->
<!-- abline(h=0, lty = 2) -->
<!-- ``` -->

<!-- When looking at burnt neighbor limits, we get an opposite effect pattern than what might be expected based on the previous results. The strictest condition (*burnt-neighbor-limit* = 1), actually has a negative effect on diversity in the middle of model run. Conversely, the conditions that allow more burning have a positive impact on diversity by the end of model run. This might be because the strictest restrictions result in much of the environment failing to receive any long term benefits from burning because burning is so limited in frequency and space. -->

<!-- Taken together, these results indicate that a certain level of burning is required for vegetation diversity to increase. -->

<!-- ```{r SDI-no-burnt_correlations, echo=FALSE, message=FALSE, warning=FALSE, out.width='100%'} -->
<!-- par(mfrow = c(1,3)) -->
<!-- par(mar=c(0,1,0,1)) -->
<!-- #plot at 250 -->
<!-- pvalue250 = psych::corr.test(data250 %>% select(mean.burn.prob, shannon.div, shannon.div.no0))$p -->
<!-- corrplot::corrplot(cor(data250 %>% select(mean.burn.prob, shannon.div, shannon.div.no0), use = "pairwise.complete.obs"), -->
<!--                    method = "square", addCoef.col = "black",  -->
<!--                    col = scales::alpha(corrplot::COL2("RdBu"), alpha = 0.85), -->
<!--                    p.mat = pvalue250, insig="blank", sig.level=0.1,  -->
<!--                    type = "lower", number.cex = 0.5, diag=F) -->

<!-- #plot at 1000 -->
<!-- pvalue1000 = psych::corr.test(data1000 %>% select(mean.burn.prob, shannon.div, shannon.div.no0))$p -->
<!-- corrplot::corrplot(cor(data1000 %>% select(mean.burn.prob, shannon.div, shannon.div.no0), use = "pairwise.complete.obs"), -->
<!--                    method = "square", addCoef.col = "black",  -->
<!--                    col = scales::alpha(corrplot::COL2("RdBu"), alpha = 0.85), -->
<!--                    p.mat = pvalue1000, insig="blank", sig.level=0.1,  -->
<!--                    type = "lower", number.cex = 0.5, diag=F) -->

<!-- #plot at 2000 -->
<!-- pvalue2000 = psych::corr.test(data2000 %>% select(mean.burn.prob, shannon.div, shannon.div.no0))$p -->
<!-- corrplot::corrplot(cor(data2000 %>% select(mean.burn.prob, shannon.div, shannon.div.no0), use = "pairwise.complete.obs"), -->
<!--                    method = "square", addCoef.col = "black",  -->
<!--                    col = scales::alpha(corrplot::COL2("RdBu"), alpha = 0.85), -->
<!--                    p.mat = pvalue2000, insig="blank", sig.level=0.1,  -->
<!--                    type = "lower", number.cex = 0.5, diag=F) -->

<!-- ``` -->

<!-- This is confirmed by the increasingly positive correlation between average probability of burning, which can be taken as a proxy for burning frequency, and vegetation diversity of non-burnt patches (*shannon.div.no0*). -->

## Spatial distribution of burning events

Because burning behaviors have such a significant impact on the structure of the vegetation in the environment, we were curious if this is caused by differential use of space. To examine this, we looked at the spatial autocorrelation of where burning events occur within the landscape to assess land use by the agents. This analysis is split *cycle-duration.* We first use linear regressions to assess how the parameters and time affect the spatial autocorrelation of burning events. For this, we only consider significant values of Moran's I to evaluate clustering (positive values) and dispersion (negative values).

```{r burning-events_1, echo=FALSE, message=FALSE, warning=FALSE, out.width="100%",fig.height=4}
parameters = c(
  "natural_ignition", # 0.00, 0.05
  "cycle_duration",  # 100, 250
  "veg_cycle_start", # productive, unproductive
  "veg_distribution", # random, clustered
  "burnt_neighbor_limit", # 1, 4, 8
  "burn_cost", # 0, 50
  "burn_veg_type_threshold", # 4, 7
  "movement_model" #Random, Directed
)

be.morans.100 <- readRDS("../results/outputs/be_morans.i_cycle.100.rds")
be.morans.100[,parameters[-2]] = lapply(be.morans.100[,parameters[-2]] , as.factor)
be.morans.250 <- readRDS("../results/outputs/be_morans.i_cycle.250.rds")
be.morans.250[,parameters[-2]] = lapply(be.morans.250[,parameters[-2]] , as.factor)

be.morans.100$veg_distribution = factor(be.morans.100$veg_distribution, levels = c("\"random\"", "\"clustered\""))
be.morans.250$veg_distribution = factor(be.morans.250$veg_distribution, levels = c("\"random\"", "\"clustered\""))

be.morans.100$movement_model = factor(be.morans.100$movement_model, levels = c("\"Random Walk\"", "\"Directed Walk\""))
be.morans.250$movement_model = factor(be.morans.250$movement_model, levels = c("\"Random Walk\"", "\"Directed Walk\""))

be.morans.100 = be.morans.100 %>% filter(exp %in% finished.exp)
be.morans.250 = be.morans.250 %>% filter(exp %in% finished.exp)

be.morans.100 = be.morans.100 %>% filter(ticks != 1000) %>% filter(ticks != 2000)
be.morans.250 = be.morans.250 %>% filter(ticks != 1000) %>% filter(ticks != 2000)

# hist(be.morans.100$morans.i)
# hist(be.morans.250$morans.i)

fit1 = lm(morans.i ~ ticks*(.), data = be.morans.100 %>% filter(signif == T) %>% select_at(c("ticks", parameters[-2], "morans.i")))

fit2 = lm(morans.i ~ ticks*(.), data = be.morans.250 %>% filter(signif == T) %>% select_at(c("ticks", parameters[-2], "morans.i")))

par(mfrow = c(1,2))
plot(fit1, which = 2)
title(main = "cycle = 100 ticks")
plot(fit2, which = 2)
title(main = "cycle = 250 ticks")

fit1$coefficients[1:2]
fit2$coefficients[1:2]

```

The intercept values show that, on average, burning events are on average marginally clustered on the landscape. This spatial autocorrelation is then significantly affected by time and, on average, decreases as model run progresses. 

```{r burning-events_2_1, echo=FALSE, message=FALSE, warning=FALSE, out.width="100%"}
plot_summs(fit1, fit2, scale = T, model.names = c("cycle = 100 ticks", "cycle = 250 ticks"))
```

When looking at scaled regression coefficients, we can see that underlying distribution of resource potential (maximum veg type), burning limits, and movement models have the strongest effects on the spatial clustering of burning events. These strong effects are also maintained over time, as evidence by the high standardized regression coefficients for the interaction variables between these parameters and time). Importantly, time increase the effect size of these parameters in the same direction. For example, directed walks reduce the clustering of burning events on average and this effect is more negative with time.

```{r burning-events_2_2, echo=FALSE, message=FALSE, warning=FALSE, out.width="100%"}
bt.labs = c("can burn veg types 1-4", "can burn veg types 1-7")
names(bt.labs) = c(4, 7)

p1 = ggplot(be.morans.100 %>% filter(signif == T)) +
  geom_point(mapping = aes(x = ticks, y = morans.i)) +
  geom_smooth(mapping = aes(x = ticks, y = morans.i, color = as.factor(burnt_neighbor_limit), group = as.factor(burnt_neighbor_limit)), method = "lm") +
  facet_grid(burn_veg_type_threshold ~ movement_model + veg_distribution, scales = "free", labeller = labeller(burn_veg_type_threshold = bt.labs)) +
  theme(axis.text = element_text(size = 5), strip.text = element_text(size = 6))

p2 = ggplot(be.morans.250 %>% filter(signif == T)) +
  geom_point(mapping = aes(x = ticks, y = morans.i)) +
  geom_smooth(mapping = aes(x = ticks, y = morans.i, color = as.factor(burnt_neighbor_limit), group = as.factor(burnt_neighbor_limit)), method = "lm") +
  facet_grid(burn_veg_type_threshold ~ movement_model + veg_distribution, scales = "free", labeller = labeller(burn_veg_type_threshold = bt.labs)) +
  theme(axis.text = element_text(size = 5), strip.text = element_text(size = 6))

ggarrange(p1, p2, common.legend = T, legend = "bottom", labels = c("cycle = 100 ticks", "cycle = 250 ticks"), font.label = list(size = 8), vjust = 0.8, hjust = -1.25
) +
  theme(plot.margin = margin(0.1,0.1,0.1,0.1, "cm"))
```

Plotting the trends of burning event spatial autocorrelation through time by these significant parameters allows us to better visualize these patterns. We can see that stricter limits on which patches can be burned typically result in dispersion of burning events (Moran's I \< 0). High clustering of burning events only occurs when the resource potential on the landscape is also clustered. However, as we can see in the above graph, this is also affected by other burning limits and movement models.

## Forager mobility

In the model, foragers adjust how many steps they take during a foraging bout if they determine they will meet their energy requirements with fewer steps. Movement in the model is, therefore, patterned primarily by the energy available in the gridded landscape, which is determined by whether the model is in a productive or unproductive climatic period and how long those climatic periods last.

```{r fm-viz, echo=FALSE, message=FALSE, warning=FALSE, out.width="100%"}
ggplot(data %>% filter(ticks > 0)) +
  # geom_point(aes(x = ticks, y = mean.fm, color = `movement-model`), alpha = 0.01, size = 0.1) +
  geom_smooth(aes(x = ticks, y = mean.fm, color = `movement-model`), method = "gam") +
  #geom_hline(yintercept = 0, linetype = "dotted") +
  facet_grid(`cycle-duration` ~ `veg-cycle-start`, labeller = label_both) +
  scale_color_colorblind(labels = c("Directed Walk", "Random Walk"))

```

While cycle duration clearly causes fluctuations in agent movement behaviors, we chose to investigate average steps per foraging bout as a linear trend, splitting the data by cycle duration. Using mixed linear models, we can see how the other parameters affect forager movement while controlling for starting vegetation state.

```{r fm-mm-regs, echo=TRUE, fig.height=3, message=FALSE, warning=FALSE, out.width="100%"}

c100 = data %>% filter(`cycle-duration` == 100) %>% filter(ticks > 0)
c250 = data %>% filter(`cycle-duration` == 250) %>% filter(ticks > 0)

mm.fit1.1 = lmer(mean.fm ~ ticks + (1 | `movement-model`)  + (1 | `veg-cycle-start`), data = data)

mm.fit1.2 = lmer(mean.fm ~ ticks + `veg-distribution` + `burnt-neighbor-limit` + `burn-cost` + `burn-veg-type-threshold` + `natural-ignition` + `cycle-duration` + (1 | `movement-model`)  + (1 | `veg-cycle-start`),, data = data)

mm.fit1.3 = lmer(mean.fm ~ ticks*(`veg-distribution` + `burnt-neighbor-limit` + `burn-cost` + `burn-veg-type-threshold` + `natural-ignition`+ `cycle-duration`) + (1 | `movement-model`)  + (1 | `veg-cycle-start`), data = data)

mm.fit1.4 = lmer(mean.fm ~ ticks*(`veg-distribution` + `burnt-neighbor-limit` + `burn-cost` + `burn-veg-type-threshold` + `natural-ignition`) + (1 | `veg-cycle-start`) + (1 | `movement-model`) + (1 | `cycle-duration`), data = data)
anova(mm.fit1.1, mm.fit1.2, mm.fit1.3, mm.fit1.4)

# mm.fit2.1 = lmer(mean.fm ~ ticks + (1 | `movement-model`)  + (1 | `veg-cycle-start`), data = c250)
# 
# mm.fit2.2 = lmer(mean.fm ~ ticks + `veg-distribution` + `burnt-neighbor-limit` + `burn-cost` + `burn-veg-type-threshold` + `natural-ignition` + (1 | `veg-cycle-start`), data = c250)
# 
# mm.fit2.3 = lmer(mean.fm ~ ticks*(`veg-distribution` + `burnt-neighbor-limit` + `burn-cost` + `burn-veg-type-threshold` + `natural-ignition`) + (1 | `veg-cycle-start`), data = c250)
# 
# mm.fit2.4 = lmer(mean.fm ~ ticks*(`veg-distribution` + `burnt-neighbor-limit` + `burn-cost` + `burn-veg-type-threshold` + `natural-ignition`) + (1 | `veg-cycle-start`) + (1 | `movement-model`), data = c250)
# anova(mm.fit2.1, mm.fit2.2, mm.fit2.3, mm.fit2.4)

qqnorm(resid(mm.fit1.4))
qqline(resid(mm.fit1.4))

# qqnorm(resid(mm.fit2.4))
# qqline(resid(mm.fit2.4))

ggpubr::ggarrange(
  ggeffects::ggpredict(mm.fit1.4, terms = c("ticks", "veg-distribution")) %>%
    plot(show_data = FALSE, show_ci = FALSE), 
  ggeffects::ggpredict(mm.fit1.4, terms = c("ticks", "natural-ignition")) %>%
    plot(show_data = FALSE, show_ci = FALSE), 
  common.legend = T, legend = "bottom", nrow = 1
)

ggpubr::ggarrange(
  ggeffects::ggpredict(mm.fit1.4, terms = c("ticks", "burnt-neighbor-limit")) %>%
    plot(show_data = FALSE, show_ci = FALSE), 
  ggeffects::ggpredict(mm.fit1.4, terms = c("ticks", "burn-veg-type-threshold")) %>%
    plot(show_data = FALSE, show_ci = FALSE), 
  ggeffects::ggpredict(mm.fit1.4, terms = c("ticks", "burn-cost")) %>%
    plot(show_data = FALSE, show_ci = FALSE), 
  common.legend = T, legend = "bottom", nrow = 1
)

# ggpubr::ggarrange(
#   ggeffects::ggpredict(mm.fit1.4, terms = c("ticks", "natural-ignition")) %>%
#     plot(show_data = FALSE, show_ci = FALSE), 
#   ggeffects::ggpredict(mm.fit2.4, terms = c("ticks", "natural-ignition")) %>%
#     plot(show_data = FALSE, show_ci = FALSE), 
#   common.legend = T, labels = c("100 ticks", "250 ticks"), legend = "bottom", vjust = -0.1
# ) +
#   theme(plot.margin = margin(0.5,0.1,0.1,0.1, "cm"))
```

*TODO*: These models demonstrate that strict burning limits lead to higher mobility across model run. When burning is more frequent, mobility decreases quickly over model run. This is likely related to the increased vegetation diversity and higher proportions of high value vegetation types toward the end of model run. This trend is visible by looking at the correlations between diversity and vegetation proportions with forager mobility (*mean.fm*).

```{r mobility-veg-correlations, echo=FALSE, message=FALSE, warning=FALSE, out.width='100%'}
par(mfrow = c(1,3))
par(mar=c(0,1,0,1))
#plot at 250
pvalue250 = psych::corr.test(data250 %>% select(mean.fm, shannon.div, mean.burn.prob, veg_7, veg_6, veg_5))$p
corrplot::corrplot(cor(data250 %>% select(mean.fm, shannon.div, mean.burn.prob, veg_7, veg_6, veg_5), use = "pairwise.complete.obs"),
                   method = "square", addCoef.col = "black", 
                   col = scales::alpha(corrplot::COL2("RdBu"), alpha = 0.85),
                   p.mat = pvalue250, insig="blank", sig.level=0.1, 
                   type = "lower", number.cex = 0.5, diag=F)

#plot at 1000
pvalue1000 = psych::corr.test(data1000 %>% select(mean.fm, shannon.div, mean.burn.prob, veg_7, veg_6, veg_5))$p
corrplot::corrplot(cor(data1000 %>% select(mean.fm, shannon.div, mean.burn.prob, veg_7, veg_6, veg_5), use = "pairwise.complete.obs"),
                   method = "square", addCoef.col = "black", 
                   col = scales::alpha(corrplot::COL2("RdBu"), alpha = 0.85),
                   p.mat = pvalue1000, insig="blank", sig.level=0.1, 
                   type = "lower", number.cex = 0.5, diag=F)

#plot at 2000
pvalue2000 = psych::corr.test(data2000 %>% select(mean.fm, shannon.div, mean.burn.prob, veg_7, veg_6, veg_5))$p
corrplot::corrplot(cor(data2000 %>% select(mean.fm, shannon.div, mean.burn.prob, veg_7, veg_6, veg_5), use = "pairwise.complete.obs"),
                   method = "square", addCoef.col = "black", 
                   col = scales::alpha(corrplot::COL2("RdBu"), alpha = 0.85),
                   p.mat = pvalue2000, insig="blank", sig.level=0.1, 
                   type = "lower", number.cex = 0.5, diag=F)

```

*TODO*: At the end of model run, when forager mobility is lowest, there are negative correlations with vegetation diversity and the highest value vegetation types (*veg_7*, *veg_6*).

## Forager interactions

When looking at forager interactions, we have to consider them in relation to populations since more foragers on the landscape will necessarily mean more possible interactions. The model outputs interaction counts averaged across all agents and we divided this by the population count to get the average proportion of the population that an individual agent interacts with each tick.

First, we investigate parameter effects via linear regression.

```{r adj-fi-reg_1, echo=TRUE, message=FALSE, warning=FALSE, out.width='100%', fig.height=5}
# ggplot(data %>% filter(ticks > 0)) +
#   geom_density(aes(x = log(adj.fi)))
# summary(data$adj.fi)
fi.data = data %>% filter(ticks > 0)
summary((fi.data$adj.fi))

parameters = c(
  "natural-ignition", # 0.00, 0.05
  "cycle-duration",  # 100, 250
  "veg-cycle-start", # productive, unproductive
  "veg-distribution", # random, clustered
  "burnt-neighbor-limit", # 1, 4, 8
  "burn-cost", # 0, 50
  "burn-veg-type-threshold", # 4, 7
  "movement-model" #Random, Directed
)

fi.fit1 = lm(adj.fi ~ ticks*(.), data = fi.data %>% dplyr::select_at(c(parameters, "ticks", "adj.fi")))

plot_summs(fi.fit1, scale = T)

```

By comparing standardized regression coefficients, we can see the greatest effect on forager interactions is movement models and burn cost.

```{r adj-fi-viz, echo=FALSE, message=FALSE, warning=FALSE, out.width="100%"}
start.labs = c("start with unproductive vegetation", "start with productive vegetation")
names(start.labs) = c("\"unproductive\"", "\"productive\"")
cycle.labs = c("cycle every 250 ticks", "cycle every 100 ticks")
names(cycle.labs) = c(250, 100)
dist.labs = c("random environmental potential", "clustered environmental potential")
names(dist.labs) = c("\"random\"", "\"clustered\"")

ggplot(data %>% filter(ticks > 0)) +
  geom_smooth(aes(x = ticks, y = adj.fi, color = `movement-model`), se = T) +
  facet_grid(`cycle-duration` + `veg-cycle-start` ~ `burn-cost`, labeller = labeller(
    `veg-cycle-start` = start.labs, `cycle-duration` = cycle.labs
  )) +
  scale_color_colorblind()

```

When we visualize these differences, we can see that random walks result in a steep drop off. This means that a linear model is probably not the best fit, which is confirmed by the QQ-plot for the random walk data.

For this reason, we split the regression of the random walk data into two segments.

```{r adj-fi-reg_2, echo=TRUE, message=FALSE, warning=FALSE, out.width='100%', fig.height=4}
#need to split out by burning cost or do a glm

rw.data = data %>% filter(`movement-model` == "\"Random Walk\"") %>% filter(ticks > 0)
dw.data = data %>% filter(`movement-model` == "\"Directed Walk\"") %>% filter(ticks > 0)

car::qqPlot(rw.data$adj.fi)
car::qqPlot(dw.data$adj.fi)

dw.fit1 = lm(adj.fi ~ ticks*(.), data = dw.data %>% filter(ticks > 0) %>% select_at(c("ticks", "adj.fi", parameters[-8])))

rw.fit1 = lm(adj.fi ~ ticks*(.), data = rw.data %>% filter(ticks > 0) %>% select_at(c("ticks", "adj.fi", parameters[-8])))

rw.fit2 = segmented::segmented(rw.fit1, seg.Z = ~ ticks, psi = list(ticks = c(250)))
#summary(rw.fit2)
rw.fit2$psi
segmented::slope(rw.fit2)

# plotNormalDensity((rw.data %>% filter(ticks < 216))$adj.fi)
# plotNormalDensity((rw.data %>% filter(ticks > 216))$adj.fi)

rw.fit3 = lm(adj.fi ~ ticks*(.), data = rw.data %>% filter(ticks > 0) %>% select_at(c("ticks", "adj.fi", parameters[-8])) %>% filter(ticks < 216))

rw.fit4 = lm(adj.fi ~ ticks*(.), data = rw.data %>% filter(ticks > 0) %>% select_at(c("ticks", "adj.fi", parameters[-8])) %>% filter(ticks > 216))

# dw.fit1 %>% broom::tidy() %>% 
#   filter(p.value <= 0.05) %>%
#   mutate(p.value = scales::pvalue(p.value)) %>%
#   kable()

rw.fit3 %>% broom::tidy() %>% full_join((rw.fit4 %>% broom::tidy()), by = "term") %>%
  select(term, estimate.x, p.value.x, estimate.y, p.value.y) %>%
  filter(p.value.y <= 0.05 | p.value.x <= 0.05) %>%
  mutate(p.value.x = scales::pvalue(p.value.x), 
         p.value.y =scales::pvalue(p.value.y)) %>%
  rename(part_1_estimate = estimate.x, 
         part_1_pvalue = p.value.x, 
         part_2_estimate = estimate.y, 
         part_2_pvalue = p.value.y) %>%
  kable()
```

For the random walk data, we can see that initially forager interactions are affected only by *natural-ignition* and *burn-cost*. After the initial decrease in forager interactions, more of the parameters have significant effects, although the effect sizes are very low. This is consistent with the very small slope estimated for the second part of the segmented regression (see above figure as well).

```{r parameter-effects-adj-fi, out.width="100%", echo=FALSE, message=FALSE, warning=FALSE, fig.height = 3}
ggarrange(
  ggeffects::ggpredict(dw.fit1, terms = c("ticks", "veg-cycle-start")) %>%
    plot(show_data = FALSE, show_ci = FALSE, limits = c(0, 0.020)), 
  ggeffects::ggpredict(rw.fit3, terms = c("ticks", "veg-cycle-start")) %>%
    plot(show_data = FALSE, show_ci = FALSE, limits = c(0, 0.020)),
  ggeffects::ggpredict(rw.fit4, terms = c("ticks", "veg-cycle-start")) %>%
    plot(show_data = FALSE, show_ci = FALSE, limits = c(0, 0.020)), 
  common.legend = T, legend = "bottom", labels = c("Directed Walk", "Random Walk (ticks < 216)", "Random Walk (ticks > 216)"), nrow = 1, ncol = 3, font.label = list(size = 8), vjust = 0.8
) +
  theme(plot.margin = margin(0.1,0.2,0.1,0.1, "cm"), title = element_text(size = 7)) 

ggarrange(
  ggeffects::ggpredict(dw.fit1, terms = c("ticks", "veg-distribution")) %>%
    plot(show_data = FALSE, show_ci = FALSE, limits = c(0, 0.020)), 
  ggeffects::ggpredict(rw.fit3, terms = c("ticks", "veg-distribution")) %>%
    plot(show_data = FALSE, show_ci = FALSE, limits = c(0, 0.020)),
  ggeffects::ggpredict(rw.fit4, terms = c("ticks", "veg-distribution")) %>%
    plot(show_data = FALSE, show_ci = FALSE, limits = c(0, 0.020)), 
  common.legend = T, legend = "bottom", labels = c("Directed Walk", "Random Walk (ticks < 216)", "Random Walk (ticks > 216)"), nrow = 1, ncol = 3, font.label = list(size = 8), vjust = 0.8
) +
  theme(plot.margin = margin(0.1,0.2,0.1,0.1, "cm"), title = element_text(size = 7)) 

ggarrange(
  ggeffects::ggpredict(dw.fit1, terms = c("ticks", "burnt-neighbor-limit")) %>%
    plot(show_data = FALSE, show_ci = FALSE, limits = c(0, 0.020)), 
  ggeffects::ggpredict(rw.fit3, terms = c("ticks", "burnt-neighbor-limit")) %>%
    plot(show_data = FALSE, show_ci = FALSE, limits = c(0, 0.020)),
  ggeffects::ggpredict(rw.fit4, terms = c("ticks", "burnt-neighbor-limit")) %>%
    plot(show_data = FALSE, show_ci = FALSE, limits = c(0, 0.020)), 
  common.legend = T, legend = "bottom", labels = c("Directed Walk", "Random Walk (ticks < 216)", "Random Walk (ticks > 216)"), nrow = 1, ncol = 3, font.label = list(size = 8), vjust = 0.8
) +
  theme(plot.margin = margin(0.1,0.2,0.1,0.1, "cm"), title = element_text(size = 7)) 

ggarrange(
  ggeffects::ggpredict(dw.fit1, terms = c("ticks", "burn-veg-type-threshold")) %>%
    plot(show_data = FALSE, show_ci = FALSE, limits = c(0, 0.020)), 
  ggeffects::ggpredict(rw.fit3, terms = c("ticks", "burn-veg-type-threshold")) %>%
    plot(show_data = FALSE, show_ci = FALSE, limits = c(0, 0.020)),
  ggeffects::ggpredict(rw.fit4, terms = c("ticks", "burn-veg-type-threshold")) %>%
    plot(show_data = FALSE, show_ci = FALSE, limits = c(0, 0.020)), 
  common.legend = T, legend = "bottom", labels = c("Directed Walk", "Random Walk (ticks < 216)", "Random Walk (ticks > 216)"), nrow = 1, ncol = 3, font.label = list(size = 8), vjust = 0.8
) +
  theme(plot.margin = margin(0.1,0.2,0.1,0.1, "cm"), title = element_text(size = 7)) 

ggarrange(
  ggeffects::ggpredict(dw.fit1, terms = c("ticks", "burn-cost")) %>%
    plot(show_data = FALSE, show_ci = FALSE, limits = c(0, 0.020)), 
  ggeffects::ggpredict(rw.fit3, terms = c("ticks", "burn-cost")) %>%
    plot(show_data = FALSE, show_ci = FALSE, limits = c(0, 0.020)),
  ggeffects::ggpredict(rw.fit4, terms = c("ticks", "burn-cost")) %>%
    plot(show_data = FALSE, show_ci = FALSE, limits = c(0, 0.020)), 
  common.legend = T, legend = "bottom", labels = c("Directed Walk", "Random Walk (ticks < 216)", "Random Walk (ticks > 216)"), nrow = 1, ncol = 3, font.label = list(size = 8), vjust = 0.8
) +
  theme(plot.margin = margin(0.1,0.2,0.1,0.1, "cm"), title = element_text(size = 7))

ggarrange(
  ggeffects::ggpredict(dw.fit1, terms = c("ticks", "natural-ignition")) %>%
    plot(show_data = FALSE, show_ci = FALSE, limits = c(0, 0.020)), 
  ggeffects::ggpredict(rw.fit3, terms = c("ticks", "natural-ignition")) %>%
    plot(show_data = FALSE, show_ci = FALSE, limits = c(0, 0.020)),
  ggeffects::ggpredict(rw.fit4, terms = c("ticks", "natural-ignition")) %>%
    plot(show_data = FALSE, show_ci = FALSE, limits = c(0, 0.020)), 
  common.legend = T, legend = "bottom", labels = c("Directed Walk", "Random Walk (ticks < 216)", "Random Walk (ticks > 216)"), nrow = 1, ncol = 3, font.label = list(size = 8), vjust = 0.8
) +
  theme(plot.margin = margin(0.1,0.2,0.1,0.1, "cm"), title = element_text(size = 7))
```

As noted above, the only parameter that seems to have varied effects on the initial forager interactions for random walks is *natural-ignition.* For this reason, we focus on comparing directed walk data and the second segment of random walk data.

When the underlying distribution of resource potential is clustered, we see more forager interactions than when that distribution is random. We also see more forager interactions when burning behaviors are not limited by burnt neighboring patches. This is interesting because the other two burning parameters, *burn-veg-type-threshold* and *burn-cost*, show increased forager interactions with stricter burning limits.

```{r veg-clustering_and_interactions, echo=FALSE, message=FALSE, warning=FALSE, out.width='100%', fig.height = 4}
par(mfrow = c(1,2))
#plot at 2000
pvalue.r = psych::corr.test(data2000 %>% filter(`veg-distribution` == "\"random\"") %>% select(mean.fm, adj.fi, veg_morans.i))$p
corrplot::corrplot(cor(data2000 %>% filter(`veg-distribution` == "\"random\"") %>% select(mean.fm, adj.fi, veg_morans.i), use = "pairwise.complete.obs"),
                   method = "square", addCoef.col = "black", 
                   col = scales::alpha(corrplot::COL2("RdBu"), alpha = 0.85),
                   p.mat = pvalue.r, insig="blank", sig.level=0.1, 
                   type = "lower", number.cex = 0.5, diag=F, 
                   title = "random distribution", mar=c(0,0,1,0))

pvalue.c = psych::corr.test(data2000 %>% filter(`veg-distribution` == "\"clustered\"") %>% select(mean.fm, adj.fi, veg_morans.i))$p
corrplot::corrplot(cor(data2000 %>% filter(`veg-distribution` == "\"clustered\"") %>% select(mean.fm, adj.fi, veg_morans.i), use = "pairwise.complete.obs"),
                   method = "square", addCoef.col = "black", 
                   col = scales::alpha(corrplot::COL2("RdBu"), alpha = 0.85),
                   p.mat = pvalue.c, insig="blank", sig.level=0.1, 
                   type = "lower", number.cex = 0.5, diag=F, 
                   title = "clustered distribution", mar=c(0,0,1,0))
```

## References

```{r citations, echo=FALSE, message=FALSE, warning=FALSE}
pkgs <- grateful::cite_packages(output = "table", out.dir = ".", omit = c("QuantPsyc", "marginaleffects"))
knitr::kable(pkgs)
```
